### 2019-10-16 ipfb.tex
Added minimal tex and bib files for getting the paper started.

\documentclass{pasa}%

\usepackage{graphicx}

\title[MWA Beamformer PFB Inversion]{MWA Beamformer PFB Inversion}

%%% SAMPLE %%%
%% Please note that the command \and is not supported in \author.
%\author[Author1 et al.]{Author1$^1$, Author2$^2$, Author3$^2$ and Author4$^{2,}$\thanks{This is an example of author footnote}
%\affil{$^1$This is  an example of Affiliation r Author 1}%
%\affil{$^2$This is  an example of Affiliation for Author 2}
%}%
%%% END SAMPLE %%%

\author[McSweeney et al.]{S. J. McSweeney$^1$, Author2, \dots
\affil{$^1$CIRA, Curtin University}%
}

\jid{PASA}
\doi{10.1017/pas.\the\year.xxx}
\jyear{\the\year}

\usepackage{aas_macros}
\usepackage{hyperref} 
\hypersetup{colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue}

%%%%%%% IMPORTANT: We disable hyperlinks by default with this line, to avoid the error "\pdfendlink ended up in different nesting level" while writing.
\hypersetup{draft}
%%%%%%% You may comment or delete the line above to make hyperlinks in your paper active. If you then encounter a strange "\pdfendlink ended up in different nesting level than \pdfstartlink", don't worry! Uncomment the line again, and see https://www.overleaf.com/help/246 for further information.

\begin{document}

\begin{frontmatter}
\maketitle

\begin{abstract}
[Abstract\dots]
\end{abstract}

\begin{keywords}
keyword1 -- keyword2 -- keyword3 -- keyword4 -- keyword5
\end{keywords}
\end{frontmatter}

\section{INTRODUCTION }
\label{sec:intro}

Here is a citation: \citep{Harris2011}.

%%% SAMPLE %%%
%\begin{table}
%\caption{This is an example of table caption.}
%\centering
%\begin{tabular}{@{}cc@{}}
%\hline\hline
%Dimension & Classification accuracy \\
%\hline%
% 1  & 0.6232$^{(a)}$ \\
% 2  & 0.9635 \\ 
% 3  & 0.9724 \\ 
% 4  & 0.9690 \\ 
% 5  & 0.9840 \\ 
% 6  & 0.9842 \\ 
% 7  & 0.9873 \\ 
% 8  & 0.9884 \\
% 9  & 0.9873 \\ 
% 10 & 0.9898 \\ 
% 11 & 0.9914 \\
%\hline\hline
%\end{tabular}
%\label{tab1}
%\medskip
%\tabnote{$^a$This is an example of table footnote}
%\tabnote{This is an example of table footnote}
%\tabnote{This is an example of table footnote}
%\end{table}
% 
%\begin{acknowledgements}
%This is a multiline text of acknowledgments. We are met here on a great battlefield of that war. We have come to dedicate a portion of it as a final resting place for those who here gave their lives that that nation might live.
%\end{acknowledgements}
%
%
%\begin{appendix}
%
%\section{AN EXAMPLE OF APPENDIX HEAD}
%
% Consider a data set
%\begin{equation}
%S=(f_{ij})_{m\times n}
%\end{equation} the \(i\)th
%data point of which is
%\[ (f_{i1}, . . . , f_{in}).\]
% Let $\overline{f}_q=\frac{1}{m}\sum_{i=1}^mf_{iq}$ and $\sigma_q$ The brave men, living and dead, who struggled, here, have consecrated it far above our poor power to add or detract. Suppose that
%\[X_i=(x_{i1},\dots,x_{in}) \indent (i=1,\dots, m),\]  
%where $x_{ij}=(f_{ij}-\overline{f}_j)/\sigma_j $ and
%\[B=(X_1^T,\dots,X_m^T)^T.\]
% Then we can show that
%\[C=B^TB=\sum\limits_{i=1}^m X_i^TX_i=(C_{jk})_{n\times n},\]
%where $C_{jk}=\sum_{i=1}^mx_{ij}x_{ik}$ is the correlation matrix. Our goal is to find a normalized vector 
%$$a_1=(a_{11},a_{12},\dots,a_{1n})^T$$
% such that the projection of the standardized data
%\[X_ia_1=\sum\limits_{k=1}^n x_{ik}a_{1k},\]
%\noindent then $Ba_1$ 
% \[a_1^TB^T ¡¤ Ba_1=a_1^TCa_1.\]
% Our goal is to maximize this value under the constraint $a_1^Ta_1=1$. Let $\lambda_{\rm max}$ be the largest eigenvalue of
% $C$. According to the Rayleigh--Ritz theorem, $a_1$ can be obtained by solving
% \[Ca_1= \lambda_{\rm max}a_1.\]
%But in a larger sense we can not dedicate -- we can not consecrate -- we can not hallow this ground. The brave men, living and dead, who struggled, here, have consecrated it far above our poor power to add or detract. The world will little note, nor long remember, what we say here, but can never forget what they did here. It is for us, the living, rather to be dedicated here to the unfinished work which they have, thus far, so nobly carried on \cite{abt1981}. It is rather for us to be here dedicated to the great task remaining before us  that from these honoured dead we take increased devotion to that cause for which they here gave the last full measure of devotion  that we here highly resolve that these dead shall not have died in vain; that this nation shall have a new birth of freedom; and that this government \cite{abt1984b} of the people, by the people, for the people, shall not perish from the earth.
%\end{appendix}
%%% END SAMPLE %%%

\bibliographystyle{pasa-mnras}
\bibliography{biblio.bib}

\end{document}

### 2019-10-16 ipfb.tex
Started writing the introduction

@@
 
-\title[MWA Beamformer PFB Inversion]{MWA Beamformer PFB Inversion}
+\title[MWA tied-array processing IV]{MWA tied-array processing IV: Microsecond time resolution via PFB synthesis}
 
@@
 
-\author[McSweeney et al.]{S. J. McSweeney$^1$, Author2, \dots
-\affil{$^1$CIRA, Curtin University}%
+\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, I. Morrison$^1$
+\affil{$^1$International Centre for Radio Astronomy Research (ICRAR), GPO Box U1987, Perth, WA 6845, Australia}%
+\affil{$^2$CSIRO Astronomy and Space Science, PO Box 76, Epping, NSW 1710, Australia}
 }
@@
 \begin{keywords}
-keyword1 -- keyword2 -- keyword3 -- keyword4 -- keyword5
+    instrumentation: interferometers -- pulsars: general -- techniques: interferometric
 \end{keywords}
@@
 
-Here is a citation: \citep{Harris2011}.
+The Murchison Widefield Array \citep[MWA;][]{Tingay2013} is a low-frequency ($\sim80$-$300\,$MHz) aperture array telescope situated in remote Western Australia.
+Now in its second phase of development \citep[Phase II;][]{Wayth2018}, it consists of 256 `tiles' (sets of $4\times4$ cross-dipole antennas) distributed over an area roughly $5.3\,$km in diameter, 128 of which can be used at a single time to form an interferometer.
+Originally conceived as an imaging telescope (which requires only the time-averaged cross-correlation products of the tiles, or `visibilities', to be retained on disk), it was subsequently augmented with the functionality to capture the raw complex voltages of each tile, known as the Voltage Capture System \citep[VCS;][]{Tremblay2015}.
+This system (with its accompanying implementation, described in further detail below) has enabled the MWA to be used as a premier instrument for high-time resolution studies of transient signals, especially pulsars \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018}.
 

### 2019-10-16 ipfb.tex
Adding to the intro. also amended title and author list

@@
 
-\title[MWA tied-array processing IV]{MWA tied-array processing IV: Microsecond time resolution via PFB synthesis}
+\title[MWA tied-array processing III]{MWA tied-array processing III: Microsecond time resolution via synthesis filterbank}
 
@@
 
-\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, I. Morrison$^1$
+\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$
 \affil{$^1$International Centre for Radio Astronomy Research (ICRAR), GPO Box U1987, Perth, WA 6845, Australia}%
@@
 
-The Murchison Widefield Array \citep[MWA;][]{Tingay2013} is a low-frequency ($\sim80$-$300\,$MHz) aperture array telescope situated in remote Western Australia.
-Now in its second phase of development \citep[Phase II;][]{Wayth2018}, it consists of 256 `tiles' (sets of $4\times4$ cross-dipole antennas) distributed over an area roughly $5.3\,$km in diameter, 128 of which can be used at a single time to form an interferometer.
+The Murchison Widefield Array \citep[MWA;][]{Tingay2013} is a low-frequency ($\sim80$ to $300\,$MHz) aperture array telescope located at the Murchison Radio Observatory (MRO) in Western Australia.
+Now in its second phase of development \citep[Phase II;][]{Wayth2018}, it consists of 256 `tiles' (sets of $4\times4$ cross-dipole antennas) distributed over an area approximately $5.3\,$km in diameter, 128 of which can be used at a single time to form an interferometer.
 Originally conceived as an imaging telescope (which requires only the time-averaged cross-correlation products of the tiles, or `visibilities', to be retained on disk), it was subsequently augmented with the functionality to capture the raw complex voltages of each tile, known as the Voltage Capture System \citep[VCS;][]{Tremblay2015}.
-This system (with its accompanying implementation, described in further detail below) has enabled the MWA to be used as a premier instrument for high-time resolution studies of transient signals, especially pulsars \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018}.
+This system has enabled the MWA to be used as a premier instrument for high-time resolution studies of transient signals, especially pulsars \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018}.
+
+Although the tile voltages are sampled at a (Nyquist) rate of $655.36\,$MHz, these data undergo several stages of processing before finally being written to disk.
+After low-noise filtering and digitising the raw signal, they are subject to a two-stage frequency analysis filter, which trades time resolution for increased frequency resolution.
+In the MWA's case, both stages of the analysis filter were implemented as polyphase filterbanks \citep[PFBs;][\dots]{Harris2011,Prabu2015}.
+The first stage (`coarse') PFB reduces the effecting sampling rate by a factor of 512, resulting in an array of complex-valued samples with $1.28\,$MHz resolution in frequency and $\sim0.8\,\mu$s in time.
+In the second stage (`fine') PFB, each $1.28\,$MHz (i.e.
+`coarse') further increases the frequency resolution (and decreases the time resolution) by a factor of 128, resulting in samples $10\,$kHz wide (in frequency) and $100\,\mu$s long (in time).
 

### 2019-10-16 ipfb.tex
Added a better opening paragraph to the introduction

@@
 
-\section{INTRODUCTION }
+\section{INTRODUCTION}
 \label{sec:intro}
+
+Some of the most exciting advances in time-domain astronomy have only been made possible by pushing the capabilities of latest generation telescopes to be sensitive to signals of shorter and shorter duration.
+The serendipitous discovery of pulsars in the late 1960's is perhaps the prototypical example.
+Another more recent example is the continuing effort to detect nanohertz gravitational waves by means of pulsar timing arrays (CITATIONS), which requires the continual monitoring of millisecond pulsars (MSPs) with microsecond accuracy.
+Pulsars are also known to exhibit temporal structures on microsecond and even nanosecond time scales, providing major clues for the underlying radio emission mechanism.
+Similarly, fast radio bursts (FRBs) have been shown to exhibit temporal sub-millisecond structures that either point to the intrinsic emission mechanism or to interesting propagation effects occurring in the intergalactic medium (CITATIONS).
+All of these examples serve to illustrate the scientifically important and still largely untapped parameter space that is only accessible to telescopes equipped with a sufficiently high time resolution observing mode.
 
@@
 Although the tile voltages are sampled at a (Nyquist) rate of $655.36\,$MHz, these data undergo several stages of processing before finally being written to disk.
-After low-noise filtering and digitising the raw signal, they are subject to a two-stage frequency analysis filter, which trades time resolution for increased frequency resolution.
+After low-noise filtering and digitising the raw signal, they are subjected to a two-stage frequency analysis filter, which trades time resolution for increased frequency resolution.
 In the MWA's case, both stages of the analysis filter were implemented as polyphase filterbanks \citep[PFBs;][\dots]{Harris2011,Prabu2015}.

### 2019-10-17 ipfb.tex
Finished first draft of the intro, started working on section 2

@@
 
-\title[MWA tied-array processing III]{MWA tied-array processing III: Microsecond time resolution via synthesis filterbank}
+\title[MWA tied-array processing III]{MWA tied-array processing III: Microsecond time resolution via a synthesis filter}
 
@@
 Some of the most exciting advances in time-domain astronomy have only been made possible by pushing the capabilities of latest generation telescopes to be sensitive to signals of shorter and shorter duration.
-The serendipitous discovery of pulsars in the late 1960's is perhaps the prototypical example.
-Another more recent example is the continuing effort to detect nanohertz gravitational waves by means of pulsar timing arrays (CITATIONS), which requires the continual monitoring of millisecond pulsars (MSPs) with microsecond accuracy.
-Pulsars are also known to exhibit temporal structures on microsecond and even nanosecond time scales, providing major clues for the underlying radio emission mechanism.
+The serendipitous discovery of pulsars in the late 1960's is perhaps the prototypical example \citep{Hewish1968}.
+In more recent times, the ongoing effort to detect nanohertz gravitational waves by means of pulsar timing arrays requires the continual monitoring of the times of arrival (TOAs) of millisecond pulsars (MSPs) with microsecond accuracy (CITATIONS).
+Pulsars are also known to exhibit temporal structures on microsecond and even nanosecond time scales, providing major clues for the underlying radio emission mechanism (CITATIONS).
 Similarly, fast radio bursts (FRBs) have been shown to exhibit temporal sub-millisecond structures that either point to the intrinsic emission mechanism or to interesting propagation effects occurring in the intergalactic medium (CITATIONS).
@@
 Originally conceived as an imaging telescope (which requires only the time-averaged cross-correlation products of the tiles, or `visibilities', to be retained on disk), it was subsequently augmented with the functionality to capture the raw complex voltages of each tile, known as the Voltage Capture System \citep[VCS;][]{Tremblay2015}.
-This system has enabled the MWA to be used as a premier instrument for high-time resolution studies of transient signals, especially pulsars \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018}.
+This system has enabled the MWA to be used as a premier instrument for high-time resolution studies of transient signals, especially pulsars.
 
 Although the tile voltages are sampled at a (Nyquist) rate of $655.36\,$MHz, these data undergo several stages of processing before finally being written to disk.
-After low-noise filtering and digitising the raw signal, they are subjected to a two-stage frequency analysis filter, which trades time resolution for increased frequency resolution.
+After preliminary filtering and digitisation, the raw voltages are subjected to a two-stage frequency analysis filter, which trades time resolution for increased frequency resolution.
 In the MWA's case, both stages of the analysis filter were implemented as polyphase filterbanks \citep[PFBs;][\dots]{Harris2011,Prabu2015}.
-The first stage (`coarse') PFB reduces the effecting sampling rate by a factor of 512, resulting in an array of complex-valued samples with $1.28\,$MHz resolution in frequency and $\sim0.8\,\mu$s in time.
-In the second stage (`fine') PFB, each $1.28\,$MHz (i.e.
-`coarse') further increases the frequency resolution (and decreases the time resolution) by a factor of 128, resulting in samples $10\,$kHz wide (in frequency) and $100\,\mu$s long (in time).
+The first stage (`coarse') PFB reduces the effecting sampling rate by a factor of 512, resulting in an array of complex-valued samples with $1.28\,$MHz resolution in frequency (`coarse' channels) and $\sim0.8\,\mu$s in time.
+In the second stage (`fine') PFB, each coarse channel is further split into $128 \times 10\,$kHz `fine' channels at the cost of decreasing the time resolution to $100\,\mu$s.
+
+In the current MWA system design, only the latter time resolution data product (i.e. $100\,\mu$s) is made available to the user.
+While this is sufficient for many pulsar studies \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018}, it is nevertheless too coarse for many science applications involving MSPs.
+In principle, the original higher time resolution can be recovered from the channelised output (either approximately or exactly) by means of a \textit{synthesis filter}, which acts as an `inverse' operation to the analysis filter.
+The conditions under which the original time series can be exactly reproduced depends on the choice of analysis and synthesis filters.
+
+Here, we describe the synthesis filter that is implemented as the (optional) final stage of the tied-array beamforming pipeline, the former stages of which are described in detail in \citet[][hereafter Paper I]{Ord2019} and \citet[][hereafter Paper II]{Xue2019}.
+The synthesis filter is applied to the fine-channel output of the beamformer, and recovers the coarse channel time series.
+That is, it effectively `undoes' the fine PFB, increasing the available time resolution to $\sim 0.8\,\mu$s.
+A brief review of PFBs in general, and their particular implementation in the case of the MWA, are given in \S\ref{sec:pfb}.
+The design of the synthesis filter is described in \S\ref{sec:ipfb}, including a discussion of its fidelity, i.e., the appearance of any temporal and spectral artefacts introduced by the synthesis filter itself.
+Finally, the practical use of this functionality is demonstrated through two examples: observations of the MSPs J2241$-$5236 and J0437$-$4715.
+
+\section{Polyphase filterbanks (PFBs)}
+\label{sec:pfb}
+
+PFBs are a type of analysis filter, designed to extract spectral information out of discrete time series data.
+They can be considered a generalisation of the more familiar Discrete Fourier Transform (DFT), and are designed to overcome the dual problems of uneven frequency response and spectral leakage inherent in the application of DFTs to finite length data sets.
+They are well described in standard texts \citep{Crochiere1983,Harris2004,Oppenheim2009}; a clear and concise review of PFBs in the context of radio astronomy is given in \citet{Harris2011}.
+Therefore, only a brief review of the salient features are given below, in order to lay out the notation used in this paper and to prepare the reader for what follows.
+
+\subsection{General review and mathematical description}
+
+\subsection{MWA implementation of the fine PFB}
+
+\section{Synthesis filter}
+\label{sec:ipfb}
+
+\subsection{Design}
+
+\subsection{Implementation}
+
+\subsection{Fidelity}
 

### 2019-10-17 ipfb.tex
Fixed up a few issues with the bibliography.

@@
 PFBs are a type of analysis filter, designed to extract spectral information out of discrete time series data.
-They can be considered a generalisation of the more familiar Discrete Fourier Transform (DFT), and are designed to overcome the dual problems of uneven frequency response and spectral leakage inherent in the application of DFTs to finite length data sets.
+They can be considered a generalisation of the more familiar discrete Fourier transform (DFT), and are designed to overcome the dual problems of uneven frequency response and spectral leakage inherent in the application of DFTs to data sets of finite length.
 They are well described in standard texts \citep{Crochiere1983,Harris2004,Oppenheim2009}; a clear and concise review of PFBs in the context of radio astronomy is given in \citet{Harris2011}.
@@
 
-\subsection{General review and mathematical description}
+\subsection{General review and mathematical notation}
+
+Like the DFT, the PFB is a transformation from the time domain, $x[m]$, to the frequency domain $X[k]$, where the $[\cdot]$ notation denotes a discretised index, and where $m$ and $k$ are indices for time and frequency, respectively.
 

### 2019-10-18 ipfb.tex
Finished first draft of the PFB description section

--- 2019-10-17 ipfb.tex
@@
 The design of the synthesis filter is described in \S\ref{sec:ipfb}, including a discussion of its fidelity, i.e., the appearance of any temporal and spectral artefacts introduced by the synthesis filter itself.
-Finally, the practical use of this functionality is demonstrated through two examples: observations of the MSPs J2241$-$5236 and J0437$-$4715.
+Finally, the practical use of this functionality is demonstrated through two examples: MWA observations of the MSPs J2241$-$5236 and J0437$-$4715.
 
@@
 PFBs are a type of analysis filter, designed to extract spectral information out of discrete time series data.
-They can be considered a generalisation of the more familiar Discrete Fourier Transform (DFT), and are designed to overcome the dual problems of uneven frequency response and spectral leakage inherent in the application of DFTs to finite length data sets.
-They are well described in standard texts \citep{Crochiere1983,Harris2004,Oppenheim2009}; a clear and concise review of PFBs in the context of radio astronomy is given in \citet{Harris2011}.
-Therefore, only a brief review of the salient features are given below, in order to lay out the notation used in this paper and to prepare the reader for what follows.
+They can be considered a generalisation of the more familiar discrete Fourier transform (DFT), and are designed to overcome the undesirably uneven frequency response (i.e.
+spectral leakage) inherent in the application of DFTs to discretely sampled time series of finite length.
+They are well described in standard texts \citep{Crochiere1983,Harris2004,Oppenheim2009}; a clear and concise review of PFBs in the context of radio astronomy is given in \citet{Harris2011}, whose notation is closely followed here.
+Thus, only a brief review of the salient features is given, in order to prepare the reader for the description of the synthesis filter in the following sections.
 
-\subsection{General review and mathematical description}
+\subsection{General review and mathematical notation}
+
+Like the DFT, the PFB is a transformation from the time domain, $x[n]$, to the frequency domain $X[k]$, where the $[\cdot]$ notation denotes a discretised index, and where $n,k \in \mathbb{Z}$ are the indices for time and frequency, respectively.
+Let $N$ be the number of (equally spaced) frequency channels required for some desired spectral resolution.
+Although applying a DFT to $N$ adjacent time samples will produce the desired resolution, the result will be an imperfect representation of the true spectral content of $x[n]$ because of \textit{spectral leakage}, which is when power that properly `belongs' to some particular frequency bin appears in (or, is \textit{aliased} to) other, nearby bins.
+The impossibility of perfectly eliminating spectral leakage can be seen by realising that operating on a finite-length time series is equivalent to multiplying an arbitrarily long time series with a rectangular window function,
+\begin{equation}
+    w_R[n] = \begin{cases} 1, & 0 \le n < N, \\ 0, & \text{elsewhere}, \end{cases}
+\end{equation}
+whose effect in the frequency domain is to convolve the ``true'' spectrum of the signal with the Fourier transform of the window function.
+In the case of a rectangular window, this is the sinc function.
+
+A common strategy for mitigating spectral leakage is to choose an alternative window function whose Fourier pair is localised in the frequency domain, and which therefore produces a tolerable level of spectral leakage when convolved with the signal's spectrum.
+Many possible windowing functions have been identified, which in general trade the `amount' of leakage with the `location' of the leaked components.
+For our purposes, it is sufficient to note that the inevitable presence of a windowing function motivates the definition of the \textit{analysis filter}, $h[n]$, and the generalised \textit{windowed DFT}
+\begin{equation}
+    X[k] = \sum_{n=0}^{N-1} h[n]\,x[n]\,e^{-2\pi j k (n/N)},
+    \label{eqn:wdft}
+\end{equation}
+where $j = \sqrt{-1}$ denotes the imaginary number, and it is understood that $0 \le k < N$.
+The choice of $h[n]$ is motivated by the shape of its \textit{frequency response} (i.e.
+its Fourier pair), whose characteristics (e.g.
+width, location of sidelobes) might carry particular advantages in certain contexts.
+Note that leaving $x[n]$ ``unweighted'' is equivalent to choosing $h[n] = w_R[n]$.
+
+It is well known that scaling a function in the time domain produces the inverse scaling in the Fourier domain.
+This fact motivates an alternative strategy for mitigating spectral leakage.
+If more samples are available, say $M = NP$ for $P > 1$, then stretching (i.e.
+scaling and upsampling) the analysis filter will result in a frequency response function that is the same shape as, but $P$ times narrower than the original analysis filter.
+Applying the DFT to the larger set of windowed samples and subsequently \emph{downsampling} the resulting spectrum (by choosing every $P$th frequency bin and rejecting the rest) ensures that the original desired spectral resolution is retained, but with significantly less spectral leakage.
+
+The algorithm embodied in the above strategy defines the PFB.
+It is clear that choosing a larger value for $P$ will lessen spectral leakage by the same factor, but this naturally comes at a greater computational cost.
+However, one of the great advantages of the PFB is that the above operations of using a wider analysis wilter and downsampling the resulting spectrum are mathematically equivalent to first segmenting the windowed time series into segments (known as `taps') of size $N$, summing their respective samples element-wise, and performing a single DFT on the resulting array (still of size $N$).
+Mathematically,
+\begin{equation}
+    X[k] = \sum_{n=0}^{N-1} b[n]\,e^{-2\pi j k (n/N)},
+    \label{eqn:pfb}
+\end{equation}
+where
+\begin{equation*}
+    b[n] = \sum_{\rho=0}^{P-1} h[n + N\rho]\,x[n + N\rho].
+\end{equation*}
+A short proof of the equivalence of this expression with the algorithm described above is given in \citet{Harris2011}.
+The name `polyphase' refers to the structure of $b[n]$ defined in Eq. \eqref{eqn:pfb}.
+It is illustrated in Fig. \ref{fig:pfb}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{example-image-a}
+    \caption{A diagramatic representation of the PFB algorithm, as defined in Eq. \eqref{eqn:pfb}.}
+    \label{fig:pfb}
+\end{figure}
 

### 2019-10-18 ipfb.tex
A small bit of rewording for clarity

@@
 If more samples are available, say $M = NP$ for $P > 1$, then stretching (i.e.
-scaling and upsampling) the analysis filter will result in a frequency response function that is the same shape as, but $P$ times narrower than the original analysis filter.
+scaling and upsampling) the analysis filter will result in a frequency response function that is similar in shape, but $P$ times narrower than the original analysis filter.
 Applying the DFT to the larger set of windowed samples and subsequently \emph{downsampling} the resulting spectrum (by choosing every $P$th frequency bin and rejecting the rest) ensures that the original desired spectral resolution is retained, but with significantly less spectral leakage.
@@
 The algorithm embodied in the above strategy defines the PFB.
-It is clear that choosing a larger value for $P$ will lessen spectral leakage by the same factor, but this naturally comes at a greater computational cost.
-However, one of the great advantages of the PFB is that the above operations of using a wider analysis wilter and downsampling the resulting spectrum are mathematically equivalent to first segmenting the windowed time series into segments (known as `taps') of size $N$, summing their respective samples element-wise, and performing a single DFT on the resulting array (still of size $N$).
+It is clear that choosing a larger value for $P$ will lessen spectral leakage by the same factor, but this naturally comes at a greater computational cost, since the DFT is now applied to $M$ samples.
+However, one of the great advantages of the PFB is that the above operations of using a wider analysis wilter and downsampling the resulting spectrum are mathematically equivalent to first segmenting the windowed time series into $P$ segments (known as `taps') of size $N$, summing their respective samples element-wise, and performing a single DFT on the resulting array (now of size $N$).
 Mathematically,

### 2019-10-18 ipfb.tex
Added a script that is trying (but not yet succeeding) in figuring out how the fine pfb filter coefficients were derived

@@
 It is clear that choosing a larger value for $P$ will lessen spectral leakage by the same factor, but this naturally comes at a greater computational cost, since the DFT is now applied to $M$ samples.
-However, one of the great advantages of the PFB is that the above operations of using a wider analysis wilter and downsampling the resulting spectrum are mathematically equivalent to first segmenting the windowed time series into $P$ segments (known as `taps') of size $N$, summing their respective samples element-wise, and performing a single DFT on the resulting array (now of size $N$).
-Mathematically,
+However, one of the great advantages of the PFB is that the above operations of using a wider analysis wilter and downsampling the resulting spectrum are mathematically equivalent to first segmenting the windowed time series into $P$ segments (known as `taps') of size $N$, summing their respective samples element-wise, and performing a single DFT on the resulting array (now of size $N$), i.e.
 \begin{equation}
@@
 A short proof of the equivalence of this expression with the algorithm described above is given in \citet{Harris2011}.
-The name `polyphase' refers to the structure of $b[n]$ defined in Eq. \eqref{eqn:pfb}.
+The term `polyphase' derives from the structure of $b[n]$ defined in Eq. \eqref{eqn:pfb}.
 It is illustrated in Fig. \ref{fig:pfb}.
@@
 \subsection{MWA implementation of the fine PFB}
+
+As the first stage
 

### 2019-10-18 filtercoeffs.py

@@ -1,0 +1,29 @@
+from scipy import kaiser
+import numpy as np
+import matplotlib.pyplot as plt
+
+fig, axs = plt.subplots(2)
+
+r = np.loadtxt("r.txt")
+rnorm = r/max(r)
+
+axs[0].plot(rnorm, label="True coefficients, normalised")
+
+ntaps = 12
+nsamps = 128
+N = ntaps*nsamps
+k = kaiser(N, 14)
+for a in [5, 6, 7, 8]:
+    axs[0].plot(kaiser(N,a), label="Kaiser {0}".format(a))
+
+x = (np.linspace(0, N, N, endpoint=False) - N/2 + 1)/N
+s = np.sinc(x*12)
+r1 = s*k
+axs[0].plot(s, label="Kaiser * sinc")
+axs[0].plot(rnorm/s, label="rnorm/sinc")
+
+axs[1].plot(r1 - rnorm, label="Residuals")
+
+axs[0].legend()
+axs[1].legend()
+plt.show()

### 2019-10-18 filtercoeffs.py
Still working on this filter script

@@ -1,4 +1,4 @@
-from scipy import kaiser
+from scipy import kaiser, hanning, hamming, bartlett, blackman
 import numpy as np
 import matplotlib.pyplot as plt
 
@@ -12,14 +12,19 @@ axs[0].plot(rnorm, label="True coefficients, normalised")
 ntaps = 12
 nsamps = 128
 N = ntaps*nsamps
-k = kaiser(N, 14)
-for a in [5, 6, 7, 8]:
-    axs[0].plot(kaiser(N,a), label="Kaiser {0}".format(a))
+a = 6
+k = kaiser(N, a)
+axs[0].plot(kaiser(N,a), label="Kaiser {0}".format(a))
+
+hn = hanning(N)
+hm = hamming(N)
+br = bartlett(N)
+bl = blackman(N)
 
 x = (np.linspace(0, N, N, endpoint=False) - N/2 + 1)/N
 s = np.sinc(x*12)
 r1 = s*k
-axs[0].plot(s, label="Kaiser * sinc")
+axs[0].plot(r1, label="Kaiser * sinc")
 axs[0].plot(rnorm/s, label="rnorm/sinc")
 
 axs[1].plot(r1 - rnorm, label="Residuals")

### 2019-10-21 ipfb.tex
Figured out the filter coefficients (at least, how to reproduce them), and wrote the section describing them

@@
 \usepackage{graphicx}
+
+\DeclareMathOperator{\sinc}{sinc}
 
@@
 
-As the first stage
+The first stage (coarse) PFB is described in \citet{Prabu2015}, and here we only document a few details pertaining to the second stage (fine) PFB.
+A PFB is completely specified by (1) the number of output channels, $N$, (2) the number of taps, $P$, and (3) the analysis filter, $h[m]$, $0 \le m < M=NP$.
+For the MWA, $N=128$ (giving fine channels $10\,$kHz wide), $P=12$, and
+\begin{equation}
+    h[m] = w_H[m]\,w_s[m],
+    \label{eqn:filter}
+\end{equation}
+where
+\begin{equation*}
+    w_H[m] = \sin\bigg(\frac{\pi (m+1)}{M+1}\bigg)
+\end{equation*}
+is the Hanning window, and
+\begin{equation*}
+    w_s[m] = \sin\bigg(\frac{\pi(m + 1 - M/2)}{N}\bigg)
+\end{equation*}
+is the stretched $\sinc$ function.
+It can be easily checked that $h[m]$ is defined to be symmetric around sample $m = 767 = M/2-1$.
+
+The above specifications yield a specific frequency response, as explained in the preceding section.
+The rationale behind these particular design choices is beyond the scope of this paper---for the purposes of creating a synthesis filter, it is sufficient to know merely how the analysis filter is defined\footnote{Eq.
+\eqref{eqn:filter} is defined on $\mathbb{R}$, but the actual implementation on the MWA's filed-programmable gate arrays (FPGAs) defines the analysis filter coefficients on $\mathbb{Z}$.
+The exact implemented values of $h[m]$ can be obtained by the operation $h[m] \rightarrow \lfloor\alpha h[m]\rceil$, where $\lfloor\cdot\rceil$ denotes rounding to the nearest integer and $\alpha = 117963.875$.}.
 

### 2019-10-21 filtercoeffs.py

@@ -1,33 +1,31 @@
-from scipy import kaiser, hanning, hamming, bartlett, blackman
+from scipy import hanning
 import numpy as np
 import matplotlib.pyplot as plt
 
 fig, axs = plt.subplots(2)
 
 r = np.loadtxt("r.txt")
-rnorm = r/max(r)
+rmax = max(r)
+print("max coefficient = {0}".format(rmax))
 
-axs[0].plot(rnorm, label="True coefficients, normalised")
+P = 12 # number of taps
+N = 128 # number of output channels
+M = N*P
 
-ntaps = 12
-nsamps = 128
-N = ntaps*nsamps
-a = 6
-k = kaiser(N, a)
-axs[0].plot(kaiser(N,a), label="Kaiser {0}".format(a))
+x = (np.linspace(0, M, M, endpoint=False) - M/2 + 1)/N
 
-hn = hanning(N)
-hm = hamming(N)
-br = bartlett(N)
-bl = blackman(N)
+s = np.sinc(x)
+hn = hanning(M+1)[1:]
+r1 = s*hn*(rmax-0.125)
+rounded = np.round(r1)
 
-x = (np.linspace(0, N, N, endpoint=False) - N/2 + 1)/N
-s = np.sinc(x*12)
-r1 = s*k
-axs[0].plot(r1, label="Kaiser * sinc")
-axs[0].plot(rnorm/s, label="rnorm/sinc")
+axs[0].plot(r, label="True coefficients")
+axs[0].plot(r1, label="Hanning * sinc")
 
-axs[1].plot(r1 - rnorm, label="Residuals")
+residuals = r1 - r
+axs[1].plot(residuals, label="Residuals")
+axs[1].plot(rounded - r, label="Rounded residuals")
+print("rounded residuals: min = {0};   max = {1}".format(min(r1-r), max(r1-r)))
 
 axs[0].legend()
 axs[1].legend()

### 2019-10-21 filtercoeffs.py
Added the filter coefficients figure for real

@@ -12,7 +12,8 @@ P = 12 # number of taps
 N = 128 # number of output channels
 M = N*P
 
-x = (np.linspace(0, M, M, endpoint=False) - M/2 + 1)/N
+m = np.linspace(0, M, M, endpoint=False)
+x = (m + 1 - M/2)/N
 
 s = np.sinc(x)
 hn = hanning(M+1)[1:]
@@ -30,3 +31,14 @@ print("rounded residuals: min = {0};   max = {1}".format(min(r1-r), max(r1-r)))
 axs[0].legend()
 axs[1].legend()
 plt.show()
+
+plt.plot(m, hn, 'k:', label="Hanning window")
+plt.plot(m, s, 'k--', label="Sinc function")
+plt.plot(m, s*hn, 'k-', label="Analysis filter")
+
+plt.xlabel("$m$")
+plt.ylabel("$h[m]$")
+plt.xlim([0,1536])
+
+plt.legend()
+plt.savefig("filter.eps")

### 2019-10-22 ipfb.tex
Fixed a typo or two, and added a placeholder image for the filter coefficients
Added the filter coefficients figure for real
Fixed another typo in one of the equations
A few tweaks to the existing text, for clarity

@@
 
+% There is some ambiguity about whether this definition includes the correct set of phases, which differ depending on whether the filterbank is defined on [0,M) or [-M/2, M/2).
+% It may turn out there is an extra phase ramp that's needed in Eq. \eqref{eqn:filter} below.
+% See Harris et al. (2011) for a fuller discussion of this point.
+
 \subsection{MWA implementation of the fine PFB}
@@
 \begin{equation*}
-    w_H[m] = \sin\bigg(\frac{\pi (m+1)}{M+1}\bigg)
+    w_H[m] = \sin^2\bigg(\frac{\pi (m+1)}{M+1}\bigg)
 \end{equation*}
@@
 \begin{equation*}
-    w_s[m] = \sin\bigg(\frac{\pi(m + 1 - M/2)}{N}\bigg)
+    w_s[m] = \sinc\bigg(\frac{\pi(m + 1 - M/2)}{N}\bigg)
 \end{equation*}
-is the stretched $\sinc$ function.
+is the scaled $\sinc(x) = \sin(x)/x$ function.
 It can be easily checked that $h[m]$ is defined to be symmetric around sample $m = 767 = M/2-1$.
+The analysis filter is shown in Fig. \ref{fig:filter}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{filter}
+    \caption{The coefficients of the analysis filter defined in Eq. \eqref{eqn:filter}, composed of a Hanning window multiplied to a $\sinc$ function.}
+    \label{fig:filter}
+\end{figure}
 
@@
 \eqref{eqn:filter} is defined on $\mathbb{R}$, but the actual implementation on the MWA's filed-programmable gate arrays (FPGAs) defines the analysis filter coefficients on $\mathbb{Z}$.
-The exact implemented values of $h[m]$ can be obtained by the operation $h[m] \rightarrow \lfloor\alpha h[m]\rceil$, where $\lfloor\cdot\rceil$ denotes rounding to the nearest integer and $\alpha = 117963.875$.}.
+The exact implemented values, $h^\ast[m]$, can be obtained from $h[m]$ via $h^\ast[m] \equiv \lfloor\alpha h[m]\rceil$, where $\lfloor\cdot\rceil$ denotes rounding to the nearest integer and $\alpha = 117963.875$.}.
 

### 2019-10-22 ipfb.tex
Improved the filter analysis plot

@@
     \includegraphics[width=\columnwidth]{filter}
-    \caption{The coefficients of the analysis filter defined in Eq. \eqref{eqn:filter}, composed of a Hanning window multiplied to a $\sinc$ function.}
+    \caption{Top: The coefficients of the analysis filter defined in Eq.
+\eqref{eqn:filter}, composed of a Hanning window multiplied to a $\sinc$ function.
+Bottom: The frequency response of the analysis filter, showing negligible attenuation across approximately $10\,$kHz (the bandwidth of a fine channel) and strong attenuation elsewhere.}
     \label{fig:filter}

### 2019-10-22 filtercoeffs.py

@@ -2,7 +2,7 @@ from scipy import hanning
 import numpy as np
 import matplotlib.pyplot as plt
 
-fig, axs = plt.subplots(2)
+fig, axs = plt.subplots(2, figsize=(5,7))
 
 r = np.loadtxt("r.txt")
 rmax = max(r)
@@ -20,6 +20,8 @@ hn = hanning(M+1)[1:]
 r1 = s*hn*(rmax-0.125)
 rounded = np.round(r1)
 
+'''
+# Plots to verify the constructed coefficients vs the actual coefficients.
 axs[0].plot(r, label="True coefficients")
 axs[0].plot(r1, label="Hanning * sinc")
 
@@ -31,14 +33,30 @@ print("rounded residuals: min = {0};   max = {1}".format(min(r1-r), max(r1-r)))
 axs[0].legend()
 axs[1].legend()
 plt.show()
+'''
 
-plt.plot(m, hn, 'k:', label="Hanning window")
-plt.plot(m, s, 'k--', label="Sinc function")
-plt.plot(m, s*hn, 'k-', label="Analysis filter")
+# Plots to go in the figure
+axs[0].plot(m, hn, 'k:', label="Hanning window")
+axs[0].plot(m, s, 'k--', label="Sinc function")
+axs[0].plot(m, s*hn, 'k-', label="Analysis filter")
 
-plt.xlabel("$m$")
-plt.ylabel("$h[m]$")
-plt.xlim([0,1536])
+axs[0].set_xlabel("$m$")
+axs[0].set_ylabel("$h[m]$")
+axs[0].set_xlim([0,1536])
 
-plt.legend()
+ctr = M//2 - 1
+k = (np.arange(M) - ctr)/P * 10 # i.e. 10 kHz
+fftr = np.roll(np.abs(np.fft.fft(s*hn)), ctr)
+dB = 10*np.log10(fftr/max(fftr))
+axs[1].plot(k, dB, 'k-')
+
+axs[1].set_xlabel("$\\nu$ (kHz)")
+axs[1].set_ylabel("Normalised power (dB)")
+axs[1].set_xlim([-30,30])
+axs[1].set_ylim([-60, 5])
+plt.grid(True)
+
+axs[0].legend(loc='upper right')
+#plt.show()
+plt.tight_layout()
 plt.savefig("filter.eps")

### 2019-10-22 ipfb.tex
A quick save of progress while I transition to my laptop. Wrote a few more sentences.

--- 2019-10-22 ipfb.tex
@@
 It is illustrated in Fig. \ref{fig:pfb}.
-\begin{figure}
+\begin{figure}[t]
     \centering
@@
 The analysis filter is shown in Fig. \ref{fig:filter}.
-\begin{figure}
+\begin{figure}[t]
     \centering
     \includegraphics[width=\columnwidth]{filter}
-    \caption{The coefficients of the analysis filter defined in Eq. \eqref{eqn:filter}, composed of a Hanning window multiplied to a $\sinc$ function.}
+    \caption{Top: The coefficients of the MWA's fine PFB analysis filter, defined in Eq.
+\eqref{eqn:filter}, which is composed of a Hanning window multiplied to a $\sinc$ function.
+Bottom: The frequency response of the analysis filter (black, solid), showing negligible attenuation across approximately $10\,$kHz (the bandwidth of a fine channel) and strong attenuation elsewhere.
+The frequency response is repeated for adjacent channels on either side (grey, dashed) showing crossover points at $-3\,$dB.}
     \label{fig:filter}
 \end{figure}
+
+The MWA fine PFB is \textit{critically sampled}, meaning that consecutive $100\,\mu$s output samples are obtained by applying the analysis filter to blocks of samples separated by the length of a tap, i.e.
+$N$ samples.
+This implies that each coarse channel sample becomes part of the input (i.e. a term in the sum) for $P$ consecutive fine channel samples.
+However, it should be noted that there is no redundant information.
+The term ``critically'' sampled is justified by noting that the downsampling by a factor of \dots inherent in the PFB algorithm is exactly balanced by the
 

### 2019-10-22 filtercoeffs.py

@@ -49,6 +49,8 @@ k = (np.arange(M) - ctr)/P * 10 # i.e. 10 kHz
 fftr = np.roll(np.abs(np.fft.fft(s*hn)), ctr)
 dB = 10*np.log10(fftr/max(fftr))
 axs[1].plot(k, dB, 'k-')
+for xshift in [-10, 10]:
+    axs[1].plot(k+xshift, dB, '--', color='#c0c0c0')
 
 axs[1].set_xlabel("$\\nu$ (kHz)")
 axs[1].set_ylabel("Normalised power (dB)")
@@ -57,6 +59,6 @@ axs[1].set_ylim([-60, 5])
 plt.grid(True)
 
 axs[0].legend(loc='upper right')
-#plt.show()
-plt.tight_layout()
-plt.savefig("filter.eps")
+plt.show()
+#plt.tight_layout()
+#plt.savefig("filter.eps")

### 2019-10-22 ipfb.tex
Added a paragraph about 'critically sampled' in the MWA implementation section.

@@
 
-The MWA fine PFB is \textit{critically sampled}, meaning that consecutive $100\,\mu$s output samples are obtained by applying the analysis filter to blocks of samples separated by the length of a tap, i.e.
-$N$ samples.
+The MWA fine PFB is \textit{critically sampled}, meaning that consecutive $100\,\mu$s output samples are obtained by applying the analysis filter to blocks of samples separated by the length of one tap, i.e.
+$N = 128$ samples.
 This implies that each coarse channel sample becomes part of the input (i.e. a term in the sum) for $P$ consecutive fine channel samples.
-However, it should be noted that there is no redundant information.
-The term ``critically'' sampled is justified by noting that the downsampling by a factor of \dots inherent in the PFB algorithm is exactly balanced by the
+The term ``critically'' sampled is justified by noting that the downsampling by a factor of $P$ (inherent in the PFB algorithm) is exactly counterbalanced by the inclusion of each coarse channel sample in $P$ distinct output channels, with a different weighting (filter coefficient and phase term) applied in each case.
+As discussed below, the fact that the PFB is critically sampled greatly informs the design of the synthesis filter used to reconstruct the coarse channel samples from the fine channels.
 
-The above specifications yield a specific frequency response, as explained in the preceding section.
 The rationale behind these particular design choices is beyond the scope of this paper---for the purposes of creating a synthesis filter, it is sufficient to know merely how the analysis filter is defined\footnote{Eq.
 \eqref{eqn:filter} is defined on $\mathbb{R}$, but the actual implementation on the MWA's filed-programmable gate arrays (FPGAs) defines the analysis filter coefficients on $\mathbb{Z}$.
-The exact implemented values, $h^\ast[m]$, can be obtained from $h[m]$ via $h^\ast[m] \equiv \lfloor\alpha h[m]\rceil$, where $\lfloor\cdot\rceil$ denotes rounding to the nearest integer and $\alpha = 117963.875$.}.
+The exact implemented values, $h^\ast[m]$, can be obtained from $h[m]$ via $h^\ast[m] \equiv \lfloor\alpha h[m]\rceil$, where $\lfloor\cdot\rceil$ denotes rounding to the nearest integer and $\alpha = 117963.875$.}, and the fact that the PFB is critically sampled.
 

### 2019-10-22 filtercoeffs.py

@@ -59,6 +59,6 @@ axs[1].set_ylim([-60, 5])
 plt.grid(True)
 
 axs[0].legend(loc='upper right')
-plt.show()
-#plt.tight_layout()
-#plt.savefig("filter.eps")
+#plt.show()
+plt.tight_layout()
+plt.savefig("filter.eps")

### 2019-10-23 ipfb.tex
Started changing the notation to be more in line with Crochiere. I think this will help in the description of the synthesis filter.

@@
 spectral leakage) inherent in the application of DFTs to discretely sampled time series of finite length.
-They are well described in standard texts \citep{Crochiere1983,Harris2004,Oppenheim2009}; a clear and concise review of PFBs in the context of radio astronomy is given in \citet{Harris2011}, whose notation is closely followed here.
+They are well described in standard texts \citep{Crochiere1983,Harris2004,Oppenheim2009}; a clear and concise review of PFBs in the context of radio astronomy is given in \citet{Harris2011}.
 Thus, only a brief review of the salient features is given, in order to prepare the reader for the description of the synthesis filter in the following sections.
@@
 \begin{equation}
-    X[k] = \sum_{n=0}^{N-1} h[n]\,x[n]\,e^{-2\pi j k (n/N)},
+    X_k[m] = \sum_{n=0}^{K-1} h[n]\,x[n+mM]\,e^{-2\pi jkn/K},
     \label{eqn:wdft}
 \end{equation}
-where $j = \sqrt{-1}$ denotes the imaginary number, and it is understood that $0 \le k < N$.
+where $j = \sqrt{-1}$ denotes the imaginary number, $m$ is the time index of the channelised (output) data, and $0 \le k < K$ denotes the (fine) channel number.
+Eq. \eqref{eqn:wdft} describes the action of performing DFTs on short, windowed segments of the input time series of length $K$.
+$M$ is the amount that the window is slid along $x[n]$ between successive DFT operations.
+If $M < K$ then the windows overlap and the resulting channelisation is \textit{oversampled}; if $M = K$, then it is \textit{critically sampled}.
 The choice of $h[n]$ is motivated by the shape of its \textit{frequency response} (i.e.
@@
 The first stage (coarse) PFB is described in \citet{Prabu2015}, and here we only document a few details pertaining to the second stage (fine) PFB.
-A PFB is completely specified by (1) the number of output channels, $N$, (2) the number of taps, $P$, and (3) the analysis filter, $h[m]$, $0 \le m < M=NP$.
+A PFB is specified by (1) the number of output channels, $N$, (2) the number of taps, $P$, and (3) the analysis filter, $h[m]$, $0 \le m < M = NP = 1536$.
 For the MWA, $N=128$ (giving fine channels $10\,$kHz wide), $P=12$, and
@@
 Bottom: The frequency response of the analysis filter (black, solid), showing negligible attenuation across approximately $10\,$kHz (the bandwidth of a fine channel) and strong attenuation elsewhere.
-The frequency response is repeated for adjacent channels on either side (grey, dashed) showing crossover points at $-3\,$dB.}
+The frequency response is repeated for adjacent channels on either side (grey, dashed) showing crossover points on the channel edges at $-3\,$dB.}
     \label{fig:filter}
@@
 
-The MWA fine PFB is \textit{critically sampled}, meaning that consecutive $100\,\mu$s output samples are obtained by applying the analysis filter to blocks of samples separated by the length of one tap, i.e.
+The MWA's fine PFB is \textit{critically sampled}, meaning that consecutive $100\,\mu$s output samples are obtained by applying the analysis filter to blocks of samples separated by the length of one tap, i.e.
 $N = 128$ samples.
@@
 The term ``critically'' sampled is justified by noting that the downsampling by a factor of $P$ (inherent in the PFB algorithm) is exactly counterbalanced by the inclusion of each coarse channel sample in $P$ distinct output channels, with a different weighting (filter coefficient and phase term) applied in each case.
-As discussed below, the fact that the PFB is critically sampled greatly informs the design of the synthesis filter used to reconstruct the coarse channel samples from the fine channels.
+As discussed below, the fact that the PFB is critically sampled informs the design of the synthesis filter used to reconstruct the coarse channel samples from the fine channels.
 
-The rationale behind these particular design choices is beyond the scope of this paper---for the purposes of creating a synthesis filter, it is sufficient to know merely how the analysis filter is defined\footnote{Eq.
+The rationale behind the particular design choices for the MWA's fine PFB is beyond the scope of this paper---for the purposes of creating a synthesis filter, it is sufficient to know merely how the analysis filter is defined\footnote{Eq.
 \eqref{eqn:filter} is defined on $\mathbb{R}$, but the actual implementation on the MWA's filed-programmable gate arrays (FPGAs) defines the analysis filter coefficients on $\mathbb{Z}$.

### 2019-10-23 ipfb.tex
Finished(?) changing notation throughout

@@
 
-Like the DFT, the PFB is a transformation from the time domain, $x[n]$, to the frequency domain $X[k]$, where the $[\cdot]$ notation denotes a discretised index, and where $n,k \in \mathbb{Z}$ are the indices for time and frequency, respectively.
-Let $N$ be the number of (equally spaced) frequency channels required for some desired spectral resolution.
-Although applying a DFT to $N$ adjacent time samples will produce the desired resolution, the result will be an imperfect representation of the true spectral content of $x[n]$ because of \textit{spectral leakage}, which is when power that properly `belongs' to some particular frequency bin appears in (or, is \textit{aliased} to) other, nearby bins.
+The PFB is a transformation from the time domain, $x[n]$, to the frequency domain $X_k[m]$, where the $[\cdot]$ notation denotes a discretised index, $k$ is the channel number, and $n,m \in \mathbb{Z}$ are the time indices for the pre- and post-channelised data, respectively.
+Let $K$ be the number of (equally spaced) frequency channels required for some desired spectral resolution.
+Although applying a DFT to $N = K$ adjacent time samples in $x[n]$ will produce the desired resolution, the result will be an imperfect representation of the true spectrum because of \textit{spectral leakage}, which is when power that properly `belongs' to some particular frequency bin appears in (or, is \textit{aliased} to) other, nearby bins.
 The impossibility of perfectly eliminating spectral leakage can be seen by realising that operating on a finite-length time series is equivalent to multiplying an arbitrarily long time series with a rectangular window function,
@@
 \begin{equation}
-    X_k[m] = \sum_{n=0}^{K-1} h[n]\,x[n+mM]\,e^{-2\pi jkn/K},
+    X_k[m] = \sum_{n=0}^{N-1} h[n]\,x[n+mM]\,e^{-2\pi jkn/K},
     \label{eqn:wdft}
 \end{equation}
-where $j = \sqrt{-1}$ denotes the imaginary number, $m$ is the time index of the channelised (output) data, and $0 \le k < K$ denotes the (fine) channel number.
+where $j = \sqrt{-1}$ denotes the imaginary number, $m$ is the time index of the channelised (output) data, and $0 \le k < K$ denotes the channel number.
 Eq. \eqref{eqn:wdft} describes the action of performing DFTs on short, windowed segments of the input time series of length $K$.
@@
 its Fourier pair), whose characteristics (e.g.
-width, location of sidelobes) might carry particular advantages in certain contexts.
-Note that leaving $x[n]$ ``unweighted'' is equivalent to choosing $h[n] = w_R[n]$.
+width, location of sidelobes) are chosen according to the advantages they carry in particular contexts.
+Leaving $x[n]$ ``unweighted'' is equivalent to choosing $h[n] = w_R[n]$, in which case Eq. \eqref{eqn:wdft} is also called the short-time Fourier transform (STFT).
+On the other hand, choosing $h[n]$ to be the $\sinc$ function will result in a frequency response that approximates a rectangular window.
 
@@
 This fact motivates an alternative strategy for mitigating spectral leakage.
-If more samples are available, say $M = NP$ for $P > 1$, then stretching (i.e.
-scaling and upsampling) the analysis filter will result in a frequency response function that is similar in shape, but $P$ times narrower than the original analysis filter.
-Applying the DFT to the larger set of windowed samples and subsequently \emph{downsampling} the resulting spectrum (by choosing every $P$th frequency bin and rejecting the rest) ensures that the original desired spectral resolution is retained, but with significantly less spectral leakage.
+Choosing a larger window size, $N = KP$ (for integer $P > 1$), and a corresponding wider analysis filter, will result in a frequency response function that is similar in shape, but $P$ times narrower than the original analysis filter.
+A DFT applied to the larger number of samples will naturally produce a correspondingly larger number of frequency channels, but choosing only every $P$th channel and discarding the rest (known as \textit{decimation}) ensures that the desired spectral resolution with $K$ channels is retained.
+In this way, spectral leakage can be contained arbitrarily close to the ``correct'' channel by choosing a sufficiently high value of $P$.
 
-The algorithm embodied in the above strategy defines the PFB.
-It is clear that choosing a larger value for $P$ will lessen spectral leakage by the same factor, but this naturally comes at a greater computational cost, since the DFT is now applied to $M$ samples.
-However, one of the great advantages of the PFB is that the above operations of using a wider analysis wilter and downsampling the resulting spectrum are mathematically equivalent to first segmenting the windowed time series into $P$ segments (known as `taps') of size $N$, summing their respective samples element-wise, and performing a single DFT on the resulting array (now of size $N$), i.e.
+The two-step algorithm described above (performing a windowed DFT on $N = KP$ samples and decimating the resulting spectrum) defines the PFB.
+Formally, it is equivalent to Eq. \eqref{eqn:wdft}; however, the term \textit{critically sampled} (i.e. $M = K$) implies that the $N$-length windows will now overlap.
+The term ``polyphase'' derives from the fact that each block of $K = N/P$ samples (knows as \textit{taps}) in $x[n]$ is included in multiple applications of the DFT, but appearing at a different relative phase in each case.
+
+One of the great advantages of the PFB is the existence of a mathematically equivalent but computationally efficient implementation.
+It can be shown that Eq.
+\eqref{eqn:wdft} is equivalent to first segmenting the windowed time series into taps, summing their respective samples element-wise, and performing a single DFT on the resulting array (now also of size $K$), i.e.
 \begin{equation}
-    X[k] = \sum_{n=0}^{N-1} b[n]\,e^{-2\pi j k (n/N)},
+    X_k[m] = \sum_{n=0}^{K-1} b[n]\,e^{-2\pi jkn/K},
     \label{eqn:pfb}
@@
 \begin{equation*}
-    b[n] = \sum_{\rho=0}^{P-1} h[n + N\rho]\,x[n + N\rho].
+    b[n] = \sum_{\rho=0}^{P-1} h[n + K\rho]\,x[n + mM + K\rho].
 \end{equation*}
-A short proof of the equivalence of this expression with the algorithm described above is given in \citet{Harris2011}.
-The term `polyphase' derives from the structure of $b[n]$ defined in Eq. \eqref{eqn:pfb}.
-It is illustrated in Fig. \ref{fig:pfb}.
+A short proof of this is given in \citet{Harris2011}.
+Eq. \eqref{eqn:pfb} is illustrated in Fig. \ref{fig:pfb}.
 \begin{figure}[t]
@@
 The first stage (coarse) PFB is described in \citet{Prabu2015}, and here we only document a few details pertaining to the second stage (fine) PFB.
-A PFB is specified by (1) the number of output channels, $N$, (2) the number of taps, $P$, and (3) the analysis filter, $h[m]$, $0 \le m < M = NP = 1536$.
-For the MWA, $N=128$ (giving fine channels $10\,$kHz wide), $P=12$, and
+A PFB is specified by (1) the number of output channels, $K$, (2) the number of taps, $P$, and (3) the analysis filter, $h[n]$.
+For the MWA, $K = 128$ (giving fine channels $10\,$kHz wide), $P = 12$, and
 \begin{equation}
-    h[m] = w_H[m]\,w_s[m],
+    h[n] = w_H[n]\,w_s[n],
     \label{eqn:filter}
@@
 \begin{equation*}
-    w_H[m] = \sin^2\bigg(\frac{\pi (m+1)}{M+1}\bigg)
+    w_H[n] = \sin^2\bigg(\frac{\pi (n+1)}{N+1}\bigg)
 \end{equation*}
@@
 \begin{equation*}
-    w_s[m] = \sinc\bigg(\frac{\pi(m + 1 - M/2)}{N}\bigg)
+    w_s[n] = \sinc\bigg(\frac{\pi(n + 1 - N/2)}{K}\bigg)
 \end{equation*}
@@
 \end{figure}
-
-The MWA's fine PFB is \textit{critically sampled}, meaning that consecutive $100\,\mu$s output samples are obtained by applying the analysis filter to blocks of samples separated by the length of one tap, i.e.
-$N = 128$ samples.
-This implies that each coarse channel sample becomes part of the input (i.e. a term in the sum) for $P$ consecutive fine channel samples.
-The term ``critically'' sampled is justified by noting that the downsampling by a factor of $P$ (inherent in the PFB algorithm) is exactly counterbalanced by the inclusion of each coarse channel sample in $P$ distinct output channels, with a different weighting (filter coefficient and phase term) applied in each case.
-As discussed below, the fact that the PFB is critically sampled informs the design of the synthesis filter used to reconstruct the coarse channel samples from the fine channels.
-
+The MWA's fine PFB is critically sampled, with $M = K = 128$.
 The rationale behind the particular design choices for the MWA's fine PFB is beyond the scope of this paper---for the purposes of creating a synthesis filter, it is sufficient to know merely how the analysis filter is defined\footnote{Eq.
 \eqref{eqn:filter} is defined on $\mathbb{R}$, but the actual implementation on the MWA's filed-programmable gate arrays (FPGAs) defines the analysis filter coefficients on $\mathbb{Z}$.
-The exact implemented values, $h^\ast[m]$, can be obtained from $h[m]$ via $h^\ast[m] \equiv \lfloor\alpha h[m]\rceil$, where $\lfloor\cdot\rceil$ denotes rounding to the nearest integer and $\alpha = 117963.875$.}, and the fact that the PFB is critically sampled.
+The exact implemented values, $h^\ast[n]$, can be obtained from $h[n]$ via $h^\ast[n] \equiv \lfloor\alpha h[n]\rceil$, where $\lfloor\cdot\rceil$ denotes rounding to the nearest integer and $\alpha = 117963.875$.}, and the fact that the PFB is critically sampled.
 

### 2019-10-23 ipfb.tex
Some minor tweaks for clarity

@@
 \begin{equation}
-    X_k[m] = \sum_{n=0}^{N-1} h[n]\,x[n+mM]\,e^{-2\pi jkn/K},
+    X_k[m] = \sum_{n=0}^{N-1} h[mM - n]\,x[n]\,e^{-2\pi jkn/K},
     \label{eqn:wdft}
@@
 Eq. \eqref{eqn:wdft} describes the action of performing DFTs on short, windowed segments of the input time series of length $K$.
-$M$ is the amount that the window is slid along $x[n]$ between successive DFT operations.
+$M$ is the number of samples that the window is translated along $x[n]$ between successive DFT operations; thus, the index of $h[mM - n]$ represents the amount the filter must be translated in order to produce the spectrum at time $m$.
 If $M < K$ then the windows overlap and the resulting channelisation is \textit{oversampled}; if $M = K$, then it is \textit{critically sampled}.
@@
 \end{equation*}
-A short proof of this is given in \citet{Harris2011}.
+A short proof of this equivalence is given in \citet{Harris2011}.
 Eq. \eqref{eqn:pfb} is illustrated in Fig. \ref{fig:pfb}.

### 2019-10-23 ipfb.tex
A few trivial textual changes to ipfb.tex; a change of variable names in filtercoeffs.py

@@
 Eq. \eqref{eqn:wdft} describes the action of performing DFTs on short, windowed segments of the input time series of length $K$.
-$M$ is the number of samples that the window is translated along $x[n]$ between successive DFT operations; thus, the index of $h[mM - n]$ represents the amount the filter must be translated in order to produce the spectrum at time $m$.
+$M$ is the number of samples that the window is translated along $x[n]$ between successive DFT operations; thus, the index of $h[mM - n]$ represents the shift required in order to produce the spectrum at time $m$.
 If $M < K$ then the windows overlap and the resulting channelisation is \textit{oversampled}; if $M = K$, then it is \textit{critically sampled}.
@@
 
-One of the great advantages of the PFB is the existence of a mathematically equivalent but computationally efficient implementation.
+One of the great advantages of the critically sampled PFB is the existence of a mathematically equivalent but computationally efficient implementation.
 It can be shown that Eq.

### 2019-10-23 filtercoeffs.py

@@ -2,23 +2,23 @@ from scipy import hanning
 import numpy as np
 import matplotlib.pyplot as plt
 
-fig, axs = plt.subplots(2, figsize=(5,7))
-
 r = np.loadtxt("r.txt")
 rmax = max(r)
 print("max coefficient = {0}".format(rmax))
 
 P = 12 # number of taps
-N = 128 # number of output channels
-M = N*P
+K = 128 # number of output channels
+N = K*P
 
-m = np.linspace(0, M, M, endpoint=False)
-x = (m + 1 - M/2)/N
+m = np.linspace(0, N, N, endpoint=False)
+x = (m + 1 - N/2)/K
 
 s = np.sinc(x)
-hn = hanning(M+1)[1:]
+hn = hanning(N+1)[1:]
 r1 = s*hn*(rmax-0.125)
 rounded = np.round(r1)
+
+fig, axs = plt.subplots(2, figsize=(5,7))
 
 '''
 # Plots to verify the constructed coefficients vs the actual coefficients.
@@ -44,13 +44,13 @@ axs[0].set_xlabel("$m$")
 axs[0].set_ylabel("$h[m]$")
 axs[0].set_xlim([0,1536])
 
-ctr = M//2 - 1
-k = (np.arange(M) - ctr)/P * 10 # i.e. 10 kHz
+ctr = N//2 - 1
+f = (np.arange(N) - ctr)/P * 10 # i.e. 10 kHz
 fftr = np.roll(np.abs(np.fft.fft(s*hn)), ctr)
 dB = 10*np.log10(fftr/max(fftr))
-axs[1].plot(k, dB, 'k-')
-for xshift in [-10, 10]:
-    axs[1].plot(k+xshift, dB, '--', color='#c0c0c0')
+axs[1].plot(f, dB, 'k-')
+for fshift in [-10, 10]:
+    axs[1].plot(f + fshift, dB, '--', color='#c0c0c0')
 
 axs[1].set_xlabel("$\\nu$ (kHz)")
 axs[1].set_ylabel("Normalised power (dB)")

### 2019-10-23 filtercoeffs.py
Put the filter coefficients function into a python function in filtercoeffs.py

@@ -6,16 +6,27 @@ r = np.loadtxt("r.txt")
 rmax = max(r)
 print("max coefficient = {0}".format(rmax))
 
+def create_fine_PFB_filter(nchans, ntaps):
+
+    P = ntaps # number of taps
+    K = nchans # number of output channels
+    N = nchans*ntaps
+
+    m = np.linspace(0, N, N, endpoint=False)
+    x = (m + 1 - N/2)/nchans
+
+    sinc = np.sinc(x)
+    hn   = hanning(N+1)[1:]
+    h    = sinc*hn
+    return h, m, hn, sinc
+
 P = 12 # number of taps
 K = 128 # number of output channels
-N = K*P
+N = K*P # size of filter
 
-m = np.linspace(0, N, N, endpoint=False)
-x = (m + 1 - N/2)/K
+h, m, hn, s = create_fine_PFB_filter(K, P)
 
-s = np.sinc(x)
-hn = hanning(N+1)[1:]
-r1 = s*hn*(rmax-0.125)
+r1 = h*(rmax-0.125)
 rounded = np.round(r1)
 
 fig, axs = plt.subplots(2, figsize=(5,7))

### 2019-10-23 ipfb_test.py
Added Steve Ord's python script for testing the PFB inversion (edited by me). I will have to alter it to use the correct coefficients (instead of the Kaiser filter that Steve implemented) in order to do proper tests.

@@ -1,0 +1,386 @@
+#!/usr/bin/env python
+# coding: utf-8
+
+# # Create a signal for demonstrating the PFB and its "inversion"
+
+# In[1]:
+
+
+from numpy import sin, arange, pi, shape, log10, zeros
+
+import scipy
+from scipy.signal import lfilter, firwin,kaiser,kaiser_beta
+from matplotlib import pyplot as plt
+
+from random import random, gauss
+from numpy.fft import fft, ifft, fftshift, ifftshift, fftfreq
+import numpy as np
+import math
+import cmath
+
+
+# In[2]:
+
+
+def db(x):
+    """ Convert linear value to dB value """
+    return 10*log10(x)
+
+
+# In[3]:
+
+
+def inv_dft(input,chan):
+  output=[]
+  stfft = input[0:chan]
+  stfft=ifftshift(stfft);
+  out=ifft(stfft)
+  for samp in out:
+    output.append(samp)
+  return output
+
+
+# In[4]:
+
+
+def plot_power(t,amps,keyname="power"):
+    power = [abs(s)**2 for s in amps]
+    plt.plot(t[:len(power)],power,label = keyname)
+    plt.xlabel("Time (s)")
+    plt.ylabel("Power")
+    plt.legend(loc='upper right')
+
+
+# ----------------
+# ## Make a signal:
+
+# In[5]:
+
+
+# Set up the signal properties
+
+nchan = 32
+ntaps = 8
+
+nsamp = 10000
+nsamples = nsamp*nchan
+sample_rate = nchan*nsamp
+
+
+# In[6]:
+
+
+def make_signal(nsamples,sample_rate):
+    """Makes a signal composed of complex-valued white noise"""
+    t = []
+    signal = []
+    for i in range (0,nsamples,1):
+        t.append(i * 1.0/sample_rate)
+        signal.append(complex(gauss(0.0,1.0),gauss(0.0,1.0)))
+    
+    return t, signal
+
+
+# In[7]:
+
+
+# Make random noise
+t, noise = make_signal(nsamples,sample_rate)
+
+# Plot it up
+plt.figure(figsize=(15,5))
+plot_power(t, noise, "Random Noise ({:d} samples)".format(nsamples))
+
+
+# In[8]:
+
+
+# Add an impulse to the noise signal
+
+def add_impulse (step,width,scale,signal):
+    """ This is multiplicative. I am increasing the power in the specified range """
[…]

### 2019-10-23 ipfb.tex
Changed wording for clarity

@@
 This fact motivates an alternative strategy for mitigating spectral leakage.
-Choosing a larger window size, $N = KP$ (for integer $P > 1$), and a corresponding wider analysis filter, will result in a frequency response function that is similar in shape, but $P$ times narrower than the original analysis filter.
+Choosing a larger window size, $N = KP$ (for integer $P > 1$), and a corresponding wider analysis filter, will result in a frequency response that is similar in shape, but $P$ times narrower than the frequency response of the original analysis filter.
 A DFT applied to the larger number of samples will naturally produce a correspondingly larger number of frequency channels, but choosing only every $P$th channel and discarding the rest (known as \textit{decimation}) ensures that the desired spectral resolution with $K$ channels is retained.

### 2019-10-29 ipfb.tex
Fixed a few typos. Added extra authors, Brad M. and Steve T.

@@
 
-\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$
+\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$, B. W. Meyers, S. E. Tremblay
 \affil{$^1$International Centre for Radio Astronomy Research (ICRAR), GPO Box U1987, Perth, WA 6845, Australia}%
@@
 %%%%%%% IMPORTANT: We disable hyperlinks by default with this line, to avoid the error "\pdfendlink ended up in different nesting level" while writing.
-\hypersetup{draft}
+%\hypersetup{draft}
 %%%%%%% You may comment or delete the line above to make hyperlinks in your paper active.
@@
 Formally, it is equivalent to Eq. \eqref{eqn:wdft}; however, the term \textit{critically sampled} (i.e. $M = K$) implies that the $N$-length windows will now overlap.
-The term ``polyphase'' derives from the fact that each block of $K = N/P$ samples (knows as \textit{taps}) in $x[n]$ is included in multiple applications of the DFT, but appearing at a different relative phase in each case.
+The term ``polyphase'' derives from the fact that each block of $K = N/P$ samples (known as \textit{taps}) in $x[n]$ is included in multiple applications of the DFT, but appearing at a different relative phase in each case.
 
@@
 A short proof of this equivalence is given in \citet{Harris2011}.
-Eq. \eqref{eqn:pfb} is illustrated in Fig. \ref{fig:pfb}.
+The procedure described by Eq. \eqref{eqn:pfb} is illustrated in Fig. \ref{fig:pfb}.
 \begin{figure}[t]
@@
 is the scaled $\sinc(x) = \sin(x)/x$ function.
-It can be easily checked that $h[m]$ is defined to be symmetric around sample $m = 767 = M/2-1$.
+It can be easily checked that $h[n]$ is defined to be symmetric around sample $n = 767 = N/2-1$.
 The analysis filter is shown in Fig. \ref{fig:filter}.

### 2019-10-29 filtercoeffs.py
Changed labels in the filter figure.

@@ -12,19 +12,19 @@ def create_fine_PFB_filter(nchans, ntaps):
     K = nchans # number of output channels
     N = nchans*ntaps
 
-    m = np.linspace(0, N, N, endpoint=False)
-    x = (m + 1 - N/2)/nchans
+    n = np.linspace(0, N, N, endpoint=False)
+    x = (n + 1 - N/2)/nchans
 
     sinc = np.sinc(x)
     hn   = hanning(N+1)[1:]
     h    = sinc*hn
-    return h, m, hn, sinc
+    return h, n, hn, sinc
 
 P = 12 # number of taps
 K = 128 # number of output channels
 N = K*P # size of filter
 
-h, m, hn, s = create_fine_PFB_filter(K, P)
+h, n, hn, s = create_fine_PFB_filter(K, P)
 
 r1 = h*(rmax-0.125)
 rounded = np.round(r1)
@@ -47,12 +47,12 @@ plt.show()
 '''
 
 # Plots to go in the figure
-axs[0].plot(m, hn, 'k:', label="Hanning window")
-axs[0].plot(m, s, 'k--', label="Sinc function")
-axs[0].plot(m, s*hn, 'k-', label="Analysis filter")
+axs[0].plot(n, hn, 'k:', label="Hanning window")
+axs[0].plot(n, s, 'k--', label="Sinc function")
+axs[0].plot(n, s*hn, 'k-', label="Analysis filter")
 
-axs[0].set_xlabel("$m$")
-axs[0].set_ylabel("$h[m]$")
+axs[0].set_xlabel("$n$")
+axs[0].set_ylabel("$h[n]$")
 axs[0].set_xlim([0,1536])
 
 ctr = N//2 - 1

### 2019-12-02 filtercoeffs.py
Added scripts for a few more images to be included in the paper.

@@ -72,4 +72,4 @@ plt.grid(True)
 axs[0].legend(loc='upper right')
 #plt.show()
 plt.tight_layout()
-plt.savefig("filter.eps")
+plt.savefig("filter.eps", bbox_inches='tight')

### 2019-12-02 inverse_condition.py

@@ -1,0 +1,34 @@
+import numpy as np
+import matplotlib.pyplot as plt
+
+ntaps = 12
+K = 128
+N = ntaps*K
+M = K  # meaning "ciritically sampled"
+
+ns = np.arange(N)
+
+def wH(n):
+    return np.sin(np.pi*(n+1)/(N+1))**2
+
+def ws(n):
+    return np.sinc((n+1-N/2)/K)
+
+def h(n):
+    return wH(n)*ws(n)*np.logical_and(n >= 0, n < N)
+
+# Choose the synthesis filter
+def f(n):
+    return h(n)
+
+res = []
+
+H = np.sum(h(ns))
+
+ss = np.arange(-12,13)
+res = np.array([sum((1/H) * f(ns) * h(ns + s*M)) for s in ss])
+
+plt.plot(ss, res, '-x')
+plt.xlabel("$s$")
+plt.ylabel("$\\lambda(s)$")
+plt.savefig("inverse_condition.eps", bbox_inches='tight')

### 2019-12-02 pre_fft_distributions.py

@@ -1,0 +1,96 @@
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib.lines import Line2D
+
+# Generate random "5-bit" values
+N = 1000
+X = np.random.randn(N,1536)*2
+X5 = np.round(X)
+
+# Get the filter coefficients
+coeffs = np.loadtxt("r.txt")
+
+# Perform the window-overlap-add
+filtered = np.reshape(X5*coeffs, (N*1536//12, 12)).transpose()
+polyphased = np.sum(filtered, axis=0)
+
+# Demote the result to 8 bits using the weird rounding scheme
+reduced = polyphased/2**14
+pos_mask = (reduced > 0)
+demoted_symmetric = np.round(reduced)
+demoted = demoted_symmetric*pos_mask + np.floor(reduced)*np.logical_not(pos_mask)
+#diff = demoted_symmetric - demoted
+demoted_all = np.array([demoted_symmetric, demoted]).transpose()
+
+# Calculate (and print out) some means
+orig_mean = np.mean(X5)
+sym_mean  = np.mean(demoted_symmetric)
+asym_mean = np.mean(demoted)
+print("Mean of original 5-bit samples: {0}".format(orig_mean))
+print("Mean of  symmetrically-rounded 8-bit samples: {0}".format(sym_mean))
+print("Mean of asymmetrically-rounded 8-bit samples: {0}".format(asym_mean))
+
+# Make plots
+fig, ax = plt.subplots(2,1)
+fig.set_size_inches([5.0, 7.0])
+
+# Create a small example to demostrate the rounding scheme used in the FPGAs
+x0 = np.arange(-5.5, 5.5)
+x0 = np.array([x0, x0+1])
+y  = np.arange(-5, 6)
+y  = np.array([y, y])
+
+y_offset = 0.2
+y0 = y + 0.2
+y1 = y - 0.2
+
+x1 = np.array([[-5, -4, -3, -2, -1, 0,   0.5, 1.5, 2.5, 3.5, 4.5],
+               [-4, -3, -2, -1,  0, 0.5, 1.5, 2.5, 3.5, 4.5, 5.5]])
+
+x0_open   = np.arange(-5.5, 6.5)
+y0_open   = np.array([-5, -4, -3, -2, -1, 0, 0, 1, 2, 3, 4, 5]) + y_offset
+x0_closed = np.arange(-4.5, 5.5)
[…]

### 2019-12-02 inverse_condition.py
Working on a 'simple' impulse response test for my toy filter pair (see inverse_condition.py)

@@ -1,13 +1,13 @@
 import numpy as np
 import matplotlib.pyplot as plt
 
+# Parameters for PFB
 ntaps = 12
 K = 128
 N = ntaps*K
 M = K  # meaning "ciritically sampled"
 
-ns = np.arange(N)
-
+# Choose the analysis filter
 def wH(n):
     return np.sin(np.pi*(n+1)/(N+1))**2
 
@@ -19,16 +19,38 @@ def h(n):
 
 # Choose the synthesis filter
 def f(n):
-    return h(n)
+    H = np.sum(h(ns))
+    return h(n)/H
 
-res = []
-
-H = np.sum(h(ns))
-
+# Calculate λ(s) from h[n] and f[n]
+ns = np.arange(N)
 ss = np.arange(-12,13)
-res = np.array([sum((1/H) * f(ns) * h(ns + s*M)) for s in ss])
+lmda = np.array([sum(f(ns) * h(ns + s*M)) for s in ss])
 
-plt.plot(ss, res, '-x')
+# Analysis-synthesis response of an impulse
+nsamples = K*64
+x_ntaps  = nsamples//K - ntaps
+x = np.zeros(nsamples)
+x[nsamples//3] = 1 # Put an impulse right smack bang in the middle
+ns = np.arange(nsamples)
+
+X = np.array([[np.sum(h(m*M-ns) * x * np.exp(-2j*np.pi*k*ns/K)) for m in range(x_ntaps)] for k in range(K)])
+
+#ks = np.arange(K)
+#xhat = ([f(ns-m*M) / K * np.sum(X[:,m] * np.exp(2j*np.pi*ks*n/K)) for m in range(x_ntaps)])
+#print(xhat.shape)
+
+plt.figure(1)
+plt.imshow(np.abs(X))
+plt.colorbar()
+plt.figure(2)
+plt.imshow(np.angle(X), cmap='hsv')
+plt.colorbar()
+plt.show()
+
+# Make plots
+plt.plot(ss, lmda, '-xk')
+plt.ylim([-0.1, 1.0])
 plt.xlabel("$s$")
 plt.ylabel("$\\lambda(s)$")
 plt.savefig("inverse_condition.eps", bbox_inches='tight')

### 2019-12-02 inverse_condition.py
Still trying to figure out how to do the (toy) PFB inverse in python

@@ -33,19 +33,25 @@ x_ntaps  = nsamples//K - ntaps
 x = np.zeros(nsamples)
 x[nsamples//3] = 1 # Put an impulse right smack bang in the middle
 ns = np.arange(nsamples)
+x = np.cos(2*ns)
 
 X = np.array([[np.sum(h(m*M-ns) * x * np.exp(-2j*np.pi*k*ns/K)) for m in range(x_ntaps)] for k in range(K)])
+X = np.roll(X, K//2, axis=0)
 
-#ks = np.arange(K)
-#xhat = ([f(ns-m*M) / K * np.sum(X[:,m] * np.exp(2j*np.pi*ks*n/K)) for m in range(x_ntaps)])
-#print(xhat.shape)
+ks = np.arange(K)
+ms = np.arange(x_ntaps)
+NS, KS, MS = np.meshgrid(ns, ks, ms)
+#xhat = [np.sum([f(n-m*M) / K * np.sum(X[:,m] * np.exp(2j*np.pi*ks*n/K)) for m in range(x_ntaps)]) for n in ns]
+xhat = f(NS-MS*M) / K
+print(xhat.shape)
 
-plt.figure(1)
-plt.imshow(np.abs(X))
-plt.colorbar()
-plt.figure(2)
-plt.imshow(np.angle(X), cmap='hsv')
-plt.colorbar()
+'''
+fig, ax = plt.subplots(3,1)
+im1 = ax[0].imshow(np.abs(X), aspect='auto')
+im2 = ax[1].imshow(np.angle(X), cmap='hsv', aspect='auto')
+im3 = ax[2].plot(x)
+#plt.colorbar(im1)
+#plt.colorbar(im2)
 plt.show()
 
 # Make plots
@@ -54,3 +60,5 @@ plt.ylim([-0.1, 1.0])
 plt.xlabel("$s$")
 plt.ylabel("$\\lambda(s)$")
 plt.savefig("inverse_condition.eps", bbox_inches='tight')
+plt.show()
+'''

### 2019-12-03 ipfb.tex
Saving the latest version (from overleaf)

@@
 \DeclareMathOperator{\sinc}{sinc}
+\newcommand{\Kron}{\delta_s^0}
+\newcommand{\vcstools}{VCSTools}
+\newcommand{\bname}{B0950$+$08}
+\newcommand{\jname}{J0953$+$0755}
 
@@
 
-\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$, B. W. Meyers, S. E. Tremblay
+\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$, B. W. Meyers$^{1,2,3}$, S. E. Tremblay, J. Jones, B. Crosse
 \affil{$^1$International Centre for Radio Astronomy Research (ICRAR), GPO Box U1987, Perth, WA 6845, Australia}%
 \affil{$^2$CSIRO Astronomy and Space Science, PO Box 76, Epping, NSW 1710, Australia}
+\affil{$^3$Dept. of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, B.C., V6T 1Z1, Canada}
 }
@@
 That is, it effectively `undoes' the fine PFB, increasing the available time resolution to $\sim 0.8\,\mu$s.
-A brief review of PFBs in general, and their particular implementation in the case of the MWA, are given in \S\ref{sec:pfb}.
-The design of the synthesis filter is described in \S\ref{sec:ipfb}, including a discussion of its fidelity, i.e., the appearance of any temporal and spectral artefacts introduced by the synthesis filter itself.
-Finally, the practical use of this functionality is demonstrated through two examples: MWA observations of the MSPs J2241$-$5236 and J0437$-$4715.
+A brief review of PFBs in general, and their particular implementation in the case of the MWA, are given in Section \ref{sec:pfb}.
+The design of the synthesis filter is described in Section \ref{sec:ipfb}, including a discussion of its fidelity, i.e., the appearance of any temporal and spectral artefacts introduced by the synthesis filter itself.
+Finally, the practical use of this functionality is demonstrated in Section \ref{sec:pulsardata} through three examples: MWA observations of the PSRs J2241$-$5236, J0437$-$4715, and \bname{} (\jname{}).
 
@@
 A short proof of this equivalence is given in \citet{Harris2011}.
-The procedure described by Eq. \eqref{eqn:pfb} is illustrated in Fig. \ref{fig:pfb}.
+The procedure described by Eq. \eqref{eqn:pfb} is called the \textit{weighted overlap-add} algorithm, and is illustrated in Fig. \ref{fig:pfb}.
 \begin{figure}[t]
@@
 \begin{equation}
-    h[n] = w_H[n]\,w_s[n],
+    h[n] =
+        \begin{cases}
+            w_H[n]\,w_s[n], & 0 \le n < N, \\
+            0               & \text{otherwise}
+        \end{cases}
     \label{eqn:filter}
@@
 
+The fine PFB is implemented on [TODO: make/model] field-programmable gate arrays (FPGAs) and was designed in such a way to accommodate the data rates and bit depths set by the surrounding hardware.
+The input signal values are signed (5+5)-bit complex integers, and the final outputs are (4+4)-bit complex integers.
+The loss of precision associated with the demotion of 1 bit naturally places limits on the ability for any synthesis filter to perfectly reconstruct the original coarse channel time series, which is analysed for our system below.
+The full details of the FPGA implementation are given in the appendix.
+
 \section{Synthesis filter}
@@
 
+The spectral output of the PFB, $X_k[m]$, can be used to reconstruct the time series $\hat{x}[n]$ by means of a \textit{synthesis filter}.
+The hat signifies the fact that the resulting time series does not necessarily equal the original input to the PFB, $x[n]$, since one is free to choose the synthesis filter itself, $f$:
+\begin{equation}
+    \hat{x}[n] = \sum_{m = 0}^{M-1} f[n - mM]\,
+        \frac{1}{K} \sum_{k=0}^{K-1} X_k[m]\,e^{2\pi jkn/K}.
+    \label{eqn:ipfb}
+\end{equation}
+The precise condition for $\hat{x}[n] = x[n]$ for a critically sampled PFB is \citep[proven in][]{Crochiere1983}:
+\begin{equation}
+    \lambda(s) = \sum_{m=0}^{M-1} f[n-mM]\,h[mM - n + sM] = \Kron
+    \label{eqn:invertibility_condition}
+\end{equation}
+for all values of $n$, where $\Kron$ is the Kronecker delta.
+Eq.
+\eqref{eqn:invertibility_condition} means that the synthesis filter must ``convolve'' with the analysis filter (where the translation part of the convolution is restricted to step sizes of $M$) to produce an impulse.
+
+Whether this condition is perfectly met clearly depends on the choice of analysis and synthesis filters.
+However, even a synthesis filter which only approximately satisfies Eq.
+\eqref{eqn:invertibility_condition} for a given analysis filter (i.e.
+$\lambda(s) \approx \Kron$) will produce a time series approximates the original coarse channel time series (i.e.
+$\hat{x}[n] \approx x[n]$).
+The more Eq. \eqref{eqn:invertibility_condition} departs from the Kronecker delta function, the more artefacts will appear in the time domain.
+In practice, the choice of synthesis filter is often obliged to be a compromise between ease of implementation and an acceptable level of imperfection in the reconstructed time series.
+
+For the filter $h[n]$ defined in Eq. \eqref{eqn:filter}, it is found that choosing
+\begin{equation}
+    f[n] = \frac{h[-n]}{H},
+    \label{eqn:synthesisfilter}
+\end{equation}
+meets the invertibility condition sufficiently closely for our purposes.
+$H = \sum_{n=0}^{N-1} h[n]$ is a normalising factor.
+The value of \eqref{eqn:invertibility_condition} is illustrated in Fig.
+\ref{fig:inverse_condition}, in which it can be readily seen that $\lambda(s)$ closely approximates, but does not exactly equal, a delta function.
+The quantitative effect of this analysis-synthesis pair is discussed in Section \ref{sec:fidelity}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{inverse_condition.eps}
+    \caption{The condition for invertibility, Eq.
+\eqref{eqn:invertibility_condition}, demonstrated for the analysis filter given in Eq.
+\eqref{eqn:filter} and the synthesis filter given in Eq.
+\eqref{eqn:synthesisfilter}.
+The fact that $\lambda(s)$ only approximates the delta function gives rise to spurious artefacts (``ringing'') in the time domain, which can be seen in Fig.
+(TODO).}
+    \label{fig:inverse_condition}
+\end{figure}
+
 \subsection{Implementation}
 
-\subsection{Fidelity}
+We have implemented the synthesis filter defined in Eq.
+\eqref{eqn:synthesisfilter} as an optional component of the MWA-VCS beamforming software, \vcstools{}\footnote{\url{https://github.com/CIRA-Pulsars-and-Transients-Group/vcstools}}, described in \citet{Ord2019}.
+In this mode, a time series reconstructed from the beamformed fine channelised data is written out for each coarse channel as two separate polarisation streams (i.e.
+without converting to Stokes parameters) in the VDIF file format \citep{Whitney2009}.
+This format was chosen because it is supported by the coherent de-dispersion functionality of DSPSR\footnote{\url{http://dspsr.sourceforge.net/}} \citep{VanStraten2011b}, a software suite for processing pulsar time series.
+
+The final stage before writing out the time series to file is the conversion from the complex floating point output of the synthesis operation into a signed 8-bit complex integer format required by the VDIF format.
+Each second of data is independently mean-subtracted and normalised in order to avoid clipping errors.
+It is worth noting that the mean-subtraction will mitigate to some degree the mean offset introduced by rounding errors in the analysis PFB (see the Appendix for details).
+
+Viewed as a linear operation, Eq. \eqref{eqn:ipfb} is ideally suited for GPUs, and we have implemented it in \vcstools{} for NVIDIA's CUDA architecture.
+Rather than use existing implementations of the implied inverse DFT, the $N \times K$ exponential terms (the so-called ``twiddle factors'') are pre-calculated and stored in a 2D array of double-precision floating point numbers on the GPUs.
+These are then accessed as required for the calculation of a given sample $\hat{x}[n]$.
+The whole pipeline (beamforming and synthesis) runs faster than real time\footnote{Verified for CUDA compute capability $>3.5$.}, unless throttled by I/O limitations of the computer system it is running on.
+
+\subsection{Fidelity of reconstructed time series}
+\label{sec:fidelity}
+
+The major challenge in verifying the fidelity of the back-to-back analysis-synthesis filter pair is the fact that the analysis PFB only exists on the FPGAs used in production and not as stand-alone software than can be fed arbitrary input.
+This makes conducting standard impulse response tests impossible, unless the exact performance of the PFB can be reproduced.
+We have therefore attempted to replicate the PFB in software; however, the replication was not perfect, causing a small difference between the our model analysis-synthesis back-to-back system, and the analysis-synthesis system used in production.
+
+In the fidelity tests presented in this section, there are therefore a number of sources of error, all of which cause the reconstructed coarse channel time series, $\hat{x}[n]$, to differ from the original input time series, $x[n]$:
+\begin{itemize}
+    \item the imperfect replication of the forward PFB, estimated to contribute noise-like error at the $-20\,$dB level (``replication error'', see Appendix for details);
+    \item the error associated with the demotion of the input (5+5)-bit complex integers ($x[n]$) to the (4+4)-bit complex integer format output by the PFB (``quantisation error'', also see Appendix); and
+    \item the error caused by the fact that the synthesis filter ($f[n]$) does not exactly complement the analysis filter ($h[n]$) in the sense described by Eq.
+\eqref{eqn:invertibility_condition} (``filter error'').
+\end{itemize}
+Although knowing the relative contributions of quantisation and filter errors is useful for improving the system (since the latter may be mitigated by identifying a better synthesis filter), it is only necessary to know their joint contribution for the purposes of characterising the analysis-synthesis system.
+This contribution is revealed in an impulse response test, the results of which are shown in Fig. \eqref{fig:impulse_response}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{compare_coarse_imp.eps}
+    \caption{The response of the back-to-back analysis-synthesis system to a finite impulse.
+The coarse-channelised output has been arbitrarily scaled to have a comparable magnitude to the original (5+5)-bit impulse, and the original impulse has been shifted slightly to the left for visual clarity.
+The spurious artefacts seen on either side of the central pulse at intervals of 64 samples are dominated by the so-called ``filter error'' (see text).}
+    \label{fig:impulse_response}
+\end{figure}
+
+As revealed by the impulse response test, our system is capable of reproducing the original impulse with high fidelity, despite the fact that the chosen synthesis filter is not ideal.
+The main discrepancy appears in the form of temporal ``echoes'' of the original impulse occurring at intervals of 64 coarse channel samples (i.e.
+half the size of one tap, equal to $50\,\mu$s for our sampling rate of $1.28\,$MHz).
+Although the power in the echoes is small compared to the central impulse (at roughly the $-10\,$dB level), it is important to realise that the echoes always appear at the same locations relative to it.
+Therefore, echoes of individual pulses from a pulsar signal will always contribute to the same phase bins when the time series is folded at the pulsar's rotation period.
+Any structure seen on this time scale must therefore always be regarded with suspicion.
+
+\section{Verification with pulsar observations}
+\label{sec:pulsardata}
+
+\section{Conclusion}
+
+The MWA-VCS telescope system outputs dynamic spectra with a frequency resolution of $10\,$kHz and a time resolution of $100\,\mu$s, which is suitable for many pulsar applications, as demonstrated in several pulsar science papers published to date \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018}.
+In this paper, we have presented an algorithm to undo the fine channelisation stage (fine PFB) of the VCS pipeline by using a synthesis polyphase filter, implemented as part of our processing software suite, \vcstools{}.
+The result is a high-fidelity reconstruction of the coarse channelised (pre-PFB) time series, suitable for high-time resolution studies of MSPs and other rapid transient signals.
+Although the reconstruction is not perfect, the introduced errors are quantified (up to $-10\,$dB in certain samples) and any spurious artefacts can be identified by virtue of the known timescale of their recurrence ($50\,\mu$s).
+
+\begin{appendix}
+
+\section{The FPGA implementation of the fine PFB}
+
+Each coarse channel is independently processed by dedicated FPGAs to convert (5+5)-bit complex integers sampled at $1.28\,$MHz into a series of spectra composed of $128\times$(4+4)-bit complex integers sampled at $10\,$kHz.
+The PFB is implemented in two stages: (1) a ``front-end'' stage which prepares the array $b[n]$ (see Eq. \eqref{eqn:pfb}), and (2) the ``FFT'' stage, which calculates the 128-point spectrum, $X_k[m]$.
+
+The first stage involves a multiplication of a window of 1536 consecutive coarse channel samples with the analysis filter shown in Fig.
+\ref{fig:filter}, and then a summation of the 12 taps together to produce a single array of 128 complex integers.
+The combination of the allowed input values $[-16, 15]$ and the filter values guarantees that the magnitudes of the summed numbers do not exceed $2^{22} = 4194304$.
+At this stage of the processing, they are stored as 48-bit signed integers, of which only the bottom 21 bits are therefore significant.
+Each integer $n$ (either real or imaginary) is then reduced from 48 bits to 8 bits in the following manner.
+If $n$ is positive, then bits 14 through 21 (counting from the least significant bit) are selected to form the 8-bit integer, and 1 is subsequently added if bit 13 is 1.
+This is equivalent to rounding the number $n/2^{14}$ to the nearest integer, where fractional values of 0.5 are always rounded up.
+If $n$ is negative, then bits 14 through 21 are selected, but no rounding occurs.
+This is equivalent to applying the floor operation to $n/2^{14}$.
+It should be noted that this rounding scheme introduces a bias into the distribution of values.
+In particular, the distribution of 8-bit values has a different mean than the distribution of the original 5-bit values, and it results in an artificial deficit in the number of values that get rounded to zero.
+The rounding scheme and its effect on the distribution are illustrated in Fig. \ref{fig:pre_fft_distributions}, including a displaced mean which artificially adds power to the DC bin of the spectrum.
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\columnwidth]{pre_fft_distributions.eps}
+    \caption{The first-stage (i.e.
+pre-FFT) rounding scheme implemented in the MWA FPGAs compared with a symmetric scheme.
+The top panel illustrates the two rounding schemes (each has been given a slightly different $y$-offset for visual clarity).
+A population of 5-bit samples was drawn from a rounded Gaussian distribution with mean $\mu = 0$ and standard deviation $\sigma = 2$.
+The vertical dashed lines show the means of the distributions after the population has been subjected to the first stage of the PFB (i.e.
+converted to 8-bit integers) and rounded according to the two different schemes.
+The bottom panel compares the distributions of the resulting population of 8-bit samples.}
+    \label{fig:pre_fft_distributions}
+\end{figure}
+
+The second stage calculates the spectrum of $b[n]$ using the standard fixed point FFT algorithm that is implemented on [make and model] FPGAs.
+The output values are scaled and (symmetrically) rounded, producing (4+4)-bit output values.
+
+As described in the main text, it was necessary to replicate the function of the fine PFB in software in order to conduct impulse tests of the analysis-synthesis pair.
+Our CPU-based implementation differs from the algorithm described above only by the use of the FFTW library\footnote{\url{http://www.fftw.org/}} for the FFT stage, which uses (and outputs) floating point values.
+Nevertheless the resulting spectrum was found to contain a small number of quantisation ``errors'': slightly under $1\%$ of the output 4-bit values differed from the FPGA-produced values by 1.
+To quantify the effect of these quantisation errors, we recorded a small amount of coarse channel data (dominated by telescope noise) along with the contemporaneous spectrum output by the FPGA PFB.
+We used the GPU-based synthesis filter described in Section \ref{sec:ipfb} to reconstruct the coarse channel data from both the FPGA spectrum and the CPU spectrum generated by our own implementation.
+We found the results to differ from each other at less than the $-20\,$dB power level, which is much less than the estimated difference between the reconstructed coarse channel data and the original.
+
+\end{appendix}
 

### 2019-12-04 ipfb.tex
Wrote more of the section about verification of the system using pulsar observations

@@
 \newcommand{\vcstools}{VCSTools}
-\newcommand{\bname}{B0950$+$08}
-\newcommand{\jname}{J0953$+$0755}
+\newcommand{\psrslowB}{B0950$+$08}
+\newcommand{\psrslowJ}{J0953$+$0755}
+\newcommand{\psrkaurJ}{J2241$-$5236}
+\newcommand{\psrbhatJ}{J0437$-$4715}
+\newcommand{\dmunits}{\ensuremath{\text{pc}\,\text{cm}^{-3}}}
 
@@
 The design of the synthesis filter is described in Section \ref{sec:ipfb}, including a discussion of its fidelity, i.e., the appearance of any temporal and spectral artefacts introduced by the synthesis filter itself.
-Finally, the practical use of this functionality is demonstrated in Section \ref{sec:pulsardata} through three examples: MWA observations of the PSRs J2241$-$5236, J0437$-$4715, and \bname{} (\jname{}).
+Finally, the practical use of this functionality is demonstrated in Section \ref{sec:pulsardata} through three examples: MWA observations of the PSRs \psrkaurJ{}, \psrbhatJ{}, and \psrslowB{} (\psrslowJ{}).
 
-\section{Polyphase filterbanks (PFBs)}
+\section{Polyphase filterbanks (PFB)}
 \label{sec:pfb}
@@
 \end{equation}
-The precise condition for $\hat{x}[n] = x[n]$ for a critically sampled PFB is \citep[proven in][]{Crochiere1983}:
+The necessary and sufficient condition for exact equality, $\hat{x}[n] = x[n]$, for a critically sampled PFB is \citep[proven in][]{Crochiere1983}:
 \begin{equation}
@@
 Eq.
-\eqref{eqn:invertibility_condition} means that the synthesis filter must ``convolve'' with the analysis filter (where the translation part of the convolution is restricted to step sizes of $M$) to produce an impulse.
+\eqref{eqn:invertibility_condition} formally resembles a kind of ``convolution'' of the synthesis filter with the analysis filter, where the translational part of the convolution operation is restricted to step sizes of $M$.
 
@@
 \eqref{eqn:invertibility_condition} for a given analysis filter (i.e.
-$\lambda(s) \approx \Kron$) will produce a time series approximates the original coarse channel time series (i.e.
+$\lambda(s) \approx \Kron$) will produce a time series that approximates the original coarse channel time series (i.e.
 $\hat{x}[n] \approx x[n]$).
-The more Eq. \eqref{eqn:invertibility_condition} departs from the Kronecker delta function, the more artefacts will appear in the time domain.
 In practice, the choice of synthesis filter is often obliged to be a compromise between ease of implementation and an acceptable level of imperfection in the reconstructed time series.
@@
 The value of \eqref{eqn:invertibility_condition} is illustrated in Fig.
-\ref{fig:inverse_condition}, in which it can be readily seen that $\lambda(s)$ closely approximates, but does not exactly equal, a delta function.
+\ref{fig:inverse_condition}, in which it can be readily seen that $\lambda(s)$ closely approximates, but does not exactly equal, $\Kron$.
 The quantitative effect of this analysis-synthesis pair is discussed in Section \ref{sec:fidelity}.
@@
 The fact that $\lambda(s)$ only approximates the delta function gives rise to spurious artefacts (``ringing'') in the time domain, which can be seen in Fig.
-(TODO).}
+\ref{fig:impulse_response}.}
     \label{fig:inverse_condition}
@@
     \caption{The response of the back-to-back analysis-synthesis system to a finite impulse.
-The coarse-channelised output has been arbitrarily scaled to have a comparable magnitude to the original (5+5)-bit impulse, and the original impulse has been shifted slightly to the left for visual clarity.
+The coarse-channelised (reconstructed) output has been arbitrarily scaled to have a comparable magnitude to the original (5+5)-bit impulse, and the original impulse has been shifted slightly to the left for visual clarity.
 The spurious artefacts seen on either side of the central pulse at intervals of 64 samples are dominated by the so-called ``filter error'' (see text).}
@@
 \label{sec:pulsardata}
+
+Pilot observations of three pulsars are presented here to vindicate the synthesis filter as a useful tool for undertaking high time resolution studies of pulsars: MSPs \psrkaurJ{} and \psrbhatJ{}, and the bright PSR \psrslowB{}.
+
+\psrkaurJ{} has a rotation period of $2.2\,$ms and a dispersion measure (DM) of $11.4\,\dmunits$.
+The resulting dispersion smear across $10\,$kHz channels at the central observing frequency of $150.4\,$MHz is approximately $0.2\,$ms, or $45^\circ$ of rotation phase, consistent with the width of the average profile formed from incoherently de-dispersed, fine channelised data recorded with the MWA-VCS system (Fig.
+\ref{fig:J2241_profiles}, top panel).
+Upon applying the synthesis filter and coherently de-dispersing the reconstructed time series sampled at the much higher rate of $1.28\,$MHz, the same data revealed exquisite detail in the average profile, including a pair of pre-cursor components only marginally visible (if at all) at higher frequencies (Fig.
+\ref{fig:J2241_profiles}, bottom panel).
+Moreover, these new, low-frequency observations have enabled the DM of this pulsar to be measured to unprecedented precision, with important consequences for measuring DM chromaticity and evaluating its effect on pulsar timing experiments.
+These results are discussed in detail in \citet{Kaur2019}.
+
+The resemblance of the newly-sighted precursor components to the temporal artefacts induced by the synthesis filter naturally raises questions about their authenticity.
+The fact that the components only appear on the leading side of the main pulse is a point in favour of them being real, since the temporal artefacts are expected to appear on both leading and trailing sides.
+In addition, the time interval between the main pulse and the closest component is $\sim150\,\mu$s, which, although it corresponds to the expected location of the third-order artefact, is not expected to be brighter than the first two; however, no evidence of the lower-order artefacts is seen.
+Finally, recent independent follow-up observations made by some of the authors using Band 3 ($250$ to $500\,$MHz) of the upgraded Giant Metrewave Radio Telescope (uGMRT) have confirmed the reality of the innermost component (Kaur et al., in prep).
+
+\psrbhatJ{} \dots
+
+\psrslowB{} \dots
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[angle=270,width=\columnwidth]{J2241_063-172_FITS_profile.eps}
+    \includegraphics[angle=270,width=\columnwidth]{J2241_063-172_vdif_profile.eps}
+    \caption{Profiles of PSR \psrkaurJ{} made using incoherently de-dispersed, $10\,$kHz fine channels (top) and coherently de-dispersed, reconstructed coarse channels (bottom) from the same data set \citep{Kaur2019}.
+The possibility that the two small components on the leading side of the main pulse are artefacts of the synthesis filter has been ruled out (see accompanying text).}
+    \label{fig:J2241_profiles}
+\end{figure}
 

### 2019-12-10 ipfb.tex
A few more updates to the text and the bibliography.

@@
 \DeclareMathOperator{\sinc}{sinc}
+\newcommand{\PaperI}{Paper I\nocite{Ord2019}}
 \newcommand{\Kron}{\delta_s^0}
@@
 
-\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$, B. W. Meyers$^{1,2,3}$, S. E. Tremblay, J. Jones, B. Crosse
+\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$, B. W. Meyers$^{1,2,3}$, S. E. Tremblay, J. Jones$^1$, B. Crosse$^1$
 \affil{$^1$International Centre for Radio Astronomy Research (ICRAR), GPO Box U1987, Perth, WA 6845, Australia}%
@@
 In more recent times, the ongoing effort to detect nanohertz gravitational waves by means of pulsar timing arrays requires the continual monitoring of the times of arrival (TOAs) of millisecond pulsars (MSPs) with microsecond accuracy (CITATIONS).
-Pulsars are also known to exhibit temporal structures on microsecond and even nanosecond time scales, providing major clues for the underlying radio emission mechanism (CITATIONS).
-Similarly, fast radio bursts (FRBs) have been shown to exhibit temporal sub-millisecond structures that either point to the intrinsic emission mechanism or to interesting propagation effects occurring in the intergalactic medium (CITATIONS).
+Pulsars are also known to exhibit temporal structures on microsecond and even nanosecond time scales \citep[e.g.][]{Craft1968,Hankins2003}, providing major clues for the underlying radio emission mechanism \citep[][\dots]{Cordes1981}.
+Similarly, fast radio bursts (FRBs) have been shown to exhibit temporal sub-millisecond structures that either point to the intrinsic emission mechanism or to interesting propagation effects occurring in the intergalactic medium \citep{Hessels2019}.
 All of these examples serve to illustrate the scientifically important and still largely untapped parameter space that is only accessible to telescopes equipped with a sufficiently high time resolution observing mode.
@@
 In the current MWA system design, only the latter time resolution data product (i.e. $100\,\mu$s) is made available to the user.
-While this is sufficient for many pulsar studies \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018}, it is nevertheless too coarse for many science applications involving MSPs.
+While this is sufficient for many pulsar studies \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018,Meyers2018}, it is nevertheless too coarse for many science applications involving MSPs.
 In principle, the original higher time resolution can be recovered from the channelised output (either approximately or exactly) by means of a \textit{synthesis filter}, which acts as an `inverse' operation to the analysis filter.
@@
     \includegraphics[width=\columnwidth]{example-image-a}
-    \caption{A diagramatic representation of the PFB algorithm, as defined in Eq. \eqref{eqn:pfb}.}
+    \caption{A diagrammatic representation of the weighted overlap-add algorithm, as defined in Eq. \eqref{eqn:pfb}.}
     \label{fig:pfb}
@@
 
-The fine PFB is implemented on [TODO: make/model] field-programmable gate arrays (FPGAs) and was designed in such a way to accommodate the data rates and bit depths set by the surrounding hardware.
+The fine PFB is implemented on field-programmable gate arrays (FPGAs)\footnote{Xilinx Virtex4 XC4VSX35} and was designed in such a way to accommodate the data rate and bit depth constraints set by the surrounding hardware.
 The input signal values are signed (5+5)-bit complex integers, and the final outputs are (4+4)-bit complex integers.
@@
 We have implemented the synthesis filter defined in Eq.
-\eqref{eqn:synthesisfilter} as an optional component of the MWA-VCS beamforming software, \vcstools{}\footnote{\url{https://github.com/CIRA-Pulsars-and-Transients-Group/vcstools}}, described in \citet{Ord2019}.
+\eqref{eqn:synthesisfilter} as an optional component of the MWA-VCS beamforming software, \vcstools{}\footnote{\url{https://github.com/CIRA-Pulsars-and-Transients-Group/vcstools}}, described in \PaperI{}.
 In this mode, a time series reconstructed from the beamformed fine channelised data is written out for each coarse channel as two separate polarisation streams (i.e.
@@
 These are then accessed as required for the calculation of a given sample $\hat{x}[n]$.
-The whole pipeline (beamforming and synthesis) runs faster than real time\footnote{Verified for CUDA compute capability $>3.5$.}, unless throttled by I/O limitations of the computer system it is running on.
+The combined GPU-accelerated calculations for both beamforming and coarse channel reconstruction run faster than real time\footnote{Verified for CUDA compute capability $>3.5$.}.
 
@@
 The main discrepancy appears in the form of temporal ``echoes'' of the original impulse occurring at intervals of 64 coarse channel samples (i.e.
-half the size of one tap, equal to $50\,\mu$s for our sampling rate of $1.28\,$MHz).
+half the size of one tap, equal to $50\,\mu$s for our sampling rate of $1.28\,$MHz) on either side of the reconstructed impulse.
 Although the power in the echoes is small compared to the central impulse (at roughly the $-10\,$dB level), it is important to realise that the echoes always appear at the same locations relative to it.
-Therefore, echoes of individual pulses from a pulsar signal will always contribute to the same phase bins when the time series is folded at the pulsar's rotation period.
+Because both the analysis and synthesis filters are symmetrical, the echoes are also expected to be symmetrical; the asymmetry seen in Fig.
+\ref{fig:impulse_response} must therefore be due to either replication or quantisation error.
+Note that echoes arising from strong individual pulses in a pulsar signal will always contribute to the same phase bins when the time series is folded at the pulsar's rotation period.
 Any structure seen on this time scale must therefore always be regarded with suspicion.
+
+Further fidelity tests were performed with data containing real pulsar signals, presented in the next section.
 
@@
 Pilot observations of three pulsars are presented here to vindicate the synthesis filter as a useful tool for undertaking high time resolution studies of pulsars: MSPs \psrkaurJ{} and \psrbhatJ{}, and the bright PSR \psrslowB{}.
+
+\subsection{PSR \psrkaurJ{}}
 
@@
 
-\psrbhatJ{} \dots
-
-\psrslowB{} \dots
-
 \begin{figure}[t!]
@@
     \includegraphics[angle=270,width=\columnwidth]{J2241_063-172_vdif_profile.eps}
-    \caption{Profiles of PSR \psrkaurJ{} made using incoherently de-dispersed, $10\,$kHz fine channels (top) and coherently de-dispersed, reconstructed coarse channels (bottom) from the same data set \citep{Kaur2019}.
+    \caption{Profiles of PSR \psrkaurJ{} made using incoherently de-dispersed, $10\,$kHz fine channels (top) and coherently de-dispersed, reconstructed coarse channels (bottom) from the same data set \citep{Kaur2019} (the flux scales are arbitrary).
 The possibility that the two small components on the leading side of the main pulse are artefacts of the synthesis filter has been ruled out (see accompanying text).}
@@
 
+\subsection{PSR \psrbhatJ{}}
+
+\begin{itemize}
+    \item Now able to resolve notches in profile
+    \item Compare to higher frequency polarimetry
+    \item \dots
+\end{itemize}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\columnwidth]{mwa0437hires.png}
+    \caption{[Caption\dots]}
+    \label{fig:0437}
+\end{figure}
+
+\subsection{PSR \psrslowB{}}
+
+\dots
+
 \section{Conclusion}
 
-The MWA-VCS telescope system outputs dynamic spectra with a frequency resolution of $10\,$kHz and a time resolution of $100\,\mu$s, which is suitable for many pulsar applications, as demonstrated in several pulsar science papers published to date \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018}.
+The MWA-VCS telescope system outputs dynamic spectra with a frequency resolution of $10\,$kHz and a time resolution of $100\,\mu$s, which is suitable for many pulsar applications, as demonstrated in several pulsar science papers published to date \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018}\textbf{[BWM: Can probably not bother with these references here since you use the same ones in the introduction.
+You could maybe cite the MWA Phase 2 science paper here?]}.
 In this paper, we have presented an algorithm to undo the fine channelisation stage (fine PFB) of the VCS pipeline by using a synthesis polyphase filter, implemented as part of our processing software suite, \vcstools{}.
@@
 
+\dots
+
 \end{appendix}
-
-%%% SAMPLE %%%
-%\begin{table}
-%\caption{This is an example of table caption.}
-%\centering
-%\begin{tabular}{@{}cc@{}}
-%\hline\hline
-%Dimension & Classification accuracy \\
-%\hline%
-% 1  & 0.6232$^{(a)}$ \\
-% 2  & 0.9635 \\
-% 3  & 0.9724 \\
-% 4  & 0.9690 \\
-% 5  & 0.9840 \\
-% 6  & 0.9842 \\
-% 7  & 0.9873 \\
-% 8  & 0.9884 \\
-% 9  & 0.9873 \\
-% 10 & 0.9898 \\
-% 11 & 0.9914 \\
-%\hline\hline
-%\end{tabular}
-%\label{tab1}
-%\medskip
-%\tabnote{$^a$This is an example of table footnote}
-%\tabnote{This is an example of table footnote}
-%\tabnote{This is an example of table footnote}
-%\end{table}
-%
-%\begin{acknowledgements}
-%This is a multiline text of acknowledgments.
-We are met here on a great battlefield of that war.
-We have come to dedicate a portion of it as a final resting place for those who here gave their lives that that nation might live.
-%\end{acknowledgements}
-%
-%
-%\begin{appendix}
-%
-%\section{AN EXAMPLE OF APPENDIX HEAD}
-%
-% Consider a data set
-%\begin{equation}
-%S=(f_{ij})_{m\times n}
-%\end{equation} the \(i\)th
-%data point of which is
-%\[ (f_{i1}, . . . , f_{in}).\]
-% Let $\overline{f}_q=\frac{1}{m}\sum_{i=1}^mf_{iq}$ and $\sigma_q$ The brave men, living and dead, who struggled, here, have consecrated it far above our poor power to add or detract. Suppose that
-%\[X_i=(x_{i1},\dots,x_{in}) \indent (i=1,\dots, m),\]
-%where $x_{ij}=(f_{ij}-\overline{f}_j)/\sigma_j $ and
-%\[B=(X_1^T,\dots,X_m^T)^T.\]
-% Then we can show that
-%\[C=B^TB=\sum\limits_{i=1}^m X_i^TX_i=(C_{jk})_{n\times n},\]
-%where $C_{jk}=\sum_{i=1}^mx_{ij}x_{ik}$ is the correlation matrix. Our goal is to find a normalized vector
-%$$a_1=(a_{11},a_{12},\dots,a_{1n})^T$$
-% such that the projection of the standardized data
-%\[X_ia_1=\sum\limits_{k=1}^n x_{ik}a_{1k},\]
-%\noindent then $Ba_1$
-% \[a_1^TB^T ¡¤ Ba_1=a_1^TCa_1.\]
-% Our goal is to maximize this value under the constraint $a_1^Ta_1=1$. Let $\lambda_{\rm max}$ be the largest eigenvalue of
-% $C$. According to the Rayleigh--Ritz theorem, $a_1$ can be obtained by solving
-% \[Ca_1= \lambda_{\rm max}a_1.\]
-%But in a larger sense we can not dedicate -- we can not consecrate -- we can not hallow this ground.
-The brave men, living and dead, who struggled, here, have consecrated it far above our poor power to add or detract.
-The world will little note, nor long remember, what we say here, but can never forget what they did here.
-It is for us, the living, rather to be dedicated here to the unfinished work which they have, thus far, so nobly carried on \cite{abt1981}.
-It is rather for us to be here dedicated to the great task remaining before us  that from these honoured dead we take increased devotion to that cause for which they here gave the last full measure of devotion  that we here highly resolve that these dead shall not have died in vain; that this nation shall have a new birth of freedom; and that this government \cite{abt1984b} of the people, by the people, for the people, shall not perish from the earth.
-%\end{appendix}
-%%% END SAMPLE %%%
 

### 2020-01-23 ipfb.tex
Added more notes. Also updated this repo with changes to the paper made on Overleaf. At this point, everything has been drafted up except the section on J0437-4715

@@
 
-\title[MWA tied-array processing III]{MWA tied-array processing III: Microsecond time resolution via a synthesis filter}
-
-%%% SAMPLE %%%
-%% Please note that the command \and is not supported in \author.
-%\author[Author1 et al.]{Author1$^1$, Author2$^2$, Author3$^2$ and Author4$^{2,}$\thanks{This is an example of author footnote}
-%\affil{$^1$This is  an example of Affiliation r Author 1}%
-%\affil{$^2$This is  an example of Affiliation for Author 2}
-%}%
-%%% END SAMPLE %%%
+\title[MWA tied-array processing III]{MWA tied-array processing III: Microsecond time resolution via a polyphase synthesis filter}
 
@@
 
-%%%%%%% IMPORTANT: We disable hyperlinks by default with this line, to avoid the error "\pdfendlink ended up in different nesting level" while writing.
-%\hypersetup{draft}
-%%%%%%% You may comment or delete the line above to make hyperlinks in your paper active.
-If you then encounter a strange "\pdfendlink ended up in different nesting level than \pdfstartlink", don't worry!
-Uncomment the line again, and see https://www.overleaf.com/help/246 for further information.
-
 \begin{document}
@@
 \begin{abstract}
-[Abstract\dots]
+A new high time resolution observing mode for the Murchison Widefield Array (MWA) is described, enabling full polarimetric observations with up to $30.72\,$MHz of bandwidth and a time resolution of $\sim 0.8\,\mu$s.
+This mode makes use of a polyphase synthesis filter to ``undo'' the polyphase analysis filter stage of the standard MWA's Voltage Capture System (VCS) observing mode.
+Sources of potential error in the reconstruction of the high time resolution data are identified and quantified, the most significant of which relate to ``temporal echoes'' seen in impulse response tests.
+The system is further verified by observing three pulsars with known structure on microsecond timescales.
 \end{abstract}
@@
 The serendipitous discovery of pulsars in the late 1960's is perhaps the prototypical example \citep{Hewish1968}.
-In more recent times, the ongoing effort to detect nanohertz gravitational waves by means of pulsar timing arrays requires the continual monitoring of the times of arrival (TOAs) of millisecond pulsars (MSPs) with microsecond accuracy (CITATIONS).
-Pulsars are also known to exhibit temporal structures on microsecond and even nanosecond time scales \citep[e.g.][]{Craft1968,Hankins2003}, providing major clues for the underlying radio emission mechanism \citep[][\dots]{Cordes1981}.
-Similarly, fast radio bursts (FRBs) have been shown to exhibit temporal sub-millisecond structures that either point to the intrinsic emission mechanism or to interesting propagation effects occurring in the intergalactic medium \citep{Hessels2019}.
+In more recent times, the ongoing effort to detect nanohertz gravitational waves by means of pulsar timing arrays requires the continual monitoring of the times of arrival (TOAs) of millisecond pulsars (MSPs) with microsecond accuracy \citep[e.g.][]{Hobbs2017}.
+Pulsars are also known to exhibit temporal structures on microsecond and even nanosecond time scales \citep[e.g.][]{Craft1968,Hankins2003}, providing major clues for the underlying radio emission mechanism \citep[e.g.][]{Cordes1981,Popov2002}.
+Similarly, fast radio bursts (FRBs) have been shown to exhibit temporal sub-millisecond structures that either point to the intrinsic emission mechanism or to interesting propagation effects occurring in the intergalactic medium \citep{Farah2018,Hessels2019}.
 All of these examples serve to illustrate the scientifically important and still largely untapped parameter space that is only accessible to telescopes equipped with a sufficiently high time resolution observing mode.
@@
 After preliminary filtering and digitisation, the raw voltages are subjected to a two-stage frequency analysis filter, which trades time resolution for increased frequency resolution.
-In the MWA's case, both stages of the analysis filter were implemented as polyphase filterbanks \citep[PFBs;][\dots]{Harris2011,Prabu2015}.
+In the MWA's case, both stages of the analysis filter were implemented as polyphase filterbanks \citep[PFBs;][]{Harris2011,Prabu2015}.
 The first stage (`coarse') PFB reduces the effecting sampling rate by a factor of 512, resulting in an array of complex-valued samples with $1.28\,$MHz resolution in frequency (`coarse' channels) and $\sim0.8\,\mu$s in time.
@@
     \centering
-    \includegraphics[width=\columnwidth]{example-image-a}
-    \caption{A diagrammatic representation of the weighted overlap-add algorithm, as defined in Eq. \eqref{eqn:pfb}.}
+    \includegraphics[width=\columnwidth]{cartoon.eps}
+    \caption{A diagrammatic representation of the weighted overlap-add algorithm, as defined in Eq.
+\eqref{eqn:pfb}.
+A discrete signal containing a sinusoid and noise (top row) is multiplied by a filter (second and third rows), and each ``tap'' (represented by columns) is summed (bottom left) and Fourier transformed to produce the final spectrum (bottom right).}
     \label{fig:pfb}
@@
 In the fidelity tests presented in this section, there are therefore a number of sources of error, all of which cause the reconstructed coarse channel time series, $\hat{x}[n]$, to differ from the original input time series, $x[n]$:
-\begin{itemize}
-    \item the imperfect replication of the forward PFB, estimated to contribute noise-like error at the $-20\,$dB level (``replication error'', see Appendix for details);
-    \item the error associated with the demotion of the input (5+5)-bit complex integers ($x[n]$) to the (4+4)-bit complex integer format output by the PFB (``quantisation error'', also see Appendix); and
-    \item the error caused by the fact that the synthesis filter ($f[n]$) does not exactly complement the analysis filter ($h[n]$) in the sense described by Eq.
-\eqref{eqn:invertibility_condition} (``filter error'').
-\end{itemize}
+\begin{description}
+    \item[``Replication error'':] The imperfect replication of the forward PFB, estimated to contribute noise-like error at the $-20\,$dB level (see Appendix for details);
+    \item[``Quantisation error'':] The error associated with the demotion of the input (5+5)-bit complex integers ($x[n]$) to the (4+4)-bit complex integer format output by the PFB (also see Appendix); and
+    \item[``Filter error'':] the error caused by the fact that the synthesis filter ($f[n]$) does not exactly complement the analysis filter ($h[n]$) in the sense described by Eq.
+\eqref{eqn:invertibility_condition}.
+\end{description}
 Although knowing the relative contributions of quantisation and filter errors is useful for improving the system (since the latter may be mitigated by identifying a better synthesis filter), it is only necessary to know their joint contribution for the purposes of characterising the analysis-synthesis system.
@@
 
-Further fidelity tests were performed with data containing real pulsar signals, presented in the next section.
+As a further verification, we also made use of a non-standard observing mode to record a small amount of simultaneous coarse and fine channel data (i.e.
+both before and after the fine PFB analysis filter stage).
+The fine channels from one polarisation of a single tile were extracted and subjected to the synthesis filter to reconstruct the $1.28\,$MHz coarse channel time series, which could then be compared directly with the original data.
+Although not as telling as an impulse response test, the close similarity of the reconstructed (white) noise with the original (see Fig.
+\ref{fig:compare_timeseries}) is indicative of the fidelity of the analysis-synthesis filter pair.
+
+Note that in this test, the FPGA-based fine PFB was used; thus, the errors shown in Fig. \ref{fig:compare_timeseries} do not contain any ``replication error''.
+However, the synthesis filter used in production uses an arbitrary scaling factor in order to make better use of the dynamic range afforded by VDIF's (8+8)-bit depth.
+The reconstructed samples shown in the figure have been rescaled by eye for the purposes of visual comparison.
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{compare_timeseries.eps}
+    \caption{128 high time resolution ($1.28\,$MHz) samples from a single coarse channel and a single polarisation of one MWA tile.
+The real (top) and imaginary (bottom) components are shown separately.
+The original coarse channel data (black boxes) are overlaid with the reconstructed data (red lines and dots), with the differences plotted in the lower panels.}
+    \label{fig:compare_timeseries}
+\end{figure}
 
@@
 
+[Suggestions:]
 \begin{itemize}
@@
 
-\dots
+Finally, we observed \psrslowB{}, a bright, slow ($P = 0.253\,$s) pulsar known to show microstructure on time scales of $\sim 60\,\mu$s \citep{Kuzmin2003}.
+A total of eighty seconds (315 pulses) of data ($128 \times 10\,$kHz fine channels) were recorded, beamformed, and subjected to the polyphase synthesis filter.
+The mean profile formed from the entire data set is shown in Fig. \ref{fig:0950_80_secs}.
+Several individual pulses were sufficiently bright to see substructure.
+One such pulse is showcased in Fig. \ref{fig:0950_single_pulse} at three different time resolutions (corresponding to the chosen bin width of each plot).
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\columnwidth]{1024bins_profile.eps}
+    \caption{Polarisation profile formed using 80 seconds (315 pulses) of \psrslowB{} data. The time resolution is $\sim 250\,\mu$s.}
+    \label{fig:0950_80_secs}
+\end{figure}
+
+\begin{figure}[t!]
+    \centering
+    \includegraphics[width=\columnwidth]{200ms_res.eps} \\[10pt]
+    \includegraphics[width=\columnwidth]{50ms_res.eps} \\[10pt]
+    \includegraphics[width=\columnwidth]{5ms_res.eps}
+    \caption{A bright, single pulse of \psrslowB{}, displayed with full polarisation at time resolutions of $\sim 200\,\mu$s (top), $\sim 50\,\mu$s (middle), and $\sim 5\,\mu$s (bottom).}
+    \label{fig:0950_single_pulse}
+\end{figure}
+
+Despite the proximity of this timescale to the temporal ``echoes'' induced by the synthesis filter ($50\mu$s), we were able to clearly identify the ($\sim 60\mu$s) microstructure reported by \citet{Kuzmin2003}.
+We also suggest that the finest observable structures (Fig. \ref{fig:0950_single_pulse}, bottom plot) might correspond to the $\sim 10\,\mu$s structures reported by \citet{Popov2002}.
+However, \citet{Kuzmin2003} used only a single linear polarisation feed, and \citet{Popov2002}, only a left-handed circularly polarised feed.
+With the benefit of full Stokes polarimetry, we are able to verify that on the smallest time scales, the emission is almost 100\% polarised---mostly linear, but with a small amount of circular polarisation during the brightest part of the pulse.
+This is evidence that the errors introduced by the analysis-synthesis filter do not contribute a significant amount of polarisation leakage into neighbouring time bins---in particular, at $50\,\mu$s intervals.
 
@@
 
-The MWA-VCS telescope system outputs dynamic spectra with a frequency resolution of $10\,$kHz and a time resolution of $100\,\mu$s, which is suitable for many pulsar applications, as demonstrated in several pulsar science papers published to date \citep[e.g.][]{Oronsaye2015,McSweeney2017,Bhat2018}\textbf{[BWM: Can probably not bother with these references here since you use the same ones in the introduction.
-You could maybe cite the MWA Phase 2 science paper here?]}.
+The MWA-VCS telescope system outputs dynamic spectra with a frequency resolution of $10\,$kHz and a time resolution of $100\,\mu$s, which is suitable for many pulsar applications, as demonstrated in several pulsar science papers published to date.
 In this paper, we have presented an algorithm to undo the fine channelisation stage (fine PFB) of the VCS pipeline by using a synthesis polyphase filter, implemented as part of our processing software suite, \vcstools{}.
 The result is a high-fidelity reconstruction of the coarse channelised (pre-PFB) time series, suitable for high-time resolution studies of MSPs and other rapid transient signals.
-Although the reconstruction is not perfect, the introduced errors are quantified (up to $-10\,$dB in certain samples) and any spurious artefacts can be identified by virtue of the known timescale of their recurrence ($50\,\mu$s).
+Although the reconstruction is not perfect, the introduced errors are quantified (up to $-10\,$dB in certain samples).
+The most significant artefacts, the ``temporal echoes'' of the impulse response, can be identified by virtue of the known timescale of their recurrence ($50\,\mu$s).
+
+We have further verified our system by observing PSRs \psrkaurJ{}, \psrbhatJ{}, and \psrslowB{}, all of which are known to exhibit structures on microsecond timescales.
+In each case, our results have been shown to be consistent with observations at higher radio frequencies.
+In particular, we have demonstrated that the errors introduced by the imperfect analysis-synthesis filter pair are negligible compared to the pulsar signals themselves, which have been reconstructed with full polarisation at the faster sampling rate ($1.28\,$MHz) with high fidelity.
+The advent of the VCS high time resolution observing mode thus distinguishes the MWA as a premier low-frequency instrument for studying pulsars and other transients at microsecond precision, with important implications for studies of the pulsar emission mechanism, the characterisation of the ISM in the ongoing search for gravitational waves, and others.
+
+\begin{acknowledgements}
+This work was supported by resources provided by the Pawsey Supercomputing Centre with funding from the Australian Government and the Government of Western Australia.
+\end{acknowledgements}
 
@@
 \ref{fig:filter}, and then a summation of the 12 taps together to produce a single array of 128 complex integers.
-The combination of the allowed input values $[-16, 15]$ and the filter values guarantees that the magnitudes of the summed numbers do not exceed $2^{22} = 4194304$.
-At this stage of the processing, they are stored as 48-bit signed integers, of which only the bottom 21 bits are therefore significant.
+The combination of the allowed input values $[-16, 15]$ and the filter values guarantees that the magnitudes of the summed (signed) numbers do not exceed $2^{21} = 2097152$.
+At this stage of the processing, they are stored as 48-bit signed integers, of which only the bottom 22 bits are therefore significant.
 Each integer $n$ (either real or imaginary) is then reduced from 48 bits to 8 bits in the following manner.
@@
 
-\dots
-
 \end{appendix}

### 2020-01-24 inverse_condition.py
Made sure that this version creates inverse_condition.eps, in case I have to re-create it at a later date.

@@ -53,6 +53,7 @@ im3 = ax[2].plot(x)
 #plt.colorbar(im1)
 #plt.colorbar(im2)
 plt.show()
+'''
 
 # Make plots
 plt.plot(ss, lmda, '-xk')
@@ -60,5 +61,3 @@ plt.ylim([-0.1, 1.0])
 plt.xlabel("$s$")
 plt.ylabel("$\\lambda(s)$")
 plt.savefig("inverse_condition.eps", bbox_inches='tight')
-plt.show()
-'''

### 2020-01-29 ipfb.tex
Final proof read corrections before submitting to the MWA collaboration for review.

@@
 \affil{$^2$CSIRO Astronomy and Space Science, PO Box 76, Epping, NSW 1710, Australia}
-\affil{$^3$Dept. of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, B.C., V6T 1Z1, Canada}
+\affil{$^3$Department of Physics and Astronomy, University of British Columbia, 6224 Agricultural Road, Vancouver, BC V6T 1Z1, Canada}
 }
@@
 spectral leakage) inherent in the application of DFTs to discretely sampled time series of finite length.
-They are well described in standard texts \citep{Crochiere1983,Harris2004,Oppenheim2009}; a clear and concise review of PFBs in the context of radio astronomy is given in \citet{Harris2011}.
+PFBs are well described in standard texts \citep{Crochiere1983,Harris2004,Oppenheim2009}; a clear and concise review of PFBs in the context of radio astronomy is given in \citet{Harris2011}.
 Thus, only a brief review of the salient features is given, in order to prepare the reader for the description of the synthesis filter in the following sections.
@@
 Choosing a larger window size, $N = KP$ (for integer $P > 1$), and a corresponding wider analysis filter, will result in a frequency response that is similar in shape, but $P$ times narrower than the frequency response of the original analysis filter.
-A DFT applied to the larger number of samples will naturally produce a correspondingly larger number of frequency channels, but choosing only every $P$th channel and discarding the rest (known as \textit{decimation}) ensures that the desired spectral resolution with $K$ channels is retained.
+A DFT applied to the larger number of samples will naturally produce a correspondingly larger number of (more closely spaced) frequency channels, but choosing only every $P$th channel and discarding the rest (known as \textit{decimation}) ensures that the desired spectral resolution with $K$ channels is retained.
 In this way, spectral leakage can be contained arbitrarily close to the ``correct'' channel by choosing a sufficiently high value of $P$.
@@
 The two-step algorithm described above (performing a windowed DFT on $N = KP$ samples and decimating the resulting spectrum) defines the PFB.
-Formally, it is equivalent to Eq. \eqref{eqn:wdft}; however, the term \textit{critically sampled} (i.e. $M = K$) implies that the $N$-length windows will now overlap.
+Formally, it is equivalent to Eq. \eqref{eqn:wdft}; however, in this context the term \textit{critically sampled} (i.e. $M = K$) implies that the $N$-length windows will now overlap.
 The term ``polyphase'' derives from the fact that each block of $K = N/P$ samples (known as \textit{taps}) in $x[n]$ is included in multiple applications of the DFT, but appearing at a different relative phase in each case.
@@
 
-For the filter $h[n]$ defined in Eq. \eqref{eqn:filter}, it is found that choosing
+For the analysis filter $h[n]$ defined in Eq. \eqref{eqn:filter}, it is found that choosing the synthesis filter
 \begin{equation}
-    f[n] = \frac{h[-n]}{H},
+    f[n] = \frac{h[-n]}{H}
     \label{eqn:synthesisfilter}
 \end{equation}
-meets the invertibility condition sufficiently closely for our purposes.
-$H = \sum_{n=0}^{N-1} h[n]$ is a normalising factor.
-The value of \eqref{eqn:invertibility_condition} is illustrated in Fig.
-\ref{fig:inverse_condition}, in which it can be readily seen that $\lambda(s)$ closely approximates, but does not exactly equal, $\Kron$.
+where $H = \sum_{n=0}^{N-1} h[n]$ is a normalising factor, meets the invertibility condition sufficiently closely for our purposes, as demonstrated below.
+With the analysis and synthesis filters thus defined, the value of Eq. \eqref{eqn:invertibility_condition} can be calculated and is illustrated in Fig. \ref{fig:inverse_condition}.
+It is readily seen that $\lambda(s)$ closely approximates, but does not exactly equal, $\Kron$.
 The quantitative effect of this analysis-synthesis pair is discussed in Section \ref{sec:fidelity}.
@@
 \eqref{eqn:synthesisfilter}.
-The fact that $\lambda(s)$ only approximates the delta function gives rise to spurious artefacts (``ringing'') in the time domain, which can be seen in Fig.
+The fact that $\lambda(s)$ only approximates the delta function gives rise to spurious artefacts (``temporal echoes'') in the time domain, which can be seen in Fig.
 \ref{fig:impulse_response}.}
@@
 half the size of one tap, equal to $50\,\mu$s for our sampling rate of $1.28\,$MHz) on either side of the reconstructed impulse.
-Although the power in the echoes is small compared to the central impulse (at roughly the $-10\,$dB level), it is important to realise that the echoes always appear at the same locations relative to it.
-Because both the analysis and synthesis filters are symmetrical, the echoes are also expected to be symmetrical; the asymmetry seen in Fig.
-\ref{fig:impulse_response} must therefore be due to either replication or quantisation error.
-Note that echoes arising from strong individual pulses in a pulsar signal will always contribute to the same phase bins when the time series is folded at the pulsar's rotation period.
-Any structure seen on this time scale must therefore always be regarded with suspicion.
+Although the power in the echoes is small compared to the central impulse (at roughly the $-10\,$dB level), the echoes always appear at the same locations relative to it.
+The asymmetry seen in Fig. \ref{fig:impulse_response} is due to replication error, quantisation error, the ``phase'' of the impulse with respect to the filter window, or some combination of the above.
+Importantly, echoes arising from strong, periodic individual pulses (e.g. in a pulsar signal) will accumulate in the same phase bins when the time series is folded at the pulsar's rotation period.
+Thus, any structure seen on this time scale must therefore be regarded with suspicion.
 
@@
 
-Note that in this test, the FPGA-based fine PFB was used; thus, the errors shown in Fig. \ref{fig:compare_timeseries} do not contain any ``replication error''.
+Note that in this test, the FPGA-based fine PFB was used; thus, the errors shown in Fig. \ref{fig:compare_timeseries} do not contain any replication error.
 However, the synthesis filter used in production uses an arbitrary scaling factor in order to make better use of the dynamic range afforded by VDIF's (8+8)-bit depth.
@@
 
-Pilot observations of three pulsars are presented here to vindicate the synthesis filter as a useful tool for undertaking high time resolution studies of pulsars: MSPs \psrkaurJ{} and \psrbhatJ{}, and the bright PSR \psrslowB{}.
+Pilot observations of three pulsars are presented here to validate the synthesis filter as a useful tool for undertaking high time resolution studies of pulsars: MSPs \psrkaurJ{} and \psrbhatJ{}, and the bright PSR \psrslowB{}.
 
@@
 In addition, the time interval between the main pulse and the closest component is $\sim150\,\mu$s, which, although it corresponds to the expected location of the third-order artefact, is not expected to be brighter than the first two; however, no evidence of the lower-order artefacts is seen.
-Finally, recent independent follow-up observations made by some of the authors using Band 3 ($250$ to $500\,$MHz) of the upgraded Giant Metrewave Radio Telescope (uGMRT) have confirmed the reality of the innermost component (Kaur et al., in prep).
+Finally, recent independent follow-up observations made by some of the authors using Band 3 ($250$ to $500\,$MHz) of the upgraded Giant Metrewave Radio Telescope (uGMRT) have confirmed that at least the innermost component is real (Kaur et al., in prep).
 
@@
 
-[Suggestions:]
-\begin{itemize}
-    \item Now able to resolve notches in profile
-    \item Compare to higher frequency polarimetry
-    \item \dots
-\end{itemize}
+PSR \psrbhatJ{} is a nearby MSP (distance $d \approx 157\,$pc; period $P \approx 5.76\,$ms) and an established target for pulsar timing array (PTA) applications.
+It boasts a complex, multi-component polarimetric profile (Fig. \ref{fig:0437}) that spans more than half of its rotation period \citep[cf.][]{Yan2011}.
+It was used in Paper I as a verification of the beamforming method employed in the VCS processing pipeline, although there is a noticeable difference between the circular polarisation published in that work and that shown here (see the Figure caption for details).
+
+As evident from Fig.
+\ref{fig:0437}, the application of the synthesis filter successfully recovers some curious fine structure (e.g.
+notch-like features at pulse phases $\sim$ 0.54 and $\sim$ 0.7) characteristic to this pulsar, first reported in early high time resolution studies made at 430 MHz \citep{Navarro1997}.
+The pulsar detection (for Stokes I only) was originally presented in \citet{Bhat2018}, where the combination of a lower time resolution (100 $\mu$s) and a non-negligible dispersive smearing ($\sim$45 $\mu$s) obscured the detection of these fine structures.
+Fig.
+\ref{fig:0437} thus presents the highest-fidelity detection of this important pulsar at frequencies below 200 MHz.
 
@@
     \centering
+    \includegraphics[width=\columnwidth]{mwa0437lowres.png} \\[10pt]
     \includegraphics[width=\columnwidth]{mwa0437hires.png}
-    \caption{[Caption\dots]}
+    \caption{Profiles of PSR \psrbhatJ{} formed from the same data set.
+Top: incoherently de-dispersed with $10\,$kHz (fine) frequency channels formed from the standard PFB analysis filter.
+Bottom: coherently de-dispersed using $1.28\,$MHz (coarse) frequency channels reconstructed using the synthesis filter described in this paper.
+The higher time resolution profile shows features (e.g.
+notches in the total intensity profile at pulse phases $\sim 0.54$ and $\sim 0.7$) that are obscured by dispersion smear at the lower time resolution.
+A comparison with these profiles with that published in Paper I reveals an excess of circular polarisation on both the leading and trailing edges of the profile.
+The reason for the discrepancy is not clear, but it should be noted that the earlier profiles were published before the polarimetric verification of Paper II was carried out.}
     \label{fig:0437}
@@
 
+%\dots
+
 \subsection{PSR \psrslowB{}}
 
-Finally, we observed \psrslowB{}, a bright, slow ($P = 0.253\,$s) pulsar known to show microstructure on time scales of $\sim 60\,\mu$s \citep{Kuzmin2003}.
+\psrslowB{} is a bright, slow ($P = 0.253\,$s) pulsar known to exhibit microstructure \citep{Popov2002,Kuzmin2003}.
 A total of eighty seconds (315 pulses) of data ($128 \times 10\,$kHz fine channels) were recorded, beamformed, and subjected to the polyphase synthesis filter.
@@
     \includegraphics[width=\columnwidth]{5ms_res.eps}
-    \caption{A bright, single pulse of \psrslowB{}, displayed with full polarisation at time resolutions of $\sim 200\,\mu$s (top), $\sim 50\,\mu$s (middle), and $\sim 5\,\mu$s (bottom).}
+    \caption{A bright, single pulse of \psrslowB{}, displayed with full polarisation at time resolutions of $\sim 200\,\mu$s (top), $\sim 50\,\mu$s (middle), and $\sim 5\,\mu$s (bottom).
+The total time span of the displayed windows are $253\,$ms, $25.3\,$ms, and $2.53\,$ms, respectively.}
     \label{fig:0950_single_pulse}
@@
 
-Despite the proximity of this timescale to the temporal ``echoes'' induced by the synthesis filter ($50\mu$s), we were able to clearly identify the ($\sim 60\mu$s) microstructure reported by \citet{Kuzmin2003}.
-We also suggest that the finest observable structures (Fig. \ref{fig:0950_single_pulse}, bottom plot) might correspond to the $\sim 10\,\mu$s structures reported by \citet{Popov2002}.
+Despite the proximity of this timescale to the temporal ``echoes'' induced by the synthesis filter ($50\mu$s), we were able to clearly identify the ($\sim 60\mu$s) microstructure reported by \citet{Kuzmin2003} at $102.5\,$MHz.
+We also suggest that the finest observable structures (Fig. \ref{fig:0950_single_pulse}, bottom plot) might correspond to the $\sim 10\,\mu$s structures reported by \citet{Popov2002} at $1.65\,$GHz.
 However, \citet{Kuzmin2003} used only a single linear polarisation feed, and \citet{Popov2002}, only a left-handed circularly polarised feed.
@@
 \begin{acknowledgements}
+This scientific work uses data obtained from the Murchison Radio-astronomy Observatory. We acknowledge the Wajarri Yamatji people as the traditional owners of the Observatory site.
 This work was supported by resources provided by the Pawsey Supercomputing Centre with funding from the Australian Government and the Government of Western Australia.
@@
 
-The second stage calculates the spectrum of $b[n]$ using the standard fixed point FFT algorithm that is implemented on [make and model] FPGAs.
+The second stage calculates the spectrum of $b[n]$ using the standard fixed point FFT algorithm that is implemented on (Xilinx Virtex4 XC4VSX35) FPGAs.
 The output values are scaled and (symmetrically) rounded, producing (4+4)-bit output values.

### 2020-02-11 ipfb.tex
Added a plot and a paragraph about comparing the synthesis filter to an IFFT. Also amended notes for producing the figures.

@@
 
+We also compared the result of the synthesis filter method with a simple inverse FFT, shown in Fig. \ref{fig:imp_sin_noise}.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{compare_coarse_imp_all.eps}
+    \caption{Similar to Fig.
+\ref{fig:impulse_response}, but showing the real and imaginary parts separately.
+In this case, the original signal is composed of an impulse (real only), a sinusoid (real only), and noise (both real and imaginary).
+Furthermore, the result of an inverse FFT is included for comparison.
+In the residual plots (immediately below the two large panels), the synthesis filter residuals are given a vertical offset to make visual comparison easier.}
+    \label{fig:imp_sin_noise}
+\end{figure}
+The input function consists of a single-bin impulse, a sinusoid, and Gaussian noise.
+Both the PFB synthesis and the inverse FFT are able to reproduce the impulse and the sinusoid, but less perfectly in the case of the inverse FFT method, as evidenced by the residuals.
+Both methods show a similar amount of error in the construction of the Gaussian noise---this is not surprising as replication and quantisation are present at this level.
+
 As a further verification, we also made use of a non-standard observing mode to record a small amount of simultaneous coarse and fine channel data (i.e.
 both before and after the fine PFB analysis filter stage).
-The fine channels from one polarisation of a single tile were extracted and subjected to the synthesis filter to reconstruct the $1.28\,$MHz coarse channel time series, which could then be compared directly with the original data.
-Although not as telling as an impulse response test, the close similarity of the reconstructed (white) noise with the original (see Fig.
-\ref{fig:compare_timeseries}) is indicative of the fidelity of the analysis-synthesis filter pair.
-
-Note that in this test, the FPGA-based fine PFB was used; thus, the errors shown in Fig. \ref{fig:compare_timeseries} do not contain any replication error.
+The fine channels from one polarisation of a single tile were extracted and subjected to the synthesis filter to reconstruct the $1.28\,$MHz coarse channel time series, which could then be compared directly with the original data (see Fig.
+\ref{fig:compare_timeseries}).
 However, the synthesis filter used in production uses an arbitrary scaling factor in order to make better use of the dynamic range afforded by VDIF's (8+8)-bit depth.
 The reconstructed samples shown in the figure have been rescaled by eye for the purposes of visual comparison.
+Because the FPGA-based fine PFB was used in this test, the errors shown in Fig. \ref{fig:compare_timeseries} do not contain any replication error.
+Without replication error, it is readily apparent that the analysis-synthesis pair is able to reproduce the noise remarkably well.
 
@@
 The real (top) and imaginary (bottom) components are shown separately.
-The original coarse channel data (black boxes) are overlaid with the reconstructed data (red lines and dots), with the differences plotted in the lower panels.}
+The original coarse channel data (black boxes) are overlaid with the reconstructed data (red lines and dots), with the residuals plotted in the lower panels.}
     \label{fig:compare_timeseries}
@@
 In this paper, we have presented an algorithm to undo the fine channelisation stage (fine PFB) of the VCS pipeline by using a synthesis polyphase filter, implemented as part of our processing software suite, \vcstools{}.
-The result is a high-fidelity reconstruction of the coarse channelised (pre-PFB) time series, suitable for high-time resolution studies of MSPs and other rapid transient signals.
-Although the reconstruction is not perfect, the introduced errors are quantified (up to $-10\,$dB in certain samples).
+The result is a reconstructed, coarse channelised (pre-PFB) time series, suitable for high-time resolution studies of MSPs and other rapid transient signals.
+Although the reconstruction is not perfect, the introduced errors are quantified (up to $-10\,$dB in certain samples, and no more than $-20\,$dB elsewhere).
 The most significant artefacts, the ``temporal echoes'' of the impulse response, can be identified by virtue of the known timescale of their recurrence ($50\,\mu$s).

### 2020-02-13 ipfb.tex
Added Ramesh's edits.

@@
 \author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$, B. W. Meyers$^{1,2,3}$, S. E. Tremblay, J. Jones$^1$, B. Crosse$^1$
-\affil{$^1$International Centre for Radio Astronomy Research (ICRAR), GPO Box U1987, Perth, WA 6845, Australia}%
+\affil{$^1$International Centre for Radio Astronomy Research (ICRAR), Curtin University, 1 Turner Avenue, Technology Park, Bentley, 6102, W.A., Australia}
 \affil{$^2$CSIRO Astronomy and Space Science, PO Box 76, Epping, NSW 1710, Australia}
@@
 Originally conceived as an imaging telescope (which requires only the time-averaged cross-correlation products of the tiles, or `visibilities', to be retained on disk), it was subsequently augmented with the functionality to capture the raw complex voltages of each tile, known as the Voltage Capture System \citep[VCS;][]{Tremblay2015}.
-This system has enabled the MWA to be used as a premier instrument for high-time resolution studies of transient signals, especially pulsars.
+This system has enabled the MWA to be used as a premier instrument for high-time resolution studies of transient signals, especially pulsars \citep[e.g.][]{Bhat2016,McSweeney2017,Meyers2018}.
 
@@
 
-In the fidelity tests presented in this section, there are therefore a number of sources of error, all of which cause the reconstructed coarse channel time series, $\hat{x}[n]$, to differ from the original input time series, $x[n]$:
+In the fidelity tests presented in this section, we therefore consider a number of sources of error, all of which cause the reconstructed coarse channel time series, $\hat{x}[n]$, to differ from the original input time series, $x[n]$:
 \begin{description}
@@
     \item[``Quantisation error'':] The error associated with the demotion of the input (5+5)-bit complex integers ($x[n]$) to the (4+4)-bit complex integer format output by the PFB (also see Appendix); and
-    \item[``Filter error'':] the error caused by the fact that the synthesis filter ($f[n]$) does not exactly complement the analysis filter ($h[n]$) in the sense described by Eq.
-\eqref{eqn:invertibility_condition}.
+    \item[``Filter error'':] the error caused by the fact that the synthesis filter ($f[n]$) does not exactly complement the analysis filter ($h[n]$), in the sense described by Eq.
+\eqref{eqn:invertibility_condition} and Fig.
+\ref{fig:inverse_condition}.
 \end{description}
@@
 half the size of one tap, equal to $50\,\mu$s for our sampling rate of $1.28\,$MHz) on either side of the reconstructed impulse.
-Although the power in the echoes is small compared to the central impulse (at roughly the $-10\,$dB level), the echoes always appear at the same locations relative to it.
+Although the power in the echoes is small compared to the central impulse (roughly $-10\,$dB level for the innermost echoes), the echoes always appear at the same locations relative to it.
 The asymmetry seen in Fig. \ref{fig:impulse_response} is due to replication error, quantisation error, the ``phase'' of the impulse with respect to the filter window, or some combination of the above.
 Importantly, echoes arising from strong, periodic individual pulses (e.g. in a pulsar signal) will accumulate in the same phase bins when the time series is folded at the pulsar's rotation period.
-Thus, any structure seen on this time scale must therefore be regarded with suspicion.
+Thus, any structure seen on this time scale ($\sim 50\,\mu$s) must therefore be regarded with suspicion.
 
@@
 
-As a further verification, we also made use of a non-standard observing mode to record a small amount of simultaneous coarse and fine channel data (i.e.
+In order to mitigate the replication error, we made use of a non-standard observing mode to record a small amount of simultaneous coarse and fine channel data (i.e.
 both before and after the fine PFB analysis filter stage).
@@
 \ref{fig:compare_timeseries}).
-However, the synthesis filter used in production uses an arbitrary scaling factor in order to make better use of the dynamic range afforded by VDIF's (8+8)-bit depth.
+Because the FPGA-based fine PFB was used in this test, the result is devoid of any replication error.
+However, the synthesis filter used in production uses an arbitrary scaling factor in order to make better use of the dynamic range afforded by VDIF's (8+8)-bit depth, and quantisation error is still present (and, in fact, dominates).
 The reconstructed samples shown in the figure have been rescaled by eye for the purposes of visual comparison.
-Because the FPGA-based fine PFB was used in this test, the errors shown in Fig. \ref{fig:compare_timeseries} do not contain any replication error.
-Without replication error, it is readily apparent that the analysis-synthesis pair is able to reproduce the noise remarkably well.
+Despite this, it is readily apparent that the analysis-synthesis pair is able to reproduce the noise characteristics remarkably well.
 
@@
 
-\section{Verification with pulsar observations}
+\section{Verification using pulsar observations}
 \label{sec:pulsardata}
 
-Pilot observations of three pulsars are presented here to validate the synthesis filter as a useful tool for undertaking high time resolution studies of pulsars: MSPs \psrkaurJ{} and \psrbhatJ{}, and the bright PSR \psrslowB{}.
+Observations of three pulsars are presented here to validate the synthesis filter as a useful tool for undertaking high time resolution studies of pulsars with the MWA: MSPs \psrkaurJ{} and \psrbhatJ{}, and the bright, long-period PSR \psrslowB{}.
 
@@
 
-\psrkaurJ{} has a rotation period of $2.2\,$ms and a dispersion measure (DM) of $11.4\,\dmunits$.
+\psrkaurJ{} has a rotation period of $2.18\,$ms and a dispersion measure (DM) of $11.41\,\dmunits$.
 The resulting dispersion smear across $10\,$kHz channels at the central observing frequency of $150.4\,$MHz is approximately $0.2\,$ms, or $45^\circ$ of rotation phase, consistent with the width of the average profile formed from incoherently de-dispersed, fine channelised data recorded with the MWA-VCS system (Fig.
 \ref{fig:J2241_profiles}, top panel).
-Upon applying the synthesis filter and coherently de-dispersing the reconstructed time series sampled at the much higher rate of $1.28\,$MHz, the same data revealed exquisite detail in the average profile, including a pair of pre-cursor components only marginally visible (if at all) at higher frequencies (Fig.
+Upon applying the synthesis filter and coherently de-dispersing the reconstructed time series sampled at the much higher rate of $1.28\,$MHz, the same data revealed exquisite detail in the average profile, including a pair of pre-cursor components that are only marginally visible (if at all) at higher frequencies (Fig.
 \ref{fig:J2241_profiles}, bottom panel).
-Moreover, these new, low-frequency observations have enabled the DM of this pulsar to be measured to unprecedented precision, with important consequences for measuring DM chromaticity and evaluating its effect on pulsar timing experiments.
+Moreover, these new, low-frequency observations have enabled the DM of this pulsar to be measured to unprecedented precision ($\sim (2$-$6) \times 10^{-6}\,\dmunits$), with important consequences for measuring DM chromaticity and evaluating its effect on pulsar timing experiments.
 These results are discussed in detail in \citet{Kaur2019}.
@@
 The fact that the components only appear on the leading side of the main pulse is a point in favour of them being real, since the temporal artefacts are expected to appear on both leading and trailing sides.
-In addition, the time interval between the main pulse and the closest component is $\sim150\,\mu$s, which, although it corresponds to the expected location of the third-order artefact, is not expected to be brighter than the first two; however, no evidence of the lower-order artefacts is seen.
-Finally, recent independent follow-up observations made by some of the authors using Band 3 ($250$ to $500\,$MHz) of the upgraded Giant Metrewave Radio Telescope (uGMRT) have confirmed that at least the innermost component is real (Kaur et al., in prep).
+In addition, the time interval between the main pulse and the closest component is $\sim150\,\mu$s, which, although it corresponds to the expected location of the third-order artefact, is not expected to be brighter than the first two (see Fig.
+\ref{fig:impulse_response}); however, no evidence of the lower-order artefacts is seen.
+Furthermore, our recent (independent) follow-up observations using the Band 3 receiver ($250$ to $500\,$MHz) of the upgraded Giant Metrewave Radio Telescope (uGMRT) have confirmed that at least the innermost component is real (Kaur et al., in prep).
 
@@
 
-PSR \psrbhatJ{} is a nearby MSP (distance $d \approx 157\,$pc; period $P \approx 5.76\,$ms) and an established target for pulsar timing array (PTA) applications.
+PSR \psrbhatJ{} is a nearby MSP (distance $\approx 157\,$pc; period $P \approx 5.76\,$ms) and an established target for pulsar timing array (PTA) applications.
 It boasts a complex, multi-component polarimetric profile (Fig. \ref{fig:0437}) that spans more than half of its rotation period \citep[cf.][]{Yan2011}.
@@
 
-\psrslowB{} is a bright, slow ($P = 0.253\,$s) pulsar known to exhibit microstructure \citep{Popov2002,Kuzmin2003}.
+\psrslowB{} is a bright, long-period ($P = 0.253\,$s) pulsar known to exhibit microstructure \citep{Popov2002,Kuzmin2003}.
 A total of eighty seconds (315 pulses) of data ($128 \times 10\,$kHz fine channels) were recorded, beamformed, and subjected to the polyphase synthesis filter.
@@
 
-Despite the proximity of this timescale to the temporal ``echoes'' induced by the synthesis filter ($50\mu$s), we were able to clearly identify the ($\sim 60\mu$s) microstructure reported by \citet{Kuzmin2003} at $102.5\,$MHz.
+Using observations at $102.5\,$MHz, \citet{Kuzmin2003} report microstructure with a characteristic timescale of $\sim 60\mu$s.
+Despite the proximity of this timescale to the temporal ``echoes'' induced by the synthesis filter ($50\,\mu$s), we are able to unambiguously identify the $\sim 60\,\mu$s microstructure.
 We also suggest that the finest observable structures (Fig. \ref{fig:0950_single_pulse}, bottom plot) might correspond to the $\sim 10\,\mu$s structures reported by \citet{Popov2002} at $1.65\,$GHz.
@@
 
-The MWA-VCS telescope system outputs dynamic spectra with a frequency resolution of $10\,$kHz and a time resolution of $100\,\mu$s, which is suitable for many pulsar applications, as demonstrated in several pulsar science papers published to date.
+The MWA-VCS telescope system outputs voltage data with a frequency resolution of $10\,$kHz and a time resolution of $100\,\mu$s, which is suitable for many pulsar applications, as demonstrated in several pulsar science papers published to date.
 In this paper, we have presented an algorithm to undo the fine channelisation stage (fine PFB) of the VCS pipeline by using a synthesis polyphase filter, implemented as part of our processing software suite, \vcstools{}.
@@
 
-We have further verified our system by observing PSRs \psrkaurJ{}, \psrbhatJ{}, and \psrslowB{}, all of which are known to exhibit structures on microsecond timescales.
-In each case, our results have been shown to be consistent with observations at higher radio frequencies.
+We have further verified our system by observing PSRs \psrkaurJ{}, \psrbhatJ{}, and \psrslowB{}, all of which are known to exhibit structures on $\sim 1$-$10\,\mu$s timescales.
+In each case, our results have been shown to be consistent with observations at other radio frequencies.
 In particular, we have demonstrated that the errors introduced by the imperfect analysis-synthesis filter pair are negligible compared to the pulsar signals themselves, which have been reconstructed with full polarisation at the faster sampling rate ($1.28\,$MHz) with high fidelity.
-The advent of the VCS high time resolution observing mode thus distinguishes the MWA as a premier low-frequency instrument for studying pulsars and other transients at microsecond precision, with important implications for studies of the pulsar emission mechanism, the characterisation of the ISM in the ongoing search for gravitational waves, and others.
+The advent of the VCS high time resolution observing mode thus distinguishes the MWA as a premier low-frequency instrument for studying pulsars and other transients at microsecond resolution, with important implications for studies of the pulsar emission mechanism, the characterisation of the ISM in the ongoing search for gravitational waves, and others.
 
@@
 This scientific work uses data obtained from the Murchison Radio-astronomy Observatory. We acknowledge the Wajarri Yamatji people as the traditional owners of the Observatory site.
-This work was supported by resources provided by the Pawsey Supercomputing Centre with funding from the Australian Government and the Government of Western Australia.
+Support for the operation of the MWA is provided by the Australian Government (NCRIS), under a contract with Curtin University administered by Astronomy Australia Limited.
+SM acknowledges the contribution of an Australian Government Research Training Program Scholarship in supporting this research.
+DK acknowledges support from both the Curtin International Postgraduate Research Scheme and the NANOGrav project, which receives support from NSF Physics Frontier Center award number 1430284.
+This work was further supported by resources provided by the Pawsey Supercomputing Centre with funding from the Australian Government and the Government of Western Australia.
 \end{acknowledgements}

### 2020-03-05 ipfb.tex
Incorporated the suggestions from Clancy and Franz

@@
 Originally conceived as an imaging telescope (which requires only the time-averaged cross-correlation products of the tiles, or `visibilities', to be retained on disk), it was subsequently augmented with the functionality to capture the raw complex voltages of each tile, known as the Voltage Capture System \citep[VCS;][]{Tremblay2015}.
-This system has enabled the MWA to be used as a premier instrument for high-time resolution studies of transient signals, especially pulsars \citep[e.g.][]{Bhat2016,McSweeney2017,Meyers2018}.
+This system has enabled the MWA to be used as a premier instrument for high-time resolution studies of transient signals, especially pulsars \citep[e.g.][]{Bhat2016,McSweeney2017,Meyers2018,Kirsten2019}.
 
@@
 width, location of sidelobes) are chosen according to the advantages they carry in particular contexts.
-Leaving $x[n]$ ``unweighted'' is equivalent to choosing $h[n] = w_R[n]$, in which case Eq. \eqref{eqn:wdft} is also called the short-time Fourier transform (STFT).
+Leaving $x[n]$ ``unweighted'' is equivalent to choosing $h[n] = w_R[n]$, in which case Eq.
+\eqref{eqn:wdft} merely describes a DFT performed on each successive window, which in this context is also called a short-time Fourier transform (STFT).
 On the other hand, choosing $h[n]$ to be the $\sinc$ function will result in a frequency response that approximates a rectangular window.
@@
 The procedure described by Eq. \eqref{eqn:pfb} is called the \textit{weighted overlap-add} algorithm, and is illustrated in Fig. \ref{fig:pfb}.
-\begin{figure}[t]
+\begin{figure}[p]
     \centering
+    (a) \\
+    \includegraphics[width=\columnwidth]{cartoon-top.eps} \\
+    (b) \\
     \includegraphics[width=\columnwidth]{cartoon.eps}
@@
 \eqref{eqn:pfb}.
-A discrete signal containing a sinusoid and noise (top row) is multiplied by a filter (second and third rows), and each ``tap'' (represented by columns) is summed (bottom left) and Fourier transformed to produce the final spectrum (bottom right).}
+Panel (a) shows the filter window being translated along a discretely sampled signal (in this case, containing a sinusoid and noise) with a step size of one tap.
+At each step, panel (b) shows how the signal (first row) is multiplied by a filter (second and third rows), and each tap is summed (bottom left) and Fourier transformed to produce the final spectrum (bottom right).}
     \label{fig:pfb}
@@
 
-The major challenge in verifying the fidelity of the back-to-back analysis-synthesis filter pair is the fact that the analysis PFB only exists on the FPGAs used in production and not as stand-alone software than can be fed arbitrary input.
+The major challenge in verifying the fidelity of the back-to-back analysis-synthesis filter pair is the fact that the analysis PFB only exists on the FPGAs used in production and not as stand-alone software that can be fed arbitrary input.
 This makes conducting standard impulse response tests impossible, unless the exact performance of the PFB can be reproduced.
-We have therefore attempted to replicate the PFB in software; however, the replication was not perfect, causing a small difference between the our model analysis-synthesis back-to-back system, and the analysis-synthesis system used in production.
+We have therefore attempted to replicate the PFB in software; however, the replication was not perfect, causing a small difference between the model analysis-synthesis back-to-back system, and the analysis-synthesis system used in production.
 
@@
 
-We also compared the result of the synthesis filter method with a simple inverse FFT, shown in Fig. \ref{fig:imp_sin_noise}.
+We also compared the result of the synthesis filter method with a simple 128-point inverse FFT, shown in Fig. \ref{fig:imp_sin_noise}.
 \begin{figure}
@@
 \ref{fig:impulse_response}, but showing the real and imaginary parts separately.
-In this case, the original signal is composed of an impulse (real only), a sinusoid (real only), and noise (both real and imaginary).
-Furthermore, the result of an inverse FFT is included for comparison.
-In the residual plots (immediately below the two large panels), the synthesis filter residuals are given a vertical offset to make visual comparison easier.}
+In this case, the original signal is composed of an impulse (real only), a sinusoid (real only), and noise (both real and imaginary), and subsequently quantised.
+The results of both the PFB synthesis and the inverse FFT are plotted for comparison.
+For each series, a vertical offset is added to make visual comparison easier.
+The PFB synthesis method is better at reconstructing the impulse and the sinusoid, but quantisation error dominates the noise for both PFB and FFT methods.}
     \label{fig:imp_sin_noise}
@@
 Both the PFB synthesis and the inverse FFT are able to reproduce the impulse and the sinusoid, but less perfectly in the case of the inverse FFT method, as evidenced by the residuals.
-Both methods show a similar amount of error in the construction of the Gaussian noise---this is not surprising as replication and quantisation are present at this level.
+The difference between the two methods can be understood as the direct consequence of the differences between the spectral response of the forward PFB and an ordinary FFT.
+Another way to say this is that the synthesis filter, $f[n]$, that corresponds to the inverse FFT is even less well matched to the analysis PFB filter, in the sense of Eq.
+\eqref{eqn:invertibility_condition}, than the synthesis filter defined in Eq.
+\eqref{eqn:synthesisfilter}.
+Notably, if an FFT had been used in the MWA's fine channelisation stage (i.e.
+instead of the PFB), the inverse FFT would exactly reproduce the original high time resolution time series, even though the spectrum produced by the forward FFT would be a less perfect representation of the true spectrum, due to more prevalent spectral leakage (i.e.
+compared to the PFB).
+Finally, note that both the synthesis filter method and the inverse FFT show a similar amount of error in the construction of the Gaussian noise (cf.
+the imaginary component shown in Fig.
+\ref{fig:imp_sin_noise})---this is not surprising as replication and quantisation errors are present at this level.
 
@@
 However, the synthesis filter used in production uses an arbitrary scaling factor in order to make better use of the dynamic range afforded by VDIF's (8+8)-bit depth, and quantisation error is still present (and, in fact, dominates).
-The reconstructed samples shown in the figure have been rescaled by eye for the purposes of visual comparison.
-Despite this, it is readily apparent that the analysis-synthesis pair is able to reproduce the noise characteristics remarkably well.
+Nevertheless, the agreement between the reconstructed samples and the original is very good, with both real and imaginary components having a correlation coefficient of approximately $0.94$.
+
+Despite the errors in the reconstruction, the analysis-synthesis pair is able to reproduce the noise characteristics well enough for the errors not to significantly affect sufficiently bright pulsar signals, as demonstrated in the next section.
+However, these errors may become significant when observing low SNR pulsar emission.
+In these cases, the errors may be mitigated by averaging over multiple time bins (e.g.
+a coarser time resolution, or averaging many pulses together).
 
@@
 The real (top) and imaginary (bottom) components are shown separately.
-The original coarse channel data (black boxes) are overlaid with the reconstructed data (red lines and dots), with the residuals plotted in the lower panels.}
+The original coarse channel data (black) are compared with the reconstructed data (red), with the residuals plotted in the lower panels.
+Because the VDIF data uses an arbitrary scaling factor, the red line has been rescaled by eye for a better visual comparison.}
     \label{fig:compare_timeseries}
@@
 \ref{fig:J2241_profiles}, bottom panel).
-Moreover, these new, low-frequency observations have enabled the DM of this pulsar to be measured to unprecedented precision ($\sim (2$-$6) \times 10^{-6}\,\dmunits$), with important consequences for measuring DM chromaticity and evaluating its effect on pulsar timing experiments.
+Moreover, these new, low-frequency observations have allowed us to measure the DM of this pulsar with unprecedented precision ($\sim (2$-$6) \times 10^{-6}\,\dmunits$), with important consequences for measuring DM chromaticity and evaluating its effect on pulsar timing experiments.
 These results are discussed in detail in \citet{Kaur2019}.
@@
     \centering
-    \includegraphics[width=\columnwidth]{mwa0437lowres.png} \\[10pt]
-    \includegraphics[width=\columnwidth]{mwa0437hires.png}
+    \includegraphics[angle=270,width=\columnwidth]{mwa0437lowres.eps} \\[10pt]
+    \includegraphics[angle=270,width=\columnwidth]{mwa0437hires.eps}
     \caption{Profiles of PSR \psrbhatJ{} formed from the same data set.
@@
 This work was further supported by resources provided by the Pawsey Supercomputing Centre with funding from the Australian Government and the Government of Western Australia.
+We would also like to thank Ian Morrison, Franz Kirsten, and Clancy James for reviewing this manuscript and offering several helpful suggestions to improve it.
 \end{acknowledgements}

### 2020-05-06 filtercoeffs.py
Started trying to actually calculate the inverse of the PFb filter

@@ -57,7 +57,11 @@ axs[0].set_xlim([0,1536])
 
 ctr = N//2 - 1
 f = (np.arange(N) - ctr)/P * 10 # i.e. 10 kHz
-fftr = np.roll(np.abs(np.fft.fft(s*hn)), ctr)
+fft = np.fft.fft(s*hn)
+fftr = np.roll(np.abs(fft), ctr)
+fftth = np.roll(np.angle(fft), ctr)
+fftre = np.roll(np.real(fft), ctr)
+fftim = np.roll(np.imag(fft), ctr)
 dB = 10*np.log10(fftr/max(fftr))
 axs[1].plot(f, dB, 'k-')
 for fshift in [-10, 10]:
@@ -73,3 +77,8 @@ axs[0].legend(loc='upper right')
 #plt.show()
 plt.tight_layout()
 plt.savefig("filter.eps", bbox_inches='tight')
+
+plt.figure(2)
+plt.plot(fftre, fftim, 'r.')
+plt.xlim([-30,30])
+plt.show()

### 2020-05-06 find_inverse.py

@@ -45,32 +45,3 @@ cb.set_label("$\\lambda(s)$")
 #plt.savefig("inverse_condition.eps", bbox_inches='tight')
 
 plt.show()
-
-
-'''
-# Analysis-synthesis response of an impulse
-nsamples = K*64
-x_ntaps  = nsamples//K - ntaps
-x = np.zeros(nsamples)
-x[nsamples//3] = 1 # Put an impulse right smack bang in the middle
-ns = np.arange(nsamples)
-x = np.cos(2*ns)
-
-X = np.array([[np.sum(h(m*M-ns) * x * np.exp(-2j*np.pi*k*ns/K)) for m in range(x_ntaps)] for k in range(K)])
-X = np.roll(X, K//2, axis=0)
-
-ks = np.arange(K)
-ms = np.arange(x_ntaps)
-NS, KS, MS = np.meshgrid(ns, ks, ms)
-#xhat = [np.sum([f(n-m*M) / K * np.sum(X[:,m] * np.exp(2j*np.pi*ks*n/K)) for m in range(x_ntaps)]) for n in ns]
-xhat = f(NS-MS*M) / K
-print(xhat.shape)
-
-fig, ax = plt.subplots(3,1)
-im1 = ax[0].imshow(np.abs(X), aspect='auto')
-im2 = ax[1].imshow(np.angle(X), cmap='hsv', aspect='auto')
-im3 = ax[2].plot(x)
-#plt.colorbar(im1)
-#plt.colorbar(im2)
-plt.show()
-'''

### 2020-05-06 find_inverse.py
Successful calculation of the least squares solution of the inverse (synthesis) filter.

@@ -22,20 +22,62 @@ def f(n):
     H = np.sum(h(ns))
     return h(-n)
 
+# Get the least squared solution
+Fhat = np.zeros((ntaps, M))
+for n in range(M):
+    # Try and find the inverse to the analysis filter, h(n)
+    # Step 1: Create H array:
+    #    [ h(n+11*M)      0          0         ...    ]
+    #    [ h(n+10*M)  h(n+11*M)      0         ...    ]
+    #    [ h(n+ 9*M)  h(n+10*M)  h(n+11*M)     ...    ]
+    #    [    ...        ...        ...        ...    ]
+    #    [    ...     h(n+ 0*M)  h(n+ 1*M)  h(n+ 2*M) ]
+    #    [    ...         0      h(n+ 0*M)  h(n+ 1*M) ]
+    #    [    ...         0          0      h(n+ 0*M) ]
+    ncols = ntaps
+    nrows = 2*ntaps - 1
+    H = np.zeros((nrows, ncols))
+    for i in range(nrows):
+        if i < ntaps:
+            H[i,0:(i+1)] = [h(n + m*M) for m in range(ntaps - i - 1, ntaps)]
+        else:
+            H[i,(i-ntaps+1):] = [h(n + m*M) for m in range(nrows - i)]
+
+    # Now, we want to solve the matrix equation HF = D for F,
+    # where D is the "Kronecker delta"
+    D = np.zeros((nrows, 1))
+    D[ntaps-1] = 1
+    if n == 0:
+        print(D)
+
+    # The least squares solution is
+    HT        = np.transpose(H)
+    HTH       = np.matmul(HT, H)
+    HTD       = np.matmul(HT, D)
+    invHTH    = np.linalg.pinv(HTH)
+    Fhat[:,n:n+1] = np.matmul(invHTH, HTD)
+
+plt.figure("Least squares")
+F = Fhat.flatten()
+ns = np.arange(N)
+plt.plot(ns, h(ns), label='Analysis filter')
+plt.plot(ns, F, label="Least squares sol'n")
+#plt.plot(ns,f(ns), label='Mirror filter')
+plt.legend()
+plt.show()
+
+#plt.show()
+
 # Calculate λ(s) from h[n] and f[n]
+'''
 ns = np.arange(N)
 ss = np.arange(-12,13)
 ms = np.arange(M)
[…]

### 2020-05-06 filtercoeffs.py
Added some commented-out code to plot the frequency response of the inverse filter.

@@ -1,4 +1,3 @@
-from scipy import hanning
 import numpy as np
 import matplotlib.pyplot as plt
 
@@ -16,7 +15,7 @@ def create_fine_PFB_filter(nchans, ntaps):
     x = (n + 1 - N/2)/nchans
 
     sinc = np.sinc(x)
-    hn   = hanning(N+1)[1:]
+    hn   = np.hanning(N+1)[1:]
     h    = sinc*hn
     return h, n, hn, sinc
 
@@ -59,9 +58,6 @@ ctr = N//2 - 1
 f = (np.arange(N) - ctr)/P * 10 # i.e. 10 kHz
 fft = np.fft.fft(s*hn)
 fftr = np.roll(np.abs(fft), ctr)
-fftth = np.roll(np.angle(fft), ctr)
-fftre = np.roll(np.real(fft), ctr)
-fftim = np.roll(np.imag(fft), ctr)
 dB = 10*np.log10(fftr/max(fftr))
 axs[1].plot(f, dB, 'k-')
 for fshift in [-10, 10]:
@@ -73,12 +69,18 @@ axs[1].set_xlim([-30,30])
 axs[1].set_ylim([-60, 5])
 plt.grid(True)
 
+'''
+# Plot FFT of least squares synthesis filter
+F = np.loadtxt("rinv.txt")
+print(F)
+Ffft = np.fft.fft(F)
+Ffftr = np.roll(np.abs(Ffft), ctr)
+FdB = 10*np.log10(Ffftr/max(Ffftr))
+axs[1].plot(f, FdB, 'b-')
+'''
+
 axs[0].legend(loc='upper right')
 #plt.show()
 plt.tight_layout()
 plt.savefig("filter.eps", bbox_inches='tight')
 
-plt.figure(2)
-plt.plot(fftre, fftim, 'r.')
-plt.xlim([-30,30])
-plt.show()

### 2020-05-06 find_inverse.py

@@ -1,3 +1,4 @@
+import sys
 import numpy as np
 import matplotlib.pyplot as plt
 
@@ -47,8 +48,6 @@ for n in range(M):
     # where D is the "Kronecker delta"
     D = np.zeros((nrows, 1))
     D[ntaps-1] = 1
-    if n == 0:
-        print(D)
 
     # The least squares solution is
     HT        = np.transpose(H)
@@ -62,29 +61,14 @@ F = Fhat.flatten()
 ns = np.arange(N)
 plt.plot(ns, h(ns), label='Analysis filter')
 plt.plot(ns, F, label="Least squares sol'n")
-#plt.plot(ns,f(ns), label='Mirror filter')
 plt.legend()
-plt.show()
-
+plt.tight_layout()
+plt.savefig("rinv.png")
 #plt.show()
 
-# Calculate λ(s) from h[n] and f[n]
-'''
-ns = np.arange(N)
-ss = np.arange(-12,13)
-ms = np.arange(M)
-NS, SS, MS = np.meshgrid(ns, ss, ms)
-lmda = np.sum(f(NS - MS*M) * h(MS*M - NS + SS*M), axis=2)
-'''
+# Write out the spectrum to rinv.txt
+header =  "Synthesis filter coefficients obtained by least squares solution to inverse analysis filter"
+header += "Generated by\n"
+header += "python" + " ".join(sys.argv)
+np.savetxt("rinv.txt", F, header=header)
 
-'''
-plt.figure(2)
-plt.imshow(lmda, aspect='auto', interpolation='None', origin='lower', extent=[-0.5,N+0.5,ss[0]-0.5,ss[-1]+0.5])
-cb = plt.colorbar()
-plt.xlabel("$n$")
-plt.ylabel("$s$")
-cb.set_label("$\\lambda(s)$")
-#plt.savefig("inverse_condition.eps", bbox_inches='tight')
-
-plt.show()
-'''

### 2020-05-08 find_inverse.py
Added code (and a figure or two) for calculating the inverse filter.

@@ -24,46 +24,68 @@ def f(n):
     return h(-n)
 
 # Get the least squared solution
-Fhat = np.zeros((ntaps, M))
-for n in range(M):
+Ftaps = ntaps + 12 # Number of taps in output filter
+Hsize = (2*ntaps - 1, Ftaps)
+Href = (Hsize[0] // 2, Hsize[1] // 2 - ntaps // 2)
+
+Fhat = np.zeros((Hsize[1], K))
+Dhat = np.zeros((Hsize[0], K))
+for n in range(K):
     # Try and find the inverse to the analysis filter, h(n)
-    # Step 1: Create H array:
-    #    [ h(n+11*M)      0          0         ...    ]
-    #    [ h(n+10*M)  h(n+11*M)      0         ...    ]
-    #    [ h(n+ 9*M)  h(n+10*M)  h(n+11*M)     ...    ]
-    #    [    ...        ...        ...        ...    ]
-    #    [    ...     h(n+ 0*M)  h(n+ 1*M)  h(n+ 2*M) ]
-    #    [    ...         0      h(n+ 0*M)  h(n+ 1*M) ]
-    #    [    ...         0          0      h(n+ 0*M) ]
-    ncols = ntaps
-    nrows = 2*ntaps - 1
-    H = np.zeros((nrows, ncols))
-    for i in range(nrows):
-        if i < ntaps:
-            H[i,0:(i+1)] = [h(n + m*M) for m in range(ntaps - i - 1, ntaps)]
-        else:
-            H[i,(i-ntaps+1):] = [h(n + m*M) for m in range(nrows - i)]
+    # Step 1: Create H array, e.g.,
+    #          <----------------  Hsize[1] ----------------->
+    #    ^     [ h(n+11*M)      0          0         ...    ]
+    #    |     [ h(n+10*M)  h(n+11*M)      0         ...    ]
+    #    |     [ h(n+ 9*M)  h(n+10*M)  h(n+11*M)     ...    ]
+    # Hsize[0] [    ...        ...        ...        ...    ]
+    #    |     [    ...     h(n+ 0*M)  h(n+ 1*M)  h(n+ 2*M) ]
+    #    |     [    ...         0      h(n+ 0*M)  h(n+ 1*M) ]
+    #    v     [    ...         0          0      h(n+ 0*M) ]
+    H = np.zeros(Hsize)
+    Mmat = np.zeros(Hsize)
[…]

### 2020-05-08 find_inverse.py
Made find_inverse.py calculate the errors for a bunch of different filters all at once, not just one at a time

@@ -23,73 +23,119 @@ def f(n):
     H = np.sum(h(ns))
     return h(-n)
 
-# Get the least squared solution
-Ftaps = ntaps + 12 # Number of taps in output filter
-Hsize = (2*ntaps - 1, Ftaps)
-Href = (Hsize[0] // 2, Hsize[1] // 2 - ntaps // 2)
+# Find some synthesis filters!
+filter_types = ["Mirror", 12, 18, 24]
+SNR = np.zeros((len(filter_types), K))
 
-Fhat = np.zeros((Hsize[1], K))
-Dhat = np.zeros((Hsize[0], K))
-for n in range(K):
-    # Try and find the inverse to the analysis filter, h(n)
-    # Step 1: Create H array, e.g.,
-    #          <----------------  Hsize[1] ----------------->
-    #    ^     [ h(n+11*M)      0          0         ...    ]
-    #    |     [ h(n+10*M)  h(n+11*M)      0         ...    ]
-    #    |     [ h(n+ 9*M)  h(n+10*M)  h(n+11*M)     ...    ]
-    # Hsize[0] [    ...        ...        ...        ...    ]
-    #    |     [    ...     h(n+ 0*M)  h(n+ 1*M)  h(n+ 2*M) ]
-    #    |     [    ...         0      h(n+ 0*M)  h(n+ 1*M) ]
-    #    v     [    ...         0          0      h(n+ 0*M) ]
-    H = np.zeros(Hsize)
-    Mmat = np.zeros(Hsize)
-    for i in range(Hsize[0]):
-        for j in range(Hsize[1]):
-            m = (j - i) - (Href[1] - Href[0])
-            #Mmat[i,j] = m
-            H[i,j] = h(n + m*M)
+for a in range(len(filter_types)):
 
-    # Now, we want to solve the matrix equation HF = D for F,
-    # where D is the "Kronecker delta"
-    D = np.zeros((Hsize[0], 1))
-    D[ntaps-1] = 1
+    filter_size = filter_types[a]
 
-    # H is non-square
-    HT        = np.transpose(H)
-    HTH       = np.matmul(HT, H)
-    HTD       = np.matmul(HT, D)
-    invHTH    = np.linalg.pinv(HTH)
-    Fhat[:,n:n+1] = np.matmul(invHTH, HTD)
-    #Fhat[:,n] = [h(n + m*M) for m in range(Ftaps)] # Set synth filter = analysis filter
[…]

### 2020-05-08 ipfb.tex
Updated draft of paper text in partial response of the referee's comments

@@
 \newcommand{\dmunits}{\ensuremath{\text{pc}\,\text{cm}^{-3}}}
+
+\newcommand{\changes}[1]{{\color{red}#1}}
 
@@
 
-\subsection{Design}
-
-The spectral output of the PFB, $X_k[m]$, can be used to reconstruct the time series $\hat{x}[n]$ by means of a \textit{synthesis filter}.
-The hat signifies the fact that the resulting time series does not necessarily equal the original input to the PFB, $x[n]$, since one is free to choose the synthesis filter itself, $f$:
+In order to regain the time resolution lost during analysis, the spectral output of the PFB must be transformed back into the time domain.
+The inverse to the analysis operation defined in Eq. \eqref{eqn:wdft} converts a spectrum $X_k[m]$ into a time series $\hat{x}[n]$ by means of a \textit{synthesis filter}, $f[n]$:
 \begin{equation}
-    \hat{x}[n] = \sum_{m = 0}^{M-1} f[n - mM]\,
+    \hat{x}[n] = \sum_{m = -\infty}^{\infty} f[n - mM]\,
         \frac{1}{K} \sum_{k=0}^{K-1} X_k[m]\,e^{2\pi jkn/K}.
@@
 \end{equation}
-The necessary and sufficient condition for exact equality, $\hat{x}[n] = x[n]$, for a critically sampled PFB is \citep[proven in][]{Crochiere1983}:
+In this expression, the index $m$ is allowed to run over all integers in order accommodate an arbitrarily large synthesis filter.
+
+Back-to-back analysis-synthesis filters can be designed so that the original time series can be perfectly reconstructed without any loss of signal (i.e.
+$\hat{x}[n] = x[n]$ exactly), and the system as a whole can be thought of as an identity operation.
+The condition for perfect reconstruction can be found by substituting the analysed spectrum obtained from Eq. \eqref{eqn:wdft} into the synthesis operation defined in Eq. \eqref{eqn:ipfb}.
+It can be shown that, for a critically sampled system,
 \begin{equation}
-    \lambda(s) = \sum_{m=0}^{M-1} f[n-mM]\,h[mM - n + sM] = \Kron
+    \begin{aligned}
+        \hat{x}[n]
+            &= \sum_{s = -\infty}^{\infty} x[n - sM]
+               \sum_{m = -\infty}^{\infty} f_m[n]\, h_m[sM - n] \\
+            &= x[n] \sum_{m = -\infty}^{\infty} f_m[n]\, h_m[-n] +{} \\
+            &\quad \sum_{\substack{s = -\infty \\ s \ne 0}}^{\infty} x[n - sM]
+               \sum_{m = -\infty}^{\infty} f_m[n]\, h_m[sM - n]
+    \end{aligned}
+    \label{eqn:backtoback}
+\end{equation}
+where, following \citet{Crochiere1983}, we have adopted the shorthand notation
+\begin{equation}
+    \begin{aligned}
+        h_m[n] &\equiv h[n - mM], \\
+        f_m[n] &\equiv f[n - mM].
+    \end{aligned}
+\end{equation}
+It can be seen that perfect reconstruction corresponds to the case when the only non-zero contribution comes from the $s = 0$ term, giving rise to the necessary and sufficient condition
+\begin{equation}
+    \sum_{m = -\infty}^{\infty} f[n-mM]\,h[(m - s)M - n] = \Kron
     \label{eqn:invertibility_condition}
@@
 for all values of $n$, where $\Kron$ is the Kronecker delta.
-Eq.
-\eqref{eqn:invertibility_condition} formally resembles a kind of ``convolution'' of the synthesis filter with the analysis filter, where the translational part of the convolution operation is restricted to step sizes of $M$.
+
+Finding the synthesis filter that perfectly inverts a given analysis filter is tantamount to solving Eq. \eqref{eqn:invertibility_condition} for $f[n]$.
+However, exact solutions do not always exist, and in general, numerical methods must be employed to find a synthesis filter that minimises the reconstruction error.
+
+\subsection{Reconstruction error}
+
+In the context of an astrophysical signal, it is desirable to quantify the reconstruction error in terms of the signal-to-noise ratio (S/N).
+If we assume that individual samples follow, and are dominated by, the same Gaussian noise statistics, then the reduction in S/N of a reconstructed sample can be estimated by considering the fraction of the power of the reconstructed sample that came from the original sample:
+\begin{equation}
+    \frac{[\text{S/N}]_\text{recon}}{[\text{S/N}]_\text{orig}}
+      = \frac{\left(\sum\limits_{m = -\infty}^{\infty} f_m[n]\,h_m[-n]\right)^2}{
+            \sum\limits_{s = -\infty}^{\infty}
+            \left(\sum\limits_{m = -\infty}^{\infty} f_m[n]\,h_m[sM - n]\right)^2
+        }
+\end{equation}
+This expression is invariant under the substitution $n \rightarrow n + \lambda M$, $\lambda \in \mathbb{Z}$, which indicates that the (average) reconstruction error is only a function of where the sample in question falls within a tap.
+Consequently, any synthesis filter (except the exact inverse of the analysis filter, if it exists) will introduce a ``ringing'' effect into the reconstructed time series that has a period equal to the size of the PFB tap.
+
+\subsection{Design constraints}
+
+Eq. \eqref{eqn:backtoback} suggests that a reconstructed time sample potentially contains contributions from up to $P$ original samples, spaced at intervals of one tap.
 
@@
 The quantitative effect of this analysis-synthesis pair is discussed in Section \ref{sec:fidelity}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{inverse_condition.eps}
-    \caption{The condition for invertibility, Eq.
+
+%\begin{figure}
+%    \centering
+%    \includegraphics[width=\columnwidth]{inverse_condition.eps}
+%    \caption{The condition for invertibility, Eq.
 \eqref{eqn:invertibility_condition}, demonstrated for the analysis filter given in Eq.
@@
 \ref{fig:impulse_response}.}
-    \label{fig:inverse_condition}
+%    \label{fig:inverse_condition}
+%\end{figure}
+
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{snr.eps}
+    \caption{The reconstructed S/N as a function of the position of the reconstructed sample within a tap.}
+    \label{fig:snr}
 \end{figure}

### 2020-05-09 ipfb.tex
Wrote up how to find the least squares solution, and also made the SNR plot pretty

@@
 
-\section{Synthesis filter}
+\section{Synthesis filters}
 \label{sec:ipfb}
@@
 The condition for perfect reconstruction can be found by substituting the analysed spectrum obtained from Eq. \eqref{eqn:wdft} into the synthesis operation defined in Eq. \eqref{eqn:ipfb}.
-It can be shown that, for a critically sampled system,
+For a critically sampled system,
 \begin{equation}
@@
             &= \sum_{s = -\infty}^{\infty} x[n - sM]
-               \sum_{m = -\infty}^{\infty} f_m[n]\, h_m[sM - n] \\
+               \sum_{m = -\infty}^{\infty} f_m[n]\, h_{m-s}[-n] \\
             &= x[n] \sum_{m = -\infty}^{\infty} f_m[n]\, h_m[-n] +{} \\
             &\quad \sum_{\substack{s = -\infty \\ s \ne 0}}^{\infty} x[n - sM]
-               \sum_{m = -\infty}^{\infty} f_m[n]\, h_m[sM - n]
+               \sum_{m = -\infty}^{\infty} f_m[n]\, h_{m-s}[-n]
     \end{aligned}
@@
     \begin{aligned}
-        h_m[n] &\equiv h[n - mM], \\
-        f_m[n] &\equiv f[n - mM].
+        h_\lambda[n] &\equiv h[n - \lambda M], \\
+        f_\lambda[n] &\equiv f[n - \lambda M].
     \end{aligned}
+    \notag
 \end{equation}
@@
 \begin{equation}
-    \sum_{m = -\infty}^{\infty} f[n-mM]\,h[(m - s)M - n] = \Kron
+    \sum_{m = -\infty}^{\infty} f_m[n]\,h_{m-s}[-n] = \Kron
     \label{eqn:invertibility_condition}
@@
             \sum\limits_{s = -\infty}^{\infty}
-            \left(\sum\limits_{m = -\infty}^{\infty} f_m[n]\,h_m[sM - n]\right)^2
-        }
+            \left(\sum\limits_{m = -\infty}^{\infty} f_m[n]\,h_{m-s}[-n]\right)^2
+        }.
 \end{equation}
@@
 
-\subsection{Design constraints}
+\subsection{Optimal and sub-optimal filter designs}
 
-Eq. \eqref{eqn:backtoback} suggests that a reconstructed time sample potentially contains contributions from up to $P$ original samples, spaced at intervals of one tap.
+Minimising the loss of S/N is equivalent to solving Eq. \eqref{eqn:invertibility_condition} in a least squares sense.
+Since any given reconstructed sample only receives contributions from samples spaced one tap apart, Eq.
+\eqref{eqn:invertibility_condition} can be thought of as $M$ independent conditions, one for each tap position, $n = 0, 1, 2, \dots, M-1$.
+Thus, considering each tap position separately, each condition can be expressed as a minimal matrix equation,
+\begin{equation}
+    H^{(n)}F^{(n)} = D,
+\end{equation}
+where $H^{(n)}$, $F^{(n)}$, and $D$ are matrices whose elements are given by
+\begin{equation}
+    \begin{aligned}
+        H^{(n)}_{ij} &= h_{P-1+j-i}[-n], \\
+        F^{(n)}_j    &= f_j[n], \\
+        D_i          &= \delta^{P-1}_i,
+    \end{aligned}
+\end{equation}
+where $P$ is the number of taps in the analysis filter, and the size of $F^{(n)}$ is set to the desired number of (non-zero) taps in the synthesis filter, $P^\prime$.
+The indices are chosen such that, owing to the finite size of the analysis filter, the smallest $H^{(n)}$ that captures every non-trivial term in Eq.
+\eqref{eqn:invertibility_condition} is the $(P^\prime+P-1) \times P^\prime$ matrix
+\begin{equation}
+    H^{(n)} =
+    \begin{bmatrix}
+       h_{P-1}[-n] & 0 & \cdots & 0 \\
+       h_{P-2}[-n] & h_{P-1}[-n] & \cdots & 0 \\
+       \vdots & & \ddots & \vdots \\
+       h_0[-n] & h_1[-n] & \cdots & h_{P-1}[-n] \\
+       \vdots & & \ddots & \vdots \\
+       0 & \cdots & h_0[-n] & h_1[-n] \\
+       0 & \cdots & 0 & h_0[-n]
+    \end{bmatrix},
+\end{equation}
+with row number $i = P - 1$ (in $H^{(n)}$ and $D$) corresponding to the $s = 0$ term.
 
-Whether this condition is perfectly met clearly depends on the choice of analysis and synthesis filters.
-However, even a synthesis filter which only approximately satisfies Eq.
-\eqref{eqn:invertibility_condition} for a given analysis filter (i.e.
-$\lambda(s) \approx \Kron$) will produce a time series that approximates the original coarse channel time series (i.e.
-$\hat{x}[n] \approx x[n]$).
-In practice, the choice of synthesis filter is often obliged to be a compromise between ease of implementation and an acceptable level of imperfection in the reconstructed time series.
+Once the matrices $H^{(n)}$, $F^{(n)}$, and $D$ have been defined, solution by least squares regression can proceed in the usual way, yielding the best-fit filter coefficients
+\begin{equation}
+    \hat{F}^{(n)} = \left({H^{(n)}}^T H^{(n)}\right)^{-1} {H^{(n)}}^T D,
+\end{equation}
+where ${H^{(n)}}^T$ is the transpose of $H^{(n)}$.
+With this notation, the reconstruction error can be more simply expressed
+\begin{equation}
+    \frac{[\text{S/N}]_\text{recon}}{[\text{S/N}]_\text{orig}}
+      = \frac{(\hat{D}_{P-1})^2}{\hat{D}^T \hat{D}},
+    \label{eqn:snr_short}
+\end{equation}
+where $\hat{D} = H^{(n)} \hat{F}^{(n)}$.
 
-For the analysis filter $h[n]$ defined in Eq. \eqref{eqn:filter}, it is found that choosing the synthesis filter
-\begin{equation}
-    f[n] = \frac{h[-n]}{H}
-    \label{eqn:synthesisfilter}
-\end{equation}
-where $H = \sum_{n=0}^{N-1} h[n]$ is a normalising factor, meets the invertibility condition sufficiently closely for our purposes, as demonstrated below.
-With the analysis and synthesis filters thus defined, the value of Eq. \eqref{eqn:invertibility_condition} can be calculated and is illustrated in Fig. \ref{fig:inverse_condition}.
-It is readily seen that $\lambda(s)$ closely approximates, but does not exactly equal, $\Kron$.
-The quantitative effect of this analysis-synthesis pair is discussed in Section \ref{sec:fidelity}.
+Fig. \ref{fig:synthfilters} shows the solutions found for the MWA's analysis filter defined in Eq. \eqref{eqn:filter}, for 12-, 18-, and 24-tap synthesis filter sizes.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{example-image-a}
+    \caption{Least-squares solutions for different filter sizes \dots}
+    \label{fig:synthfilters}
+\end{figure}
+Despite the complexity of the synthesis filters, they all share the same basic form as the analysis filter.
+This suggests that choosing a synthesis filter that is the mirror image of the analysis filter (i.e.
+$f[n] = h[-n]$), might also yield a reasonably good reconstruction, without having to calculate the optimal solutions numerically.
+The performance of both the mirror filter and the set of optimal solutions (for different choices of $P^\prime$) can be evaluated straightforwardly using Eq. \eqref{eqn:snr_short}.
+However, before comparing the results for various filters, there is another source of reconstruction error, specific to the MWA implementation of the PFB, that must first be considered.
 
-%\begin{figure}
-%    \centering
-%    \includegraphics[width=\columnwidth]{inverse_condition.eps}
-%    \caption{The condition for invertibility, Eq.
-\eqref{eqn:invertibility_condition}, demonstrated for the analysis filter given in Eq.
-\eqref{eqn:filter} and the synthesis filter given in Eq.
-\eqref{eqn:synthesisfilter}.
-The fact that $\lambda(s)$ only approximates the delta function gives rise to spurious artefacts (``temporal echoes'') in the time domain, which can be seen in Fig.
-\ref{fig:impulse_response}.}
-%    \label{fig:inverse_condition}
-%\end{figure}
+\subsection{Quantisation error}
+
+\subsection{Comparison of various filters}
 
@@
 
-\subsection{Implementation}
+\subsection{MWA Implementation}
 

### 2020-05-09 find_inverse.py

@@ -36,7 +36,7 @@ for a in range(len(filter_types)):
     else:
         Ftaps = filter_size
 
-    Hsize = (2*ntaps - 1, Ftaps)
+    Hsize = (Ftaps + ntaps - 1, Ftaps)
     Href = (Hsize[0] // 2, Hsize[1] // 2 - ntaps // 2)
 
     Fhat = np.zeros((Hsize[1], K))
@@ -80,16 +80,9 @@ for a in range(len(filter_types)):
         # Let's see how well the solution does
         Dhat[:,n:n+1] = np.matmul(H, Fhat[:,n:n+1])
 
-    # Finally, calculate the relative S/N for each n
-    SNR[a,:] = (Dhat[(Hsize[0] + 1)//2 - 1])**2 / np.sum(Dhat**2, axis=0)
-    SNR[a,:] = 10*np.log10(SNR[a,:])
-
-    # Remove the "correct" answer, to just be left with the errors
-    Dhat[(Hsize[0] + 1)//2 - 1] -= 1
-
-    '''
     # Plot figures
-    plt.figure("Least squares")
+    plt.figure("Filter coefficients")
+    plt.clf()
     F = Fhat.flatten()
     ns = np.arange(N)
     Fns = np.arange(F.size)
@@ -97,19 +90,31 @@ for a in range(len(filter_types)):
     plt.plot(Fns - F.size//2, F, label="Least squares sol'n")
     plt.legend()
     plt.tight_layout()
-    plt.savefig("rinv.png")
+    plt.savefig("rinv_{0}.eps".format(filter_size))
 
     plt.figure("Performance overall")
+    plt.clf()
     plt.imshow(Dhat, origin='lower', aspect='auto', cmap='bwr', extent=(-0.5, M+0.5, -(Hsize[0]+1)//2-0.5, (Hsize[0]+1)//2+0.5))
     cmax = np.max(np.abs(Dhat))
     plt.clim([-cmax, cmax])
-    plt.colorbar(label="$\\sum_{m=0}^{M-1}\,f[n-mM]\,h[(m+s)M-n] - \\delta_s^0$")
+    plt.colorbar(label="$\\sum_{m=0}^{M-1}\,f_m[n]\,h_m[sM-n] - \\delta_s^0$")
     plt.xlabel("$n$")
     plt.ylabel("$s$")
-    plt.savefig("rinv_perf.png")
+    plt.savefig("rinv_perf_{0}.png".format(filter_size))
+
+    # Finally, calculate the relative S/N for each n
[…]

### 2020-05-09 ipfb.tex
Chipping away at the new Quantisation Error section.

@@
 \begin{equation}
-    X_k[m] = \sum_{n=0}^{K-1} b[n]\,e^{-2\pi jkn/K},
+    X_k[m] = \sum_{n=0}^{K-1} b_m[n]\,e^{-2\pi jkn/K},
     \label{eqn:pfb}
@@
 \begin{equation*}
-    b[n] = \sum_{\rho=0}^{P-1} h[n + K\rho]\,x[n + mM + K\rho].
+    b_m[n] = \sum_{\rho=0}^{P-1} h[K\rho - n]\,x[n + mM - K\rho].
 \end{equation*}
@@
 \subsection{MWA implementation of the fine PFB}
+\label{sec:mwa_pfb}
 
@@
         }.
+    \label{eqn:snr_long}
 \end{equation}
@@
 
-Minimising the loss of S/N is equivalent to solving Eq. \eqref{eqn:invertibility_condition} in a least squares sense.
+Minimising the loss of S/N is equivalent to solving Eq. \eqref{eqn:invertibility_condition} using least squares regression.
 Since any given reconstructed sample only receives contributions from samples spaced one tap apart, Eq.
@@
         F^{(n)}_j    &= f_j[n], \\
-        D_i          &= \delta^{P-1}_i,
+        D_i          &= \delta^{(P^\prime+P)/2}_i,
     \end{aligned}
@@
        h_{P-2}[-n] & h_{P-1}[-n] & \cdots & 0 \\
-       \vdots & & \ddots & \vdots \\
-       h_0[-n] & h_1[-n] & \cdots & h_{P-1}[-n] \\
-       \vdots & & \ddots & \vdots \\
+       \vdots & \ddots & \ddots & \vdots \\
        0 & \cdots & h_0[-n] & h_1[-n] \\
        0 & \cdots & 0 & h_0[-n]
-    \end{bmatrix},
+    \end{bmatrix}
 \end{equation}
-with row number $i = P - 1$ (in $H^{(n)}$ and $D$) corresponding to the $s = 0$ term.
+with row number $i = (P^\prime + P)/2$ (in $H^{(n)}$ and $D$) corresponding to the $s = 0$ term\footnote{Note that since $P = 12$ for the PFB considered here, only the case where $P^\prime$ is even has been considered.}.
 
@@
 where ${H^{(n)}}^T$ is the transpose of $H^{(n)}$.
-With this notation, the reconstruction error can be more simply expressed
+With this notation, the reconstruction error can be more concisely expressed
 \begin{equation}
@@
 $f[n] = h[-n]$), might also yield a reasonably good reconstruction, without having to calculate the optimal solutions numerically.
-The performance of both the mirror filter and the set of optimal solutions (for different choices of $P^\prime$) can be evaluated straightforwardly using Eq. \eqref{eqn:snr_short}.
+The performance of both the (sub-optimal) mirror filter and the (optimal) set of least-squares solutions can be evaluated straightforwardly using Eq. \eqref{eqn:snr_short}.
 However, before comparing the results for various filters, there is another source of reconstruction error, specific to the MWA implementation of the PFB, that must first be considered.
@@
 \subsection{Quantisation error}
+
+The MWA implementation of the fine PFB differs from Eq.
+\eqref{eqn:pfb} in a few important respects, causing a reduction in the reconstructed S/N that would be present even if the synthesis filter perfectly inverted the analysis filter.
+The most significant difference is that both the coefficients $b[n]$ and the final sum undergo a rounding operation, resulting in the approximate (i.e. less precise and biased) spectrum
+\begin{equation}
+    \tilde{X}_k[m] = \left\lfloor\sum_{n=0}^{K-1} \bigg\lfloor b_m[n] \bigg\rfloor_{\text{asym}} e^{-2\pi jkn/K}\right\rfloor,
+\end{equation}
+where $\lfloor\cdot\rfloor$ denotes rounding to the nearest integer, and $\lfloor\cdot\rfloor_{\text{asym}}$ denotes the asymmetrical rounding scheme described in detail in Appendix \ref{sec:fpga_pfb}.
+Under these circumstances, Eq. \eqref{eqn:snr_long} cannot be used in its current form to estimate the signal loss, because it does not follow from the adjusted synthesis operation
+\begin{equation}
+    \hat{x}[n] = \sum_{m = -\infty}^{\infty} f[n - mM]\,
+        \frac{1}{K} \sum_{k=0}^{K-1} \tilde{X}_k[m]\,e^{2\pi jkn/K},
+    \label{eqn:ipfb_adjusted}
+\end{equation}
+which differs from Eq. \eqref{eqn:ipfb} only by the substitution $X_k[m] \rightarrow \tilde{X}_k[m]$.
 
@@
 
-We have implemented the synthesis filter defined in Eq.
-\eqref{eqn:synthesisfilter} as an optional component of the MWA-VCS beamforming software, \vcstools{}\footnote{\url{https://github.com/CIRA-Pulsars-and-Transients-Group/vcstools}}, described in \PaperI{}.
+We have implemented the ``mirror'' synthesis filter as an optional component of the MWA-VCS beamforming software, \vcstools{}\footnote{\url{https://github.com/CIRA-Pulsars-and-Transients-Group/vcstools}}, described in \PaperI{}.
 In this mode, a time series reconstructed from the beamformed fine channelised data is written out for each coarse channel as two separate polarisation streams (i.e.
@@
 \section{The FPGA implementation of the fine PFB}
+\label{sec:fpga_pfb}
 

### 2020-05-12 find_inverse.py
Added notes on quantisation effects

@@ -18,12 +18,12 @@ def ws(n):
 def h(n):
     return wH(n)*ws(n)*np.logical_and(n >= 0, n < N)
 
-# Choose the synthesis filter
+# The mirror synthesis filter
 def f(n):
     H = np.sum(h(ns))
     return h(-n)
 
-# Find some synthesis filters!
+# Find some other synthesis filters!
 filter_types = ["Mirror", 12, 18, 24]
 SNR = np.zeros((len(filter_types), K))
 
@@ -106,13 +106,11 @@ for a in range(len(filter_types)):
     SNR[a,:] = (Dhat[(Hsize[0] + 1)//2 - 1])**2 / np.sum(Dhat**2, axis=0)
     SNR[a,:] = 10*np.log10(SNR[a,:])
 
-    '''
     # Write out the spectrum to rinv.txt
-    header =  "Synthesis filter coefficients obtained by least squares solution to inverse analysis filter"
+    header =  "Synthesis filter coefficients for the {0}-tap filter\n".format(filter_size)
     header += "Generated by\n"
     header += "python" + " ".join(sys.argv)
-    np.savetxt("rinv.txt", F, header=header)
-    '''
+    np.savetxt("rinv_{0}.txt".format(filter_size), F, header=header)
 
     plt.figure("Reconstructed S/N")
     ms = np.arange(M)

### 2020-05-13 find_inverse.py
Made find_inverse.py generate a plot of the filter coefficients, to my liking

@@ -25,7 +25,9 @@ def f(n):
 
 # Find some other synthesis filters!
 filter_types = ["Mirror", 12, 18, 24]
+plottable = [0, 1, 2, 3] # The indices for which filters in "filter_types" should be plotted
 SNR = np.zeros((len(filter_types), K))
+fig, axs = plt.subplots(len(plottable), sharex=True, gridspec_kw={'hspace': 0}) # Plots for the filter coefficients
 
 for a in range(len(filter_types)):
 
@@ -80,17 +82,22 @@ for a in range(len(filter_types)):
         # Let's see how well the solution does
         Dhat[:,n:n+1] = np.matmul(H, Fhat[:,n:n+1])
 
-    # Plot figures
-    plt.figure("Filter coefficients")
-    plt.clf()
     F = Fhat.flatten()
     ns = np.arange(N)
     Fns = np.arange(F.size)
-    plt.plot(ns - N//2, h(ns), label='Analysis filter')
-    plt.plot(Fns - F.size//2, F, label="Least squares sol'n")
-    plt.legend()
-    plt.tight_layout()
-    plt.savefig("rinv_{0}.eps".format(filter_size))
+
+    # Plot figures
+    # The plot for the filter coefficients
+    if a in plottable:
+        if filter_types[a] == "Mirror":
+            label = "Mirror filter, {0} taps".format(Ftaps)
+        else:
+            label = "Least squares filter, {0} taps".format(filter_size)
+        plot_no = plottable.index(a)
+        axs[plot_no].plot(Fns - F.size//2, F, 'k-', label=label)
+        axs[plot_no].legend()
+        axs[plot_no].set_yticks([0,1])
+        axs[plot_no].set_ylabel(" ")
 
     plt.figure("Performance overall")
     plt.clf()
@@ -130,6 +137,11 @@ plt.ylim([-0.65,0.025])
 plt.tight_layout()
 plt.legend()
 plt.savefig("snr.eps")
+
+axs[-1].set_xlabel("Sample number, $n$")
+fig.text(0.02, 0.5, 'Normalised filter coefficients', va='center', rotation='vertical')
+fig.tight_layout()
+fig.savefig("inverse_filters.eps")
 
 '''
 # Show figures

### 2020-05-13 find_inverse.py
Adjusted the order of the subplots in inverse_filters.eps

@@ -25,7 +25,7 @@ def f(n):
 
 # Find some other synthesis filters!
 filter_types = ["Mirror", 12, 18, 24]
-plottable = [0, 1, 2, 3] # The indices for which filters in "filter_types" should be plotted
+plottable = [3, 2, 1, 0] # The indices for which filters in "filter_types" should be plotted
 SNR = np.zeros((len(filter_types), K))
 fig, axs = plt.subplots(len(plottable), sharex=True, gridspec_kw={'hspace': 0}) # Plots for the filter coefficients
 

### 2020-05-13 ipfb.tex
Still making sweeping changes to the paper, as well as incidental changes to some of the figures. Still got a long way to go.

@@
     \centering
-    \includegraphics[width=\columnwidth]{example-image-a}
-    \caption{Least-squares solutions for different filter sizes \dots}
+    \includegraphics[width=\columnwidth]{inverse_filters.eps}
+    \caption{The coefficients for four different synthesis filter designs: three generated using least-squares optimisation methods, and the sub-optimal mirror filter.}
     \label{fig:synthfilters}
@@
 Despite the complexity of the synthesis filters, they all share the same basic form as the analysis filter.
-This suggests that choosing a synthesis filter that is the mirror image of the analysis filter (i.e.
+This resemblance suggests that choosing a synthesis filter that is the mirror image of the analysis filter (i.e.
 $f[n] = h[-n]$), might also yield a reasonably good reconstruction, without having to calculate the optimal solutions numerically.
+
 The performance of both the (sub-optimal) mirror filter and the (optimal) set of least-squares solutions can be evaluated straightforwardly using Eq. \eqref{eqn:snr_short}.
-However, before comparing the results for various filters, there is another source of reconstruction error, specific to the MWA implementation of the PFB, that must first be considered.
+Fig.
+\ref{fig:snr} compares the loss of S/N due to each filter (under the assumption of noise-dominated samples), revealing that, as expected, the filters with the larger number of taps perform better, and the mirror filter performs the least well.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{snr.eps}
+    \caption{The reconstructed S/N, defined in Eqs.
+\eqref{eqn:snr_long} and \eqref{eqn:snr_short}, as a function of the position of the reconstructed sample within a tap for the filters displayed in Fig.
+\ref{fig:synthfilters}.}
+    \label{fig:snr}
+\end{figure}
 
-\subsection{Quantisation error}
+Presumably, one can achieve arbitrarily good performance by choosing a sufficiently long filter.
+However, the better performance of the longer filters is balanced by the increased computational resources and/or time required to apply them, which may exceed the system's design specifications.
+On the other hand, there is no advantage whatsoever gained by using the mirror filter over the least squares filter of the same length.
+
+\subsection{MWA Implementation}
+
+We initially implemented the mirror filter for the purpose of prototyping the synthesis filter, due to the ease of generating the coefficients, and the 12-tap least squares filter was implemented once proof-of-concept had been demonstrated.
+Both of these synthesis filters are available as optional components of the MWA-VCS beamforming software, \vcstools{}\footnote{\url{https://github.com/CIRA-Pulsars-and-Transients-Group/vcstools}}, described in \PaperI{}.
+Even though our system places no stringent limits on computational resources, we have not implemented the larger filters due to the identification of other sources of error that dominate over the reconstruction error defined above, rendering the advantages of the longer filters relatively minor in comparison.
+An analysis of these errors is presented in the following sections.
+
+Viewed as a linear operation, Eq. \eqref{eqn:ipfb} is ideally suited for GPUs, and we have implemented it in \vcstools{} for NVIDIA's CUDA architecture.
+Rather than use existing implementations of the implied inverse DFT, the $N \times K$ exponential terms (the so-called ``twiddle factors'') are pre-calculated and stored in a 2D array of double-precision floating point numbers on the GPUs.
+These are then accessed as required for the calculation of a given sample $\hat{x}[n]$.
+The combined GPU-accelerated calculations for both beamforming and coarse channel reconstruction run faster than real time\footnote{Verified for CUDA compute capability $>3.5$.}.
+
+Once the synthesis filter has been applied to each of the MWA's polarisation streams for each coarse channel, the resulting high-time resolution time series is written out as complex voltages (i.e.
+without converting to Stokes parameters) in the VDIF file format \citep{Whitney2009}.
+This format was chosen because it is supported by the coherent de-dispersion functionality of DSPSR\footnote{\url{http://dspsr.sourceforge.net/}} \citep{VanStraten2011b}, a software suite for processing pulsar time series.
+The VDIF format requires each sample to fit into a signed 8-bit complex integer data type, which is performed as the final step before writing to disk.
+
+\subsection{System performance}
 
@@
     \tilde{X}_k[m] = \left\lfloor\sum_{n=0}^{K-1} \bigg\lfloor b_m[n] \bigg\rfloor_{\text{asym}} e^{-2\pi jkn/K}\right\rfloor,
+    \label{eqn:rounded}
 \end{equation}
-where $\lfloor\cdot\rfloor$ denotes rounding to the nearest integer, and $\lfloor\cdot\rfloor_{\text{asym}}$ denotes the asymmetrical rounding scheme described in detail in Appendix \ref{sec:fpga_pfb}.
-Under these circumstances, Eq. \eqref{eqn:snr_long} cannot be used in its current form to estimate the signal loss, because it does not follow from the adjusted synthesis operation
+where $\lfloor\cdot\rfloor$ denotes a symmetric, and $\lfloor\cdot\rfloor_{\text{asym}}$, an asymmetric rounding operation, both of which are described in detail in Appendix \ref{sec:fpga_pfb}.
+
+The loss of precision implied by Eq. \eqref{eqn:rounded} naturally introduces further reconstruction errors in the back-to-back system.
+Unfortunately, Eq. \eqref{eqn:snr_long} cannot be used in its current form to estimate the signal loss, because it does not follow from the adjusted synthesis operation
 \begin{equation}
@@
 which differs from Eq. \eqref{eqn:ipfb} only by the substitution $X_k[m] \rightarrow \tilde{X}_k[m]$.
+Therefore, to estimate the performance of our system, we made use of a non-standard observing mode to record a small amount of simultaneous coarse and fine channel data (i.e.
+both before and after the fine PFB analysis filter stage).
+The fine channels from one polarisation of a single tile were extracted and subjected to both the mirror filter and the 12-tap least squares filter to reconstruct the $1.28\,$MHz coarse channel time series, which could then be compared directly with the original data (see Fig.
+\ref{fig:compare_timeseries}).
 
-\subsection{Comparison of various filters}
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{snr.eps}
-    \caption{The reconstructed S/N as a function of the position of the reconstructed sample within a tap.}
-    \label{fig:snr}
-\end{figure}
-
-\subsection{MWA Implementation}
-
-We have implemented the ``mirror'' synthesis filter as an optional component of the MWA-VCS beamforming software, \vcstools{}\footnote{\url{https://github.com/CIRA-Pulsars-and-Transients-Group/vcstools}}, described in \PaperI{}.
-In this mode, a time series reconstructed from the beamformed fine channelised data is written out for each coarse channel as two separate polarisation streams (i.e.
-without converting to Stokes parameters) in the VDIF file format \citep{Whitney2009}.
-This format was chosen because it is supported by the coherent de-dispersion functionality of DSPSR\footnote{\url{http://dspsr.sourceforge.net/}} \citep{VanStraten2011b}, a software suite for processing pulsar time series.
-
-The final stage before writing out the time series to file is the conversion from the complex floating point output of the synthesis operation into a signed 8-bit complex integer format required by the VDIF format.
-Each second of data is independently mean-subtracted and normalised in order to avoid clipping errors.
-It is worth noting that the mean-subtraction will mitigate to some degree the mean offset introduced by rounding errors in the analysis PFB (see the Appendix for details).
-
-Viewed as a linear operation, Eq. \eqref{eqn:ipfb} is ideally suited for GPUs, and we have implemented it in \vcstools{} for NVIDIA's CUDA architecture.
-Rather than use existing implementations of the implied inverse DFT, the $N \times K$ exponential terms (the so-called ``twiddle factors'') are pre-calculated and stored in a 2D array of double-precision floating point numbers on the GPUs.
-These are then accessed as required for the calculation of a given sample $\hat{x}[n]$.
-The combined GPU-accelerated calculations for both beamforming and coarse channel reconstruction run faster than real time\footnote{Verified for CUDA compute capability $>3.5$.}.
+\dots
 
@@
 
-In order to mitigate the replication error, we made use of a non-standard observing mode to record a small amount of simultaneous coarse and fine channel data (i.e.
-both before and after the fine PFB analysis filter stage).
-The fine channels from one polarisation of a single tile were extracted and subjected to the synthesis filter to reconstruct the $1.28\,$MHz coarse channel time series, which could then be compared directly with the original data (see Fig.
-\ref{fig:compare_timeseries}).
-Because the FPGA-based fine PFB was used in this test, the result is devoid of any replication error.
-However, the synthesis filter used in production uses an arbitrary scaling factor in order to make better use of the dynamic range afforded by VDIF's (8+8)-bit depth, and quantisation error is still present (and, in fact, dominates).
-Nevertheless, the agreement between the reconstructed samples and the original is very good, with both real and imaginary components having a correlation coefficient of approximately $0.94$.
+\dots
 

### 2020-05-13 find_inverse.py

@@ -24,8 +24,9 @@ def f(n):
     return h(-n)
 
 # Find some other synthesis filters!
-filter_types = ["Mirror", 12, 18, 24]
-plottable = [3, 2, 1, 0] # The indices for which filters in "filter_types" should be plotted
+filter_types = [24, 18, 12, "Mirror"]
+plottable = [0, 1, 2, 3] # The indices for which filters in "filter_types" should be plotted
+dashtypes = ['k:', 'k-.', 'k--', 'k-'] # These match up with the "filter_types" array
 SNR = np.zeros((len(filter_types), K))
 fig, axs = plt.subplots(len(plottable), sharex=True, gridspec_kw={'hspace': 0}) # Plots for the filter coefficients
 
@@ -89,10 +90,14 @@ for a in range(len(filter_types)):
     # Plot figures
     # The plot for the filter coefficients
     if a in plottable:
-        if filter_types[a] == "Mirror":
-            label = "Mirror filter, {0} taps".format(Ftaps)
+        if isinstance(filter_size, int):
+            label = "Least squares filter"
+        elif filter_size == "Mirror":
+            label = "Mirror filter"
         else:
-            label = "Least squares filter, {0} taps".format(filter_size)
+            label = "(undefined)"
+        label += ", {0} taps".format(Ftaps)
+
         plot_no = plottable.index(a)
         axs[plot_no].plot(Fns - F.size//2, F, 'k-', label=label)
         axs[plot_no].legend()
@@ -119,16 +124,19 @@ for a in range(len(filter_types)):
     header += "python" + " ".join(sys.argv)
     np.savetxt("rinv_{0}.txt".format(filter_size), F, header=header)
 
-    plt.figure("Reconstructed S/N")
     ms = np.arange(M)
-    if isinstance(filter_size, int):
-        label = "Least squares sol'n"
-    elif filter_size == "Mirror":
-        label = "Mirror filter"
-    else:
-        label = "(undefined)"
-    label += ", {0} taps".format(Ftaps)
-    plt.plot(ms, SNR[a,:], label=label)
+    if a in plottable:
+        plt.figure("Reconstructed S/N")
+
+        if isinstance(filter_size, int):
+            label = "Least squares filter"
+        elif filter_size == "Mirror":
+            label = "Mirror filter"
+        else:
+            label = "(undefined)"
+        label += ", {0} taps".format(Ftaps)
+
[…]

### 2020-05-28 find_inverse.py
Improved the look of the impulse response plot

@@ -104,11 +104,14 @@ for a in range(len(filter_types)):
         axs[plot_no].set_yticks([0,1])
         axs[plot_no].set_ylabel(" ")
 
+        xlims = [-18.5,18.5]
+        axs_imp[plot_no].plot(xlims,[-25,-25], color='gray', linestyle='dashed')
         axs_imp[plot_no].plot(ns/M - 5.5, 10*np.log10(impulse_response), 'k-', label=label)
         axs_imp[plot_no].legend()
-        axs_imp[plot_no].set_yticks([-60,-30,0])
+        axs_imp[plot_no].set_yticks([-50,-25,0])
         axs_imp[plot_no].set_ylabel(" ")
         axs_imp[plot_no].set_ylim([-70,5])
+        axs_imp[plot_no].set_xlim(xlims)
 
         plt.figure("Impulse response (zoom)")
         plt.plot(ns - 5.5*M, 10*np.log10(impulse_response), dashtypes[a], label=label)

### 2020-05-28 ipfb.tex
This is a 'complete' version of the draft that is considered to be put back to the referee, pending comments from the other authors.

@@
 \end{equation}
-It can be seen that perfect reconstruction corresponds to the case when the only non-zero contribution comes from the $s = 0$ term, giving rise to the necessary and sufficient condition
+Perfect reconstruction corresponds to the case when the only non-zero contribution comes from the $s = 0$ term, giving rise to the necessary and sufficient condition
 \begin{equation}
@@
 \begin{equation}
-    \frac{[\text{S/N}]_\text{recon}}{[\text{S/N}]_\text{orig}}
+    [\text{S/N}]_\text{recon}
       = \frac{\left(\sum\limits_{m = -\infty}^{\infty} f_m[n]\,h_m[-n]\right)^2}{
@@
 Consequently, any synthesis filter (except the exact inverse of the analysis filter, if it exists) will introduce a ``ringing'' effect into the reconstructed time series that has a period equal to the size of the PFB tap.
+
+The ``leakage'' of power into other samples implied by Eq. \eqref{eqn:snr_long} can also manifest itself as spurious imaging of a ``true'' signal at intervals of one tap.
+This can be seen by considering the effect of a single-sample impulse, with a power much greater than the ambient noise, on the reconstructed time series.
+The sample itself, say, $x[n]$, will be reconstructed with high fidelity, as the reconstructed error is only comprised of contributions from the (relatively) low-level noise.
+The reconstruction error of the sample $x[n+K]$, however, will be dominated by the term in Eq.
+\eqref{eqn:backtoback} involving $x[n]$, according to the relative weighting introduced by the analysis and synthesis filters.
+Thus, the impulse will reappear at intervals of one tap, but where the relative power of each appearance is given by
+\begin{equation}
+    p(s) = \left(\sum\limits_{m = -\infty}^{\infty} f_m[n]\,h_{m-s}[-n]\right)^2.
+    \label{eqn:ringing}
+\end{equation}
+This effect, termed temporal imaging, is discussed further in the context of specific filters.
 
@@
 \begin{equation}
-    \frac{[\text{S/N}]_\text{recon}}{[\text{S/N}]_\text{orig}}
-      = \frac{(\hat{D}_{P-1})^2}{\hat{D}^T \hat{D}},
+    [\text{S/N}]_\text{recon}
+      = \frac{(\hat{D}_{(P^\prime+P)/2})^2}{\hat{D}^T \hat{D}},
     \label{eqn:snr_short}
@@
     \centering
-    \includegraphics[width=\columnwidth]{snr.eps}
-    \caption{The reconstructed S/N, defined in Eqs.
+    \includegraphics[width=\columnwidth]{snr.eps} \\[10pt]
+    \includegraphics[width=\columnwidth]{impulse_response.eps}
+    \caption{\textit{Top}: The reconstructed S/N, defined in Eqs.
 \eqref{eqn:snr_long} and \eqref{eqn:snr_short}, as a function of the position of the reconstructed sample within a tap for the filters displayed in Fig.
-\ref{fig:synthfilters}.}
+\ref{fig:synthfilters}.
+\textit{Bottom}: The effect of temporal imaging, quantified in Eq.
+\eqref{eqn:ringing}, demonstrating how power ``leaks'' across adjacent taps during reconstruction.
+A grey dashed line is drawn at $-25\,$dB to aid visual comparison.}
     \label{fig:snr}
@@
 
-Presumably, one can achieve arbitrarily good performance by choosing a sufficiently long filter.
-However, the better performance of the longer filters is balanced by the increased computational resources and/or time required to apply them, which may exceed the system's design specifications.
-On the other hand, there is no advantage whatsoever gained by using the mirror filter over the least squares filter of the same length.
+Fig. \ref{fig:snr} suggests that one can achieve arbitrarily good performance by choosing a sufficiently long filter.
+However, the better performance of the longer filters is offset by the increased computational resources and/or time required to apply them, which may exceed the system's design specifications.
+Note that the mirror filter, being the same size as the 12-tap least squares filter, offers no advantage in terms of minimising the reconstruction error.
+On the other hand, the way that the signal power is distributed across multiple taps is markedly different for the two filter types, as shown in the bottom panel of Fig. \ref{fig:snr}.
+The mirror filter performs slightly worse in nearby taps, but drops off more quickly further out.
+For applications where the samples are signal-dominated, and minimising temporal imaging is more important than measuring the S/N of the signal precisely, the mirror filter may therefore offer some advantage over the least squares solution.
+However, observations of pulsars only rarely fall into this regime, even for observations of single pulses, where typically many samples must be averaged before the signal becomes more significant than the noise.
+A more detailed analysis of these effects are therefore outside the scope of the present work.
 
@@
 \eqref{eqn:pfb} in a few important respects, causing a reduction in the reconstructed S/N that would be present even if the synthesis filter perfectly inverted the analysis filter.
-The most significant difference is that both the coefficients $b[n]$ and the final sum undergo a rounding operation, resulting in the approximate (i.e. less precise and biased) spectrum
+The most significant difference is that both the coefficients $b[n]$ and the final sum undergo a rounding operation, resulting in the approximate (i.e. both less precise and biased) spectrum
 \begin{equation}
@@
 \end{equation}
-where $\lfloor\cdot\rfloor$ denotes a symmetric, and $\lfloor\cdot\rfloor_{\text{asym}}$, an asymmetric rounding operation, both of which are described in detail in Appendix \ref{sec:fpga_pfb}.
+where $\lfloor\cdot\rfloor$ and $\lfloor\cdot\rfloor_{\text{asym}}$ denote symmetric and asymmetric rounding operations respectively, described in Appendix \ref{sec:fpga_pfb}.
 
-The loss of precision implied by Eq. \eqref{eqn:rounded} naturally introduces further reconstruction errors in the back-to-back system.
-Unfortunately, Eq. \eqref{eqn:snr_long} cannot be used in its current form to estimate the signal loss, because it does not follow from the adjusted synthesis operation
-\begin{equation}
-    \hat{x}[n] = \sum_{m = -\infty}^{\infty} f[n - mM]\,
-        \frac{1}{K} \sum_{k=0}^{K-1} \tilde{X}_k[m]\,e^{2\pi jkn/K},
-    \label{eqn:ipfb_adjusted}
-\end{equation}
-which differs from Eq. \eqref{eqn:ipfb} only by the substitution $X_k[m] \rightarrow \tilde{X}_k[m]$.
-Therefore, to estimate the performance of our system, we made use of a non-standard observing mode to record a small amount of simultaneous coarse and fine channel data (i.e.
+The non-linearity of the back-to-back system induced by Eq. \eqref{eqn:rounded} implies that there is no single impulse response test that can adequately characterise the whole system.
+To wit, the results of an impulse response test depend sensitively on at least three factors: the magnitude of the impulse; its position within a tap; and the arbitrary scaling factor and quantisation applied at the end of the test required by the integer-based output formats.
+For example, an impulse at tap position $n = 0$ will be perfectly reproduced if its magnitude is chosen to minimise the amount of rounding that takes place during analysis.
+One the other hand, an impulse at $n = 64$ can be chosen such that the response is significantly worse than that implied by Fig. \ref{fig:snr}.
+
+For this reason, and also because the vast majority of applications of this system falls in the regime of noise-dominated samples, we have decided to forego the traditional impulse response test in favour of a back-to-back test involving real data collected expressly for this purpose.
+This is an empirical test of system that made use of a non-standard observing mode to record a small amount of simultaneous coarse and fine channel data (i.e.
 both before and after the fine PFB analysis filter stage).
-The fine channels from one polarisation of a single tile were extracted and subjected to both the mirror filter and the 12-tap least squares filter to reconstruct the $1.28\,$MHz coarse channel time series, which could then be compared directly with the original data (see Fig.
-\ref{fig:compare_timeseries}).
-
-\dots
-
-\subsection{Fidelity of reconstructed time series}
-\label{sec:fidelity}
-
-The major challenge in verifying the fidelity of the back-to-back analysis-synthesis filter pair is the fact that the analysis PFB only exists on the FPGAs used in production and not as stand-alone software that can be fed arbitrary input.
-This makes conducting standard impulse response tests impossible, unless the exact performance of the PFB can be reproduced.
-We have therefore attempted to replicate the PFB in software; however, the replication was not perfect, causing a small difference between the model analysis-synthesis back-to-back system, and the analysis-synthesis system used in production.
-
-In the fidelity tests presented in this section, we therefore consider a number of sources of error, all of which cause the reconstructed coarse channel time series, $\hat{x}[n]$, to differ from the original input time series, $x[n]$:
-\begin{description}
-    \item[``Replication error'':] The imperfect replication of the forward PFB, estimated to contribute noise-like error at the $-20\,$dB level (see Appendix for details);
-    \item[``Quantisation error'':] The error associated with the demotion of the input (5+5)-bit complex integers ($x[n]$) to the (4+4)-bit complex integer format output by the PFB (also see Appendix); and
-    \item[``Filter error'':] the error caused by the fact that the synthesis filter ($f[n]$) does not exactly complement the analysis filter ($h[n]$), in the sense described by Eq.
-\eqref{eqn:invertibility_condition} and Fig.
-\ref{fig:inverse_condition}.
-\end{description}
-Although knowing the relative contributions of quantisation and filter errors is useful for improving the system (since the latter may be mitigated by identifying a better synthesis filter), it is only necessary to know their joint contribution for the purposes of characterising the analysis-synthesis system.
-This contribution is revealed in an impulse response test, the results of which are shown in Fig. \eqref{fig:impulse_response}.
+The fine channels from one polarisation of a single tile were extracted and subjected to both the mirror filter and the 12-tap least squares filter to reconstruct the $1.28\,$MHz coarse channel time series, which could then be compared directly with the original data.
+The real and imaginary parts of the time series resulting from the least squares filter are shown in Fig. \ref{fig:compare_timeseries}.
 \begin{figure}
     \centering
-    \includegraphics[width=\columnwidth]{compare_coarse_imp.eps}
-    \caption{The response of the back-to-back analysis-synthesis system to a finite impulse.
-The coarse-channelised (reconstructed) output has been arbitrarily scaled to have a comparable magnitude to the original (5+5)-bit impulse, and the original impulse has been shifted slightly to the left for visual clarity.
-The spurious artefacts seen on either side of the central pulse at intervals of 64 samples are dominated by the so-called ``filter error'' (see text).}
-    \label{fig:impulse_response}
-\end{figure}
-
-As revealed by the impulse response test, our system is capable of reproducing the original impulse with high fidelity, despite the fact that the chosen synthesis filter is not ideal.
-The main discrepancy appears in the form of temporal ``echoes'' of the original impulse occurring at intervals of 64 coarse channel samples (i.e.
-half the size of one tap, equal to $50\,\mu$s for our sampling rate of $1.28\,$MHz) on either side of the reconstructed impulse.
-Although the power in the echoes is small compared to the central impulse (roughly $-10\,$dB level for the innermost echoes), the echoes always appear at the same locations relative to it.
-The asymmetry seen in Fig. \ref{fig:impulse_response} is due to replication error, quantisation error, the ``phase'' of the impulse with respect to the filter window, or some combination of the above.
-Importantly, echoes arising from strong, periodic individual pulses (e.g. in a pulsar signal) will accumulate in the same phase bins when the time series is folded at the pulsar's rotation period.
-Thus, any structure seen on this time scale ($\sim 50\,\mu$s) must therefore be regarded with suspicion.
-
-We also compared the result of the synthesis filter method with a simple 128-point inverse FFT, shown in Fig. \ref{fig:imp_sin_noise}.
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{compare_coarse_imp_all.eps}
-    \caption{Similar to Fig.
-\ref{fig:impulse_response}, but showing the real and imaginary parts separately.
-In this case, the original signal is composed of an impulse (real only), a sinusoid (real only), and noise (both real and imaginary), and subsequently quantised.
-The results of both the PFB synthesis and the inverse FFT are plotted for comparison.
-For each series, a vertical offset is added to make visual comparison easier.
-The PFB synthesis method is better at reconstructing the impulse and the sinusoid, but quantisation error dominates the noise for both PFB and FFT methods.}
-    \label{fig:imp_sin_noise}
-\end{figure}
-The input function consists of a single-bin impulse, a sinusoid, and Gaussian noise.
-Both the PFB synthesis and the inverse FFT are able to reproduce the impulse and the sinusoid, but less perfectly in the case of the inverse FFT method, as evidenced by the residuals.
-The difference between the two methods can be understood as the direct consequence of the differences between the spectral response of the forward PFB and an ordinary FFT.
-Another way to say this is that the synthesis filter, $f[n]$, that corresponds to the inverse FFT is even less well matched to the analysis PFB filter, in the sense of Eq.
-\eqref{eqn:invertibility_condition}, than the synthesis filter defined in Eq.
-\eqref{eqn:synthesisfilter}.
-Notably, if an FFT had been used in the MWA's fine channelisation stage (i.e.
-instead of the PFB), the inverse FFT would exactly reproduce the original high time resolution time series, even though the spectrum produced by the forward FFT would be a less perfect representation of the true spectrum, due to more prevalent spectral leakage (i.e.
-compared to the PFB).
-Finally, note that both the synthesis filter method and the inverse FFT show a similar amount of error in the construction of the Gaussian noise (cf.
-the imaginary component shown in Fig.
-\ref{fig:imp_sin_noise})---this is not surprising as replication and quantisation errors are present at this level.
-
-\dots
-
-Despite the errors in the reconstruction, the analysis-synthesis pair is able to reproduce the noise characteristics well enough for the errors not to significantly affect sufficiently bright pulsar signals, as demonstrated in the next section.
-However, these errors may become significant when observing low SNR pulsar emission.
-In these cases, the errors may be mitigated by averaging over multiple time bins (e.g.
-a coarser time resolution, or averaging many pulses together).
-
-\begin{figure}
-    \centering
-    \includegraphics[width=\columnwidth]{compare_timeseries.eps}
+    \includegraphics[width=\columnwidth]{compare_timeseries_LSQ12.eps}
     \caption{128 high time resolution ($1.28\,$MHz) samples from a single coarse channel and a single polarisation of one MWA tile.
 The real (top) and imaginary (bottom) components are shown separately.
-The original coarse channel data (black) are compared with the reconstructed data (red), with the residuals plotted in the lower panels.
+The original coarse channel data (black) are compared with the data reconstructed using the 12-tap least squares filter (red), with the residuals plotted in the lower panels.
 Because the VDIF data uses an arbitrary scaling factor, the red line has been rescaled by eye for a better visual comparison.}
@@
 \end{figure}
+
+With the original and reconstructed time series in hand, we estimated the S/N loss for each tap position by comparing the variance of the original time series (the `signal'), $\sigma_S^2$, with the variance of the residuals (the `noise'), $\sigma_N^2$.
+In analogy with Eq. \eqref{eqn:snr_long},
+\begin{equation}
+    [\text{S/N}]_\text{recon}
+      = \frac{\sigma_S^2}{\sigma_S^2 + \sigma_N^2}.
+    \label{eqn:snr_measured}
+\end{equation}
+Recognising that some of the noise variance is due to the synthesis filter (cf.
+Fig.
+\ref{fig:snr}), we have estimated the contribution due to rounding errors (and any other implementation-specific effects) by calculating the ``filter-subtracted'' S/N loss:
+\begin{equation}
+    [\text{S/N}]_\text{recon}
+      = \frac{\sigma_S^2}{\sigma_S^2 + (\sigma_N^2 - \sigma_\text{filter}^2)},
+    \label{eqn:snr_filter_subtracted}
+\end{equation}
+where $\sigma_\text{filter}$ is derived from Eq. \eqref{eqn:snr_long}.
+
+Fig.
+\ref{fig:snr_measured} shows the results for just under one second's worth of data ($1278464 \times 0.78\,\mu$s samples), where 1536 samples (one tap) were excised due to the synthesis filter being applied to zero-padded data beyond the edge of the second.
+\begin{figure}
+    \centering
+    \includegraphics[width=\columnwidth]{snr_measured.eps}
+    \caption{The S/N loss as a function of the position of the reconstructed sample within a tap for both the mirror filter and the 12-tap least squares filter.
+Both the total S/N loss (solid lines) and the S/N loss due to rounding and other implementation-specific effects (dashed lines) are plotted (cf.
+Eqs.
+\eqref{eqn:snr_measured} and \eqref{eqn:snr_filter_subtracted}).}
+    \label{fig:snr_measured}
+\end{figure}
+The remaining samples were sorted into their respective tap positions, and the variances calculated for each set (containing $1278464/128 = 9988$ samples).
+Near the edges of the tap, the rounding errors dominate the reconstruction noise, which we estimate contributes roughly $-0.26\,$dB of signal loss at all tap positions.
+In more central tap positions, however, the contributions from the rounding errors and the filters are comparable, and significant improvements could made by using longer filters.
+Nevertheless, unless there is a way to mitigate the rounding errors during the application of the analysis filter (explored below), it is unlikely that we will be able to achieve a total S/N loss better than approximately $-0.26\,$dB at any tap position.
+
+\subsubsection{Mitigating rounding errors}
+
+The original (i.e.
+before applying the fine PFB) high-time resolution samples are (5+5)-bit complex integers, scaled such that the bit occupancy is not so low that information is lost, and not so high that individual samples are clipped.
+Interestingly, one may question whether or not this known quantisation can be used to recover some of the information lost by the imperfect back-to-back system.
+If the errors are sufficiently small, then re-quantising the reconstructed samples will correct more errors than it introduces, giving overall better performance.
+
+In this section, we offer a short proof of the condition for which re-quantisation results in a net recovery of S/N for samples following Gaussian statistics.
+As before, let $\sigma_N^2$ be the variance of the residuals which are assumed to be drawn from a normal distribution with zero mean.
+The effect of re-quantisation on the variance is that every sample between $k-\frac12$ and $k+\frac12$, for any integer $k$, gets ``counted'' as if it had the value $k$.
+The adjusted variance, $\hat{\sigma}_N^2$, can then be expressed in terms of $\sigma_N^2$ via the second moment,
+\begin{equation}
+    \begin{aligned}
+        \hat{\sigma}_N^2
+         &= \sum_{k \in \mathbb{Z}} \int_{k-\frac12}^{k+\frac12} k^2
+            \frac{1}{\sigma_N\sqrt{2\pi}} e^{-\frac{x^2}{2\sigma_N^2}}\,dx, \\
+         &= \sum_{k \in \mathbb{Z}} k^2
+            \left[\frac12\text{erf}\left(\frac{k+\frac12}{\sigma_N\sqrt{2}}\right) -
+            \frac12\text{erf}\left(\frac{k-\frac12}{\sigma_N\sqrt{2}}\right)\right] \\
+         &= \sum_{k=1}^{\infty} k^2
+            \left[\text{erf}\left(\frac{k+\frac12}{\sigma_N\sqrt{2}}\right) -
+            \text{erf}\left(\frac{k-\frac12}{\sigma_N\sqrt{2}}\right)\right],
+    \end{aligned}
+\end{equation}
+where the last equality takes advantage of the symmetry of the error function.
+
+Re-quantisation is beneficial precisely when $\hat{\sigma}_N^2 < \sigma_N^2$, which can be shown by numerical methods to occur when $\sigma_N^2 \lesssim 0.29$.
+The MWA test data set presented above has a variance of approximately $6.7$, which implies that the total S/N loss of the back-to-back system would have to be smaller than $-0.05\,$dB before re-quantisation would improve the signal reconstruction.
+As Fig. \ref{fig:snr_measured} shows, this is not met for any tap position, so we did not pursue this possibility further.
 
@@
 \ref{fig:J2241_profiles}, bottom panel).
-Moreover, these new, low-frequency observations have allowed us to measure the DM of this pulsar with unprecedented precision ($\sim (2$-$6) \times 10^{-6}\,\dmunits$), with important consequences for measuring DM chromaticity and evaluating its effect on pulsar timing experiments.
+These have since been confirmed during follow-up observations (Kaur et al., in prep) using the Band 3 receiver ($250$ to $500\,$MHz) of the upgraded Giant Metrewave Radio Telescope (uGMRT).
+In addition, these new, low-frequency observations have allowed us to measure the DM of this pulsar with unprecedented precision ($\sim (2$-$6) \times 10^{-6}\,\dmunits$), with important consequences for measuring DM chromaticity and evaluating its effect on pulsar timing experiments.
 These results are discussed in detail in \citet{Kaur2019}.
 
-The resemblance of the newly-sighted precursor components to the temporal artefacts induced by the synthesis filter naturally raises questions about their authenticity.
-The fact that the components only appear on the leading side of the main pulse is a point in favour of them being real, since the temporal artefacts are expected to appear on both leading and trailing sides.
-In addition, the time interval between the main pulse and the closest component is $\sim150\,\mu$s, which, although it corresponds to the expected location of the third-order artefact, is not expected to be brighter than the first two (see Fig.
+%The resemblance of the newly-sighted precursor components to the temporal artefacts induced by the synthesis filter naturally raises questions about their authenticity.
+%The fact that the components only appear on the leading side of the main pulse is a point in favour of them being real, since the temporal artefacts are expected to appear on both leading and trailing sides.
+%In addition, the time interval between the main pulse and the closest component is $\sim150\,\mu$s, which, although it corresponds to the expected location of the third-order artefact, is not expected to be brighter than the first two (see Fig.
 \ref{fig:impulse_response}); however, no evidence of the lower-order artefacts is seen.
-Furthermore, our recent (independent) follow-up observations using the Band 3 receiver ($250$ to $500\,$MHz) of the upgraded Giant Metrewave Radio Telescope (uGMRT) have confirmed that at least the innermost component is real (Kaur et al., in prep).
+%Furthermore, our recent (independent) follow-up observations using the Band 3 receiver ($250$ to $500\,$MHz) of the upgraded Giant Metrewave Radio Telescope (uGMRT) have confirmed that at least the innermost component is real (Kaur et al., in prep).
 
@@
     \centering
-    \includegraphics[angle=270,width=\columnwidth]{J2241_063-172_FITS_profile.eps}
+    \includegraphics[angle=270,width=\columnwidth]{J2241_063-172_FITS_profile.eps} \\[10pt]
     \includegraphics[angle=270,width=\columnwidth]{J2241_063-172_vdif_profile.eps}
@@
 
-As described in the main text, it was necessary to replicate the function of the fine PFB in software in order to conduct impulse tests of the analysis-synthesis pair.
-Our CPU-based implementation differs from the algorithm described above only by the use of the FFTW library\footnote{\url{http://www.fftw.org/}} for the FFT stage, which uses (and outputs) floating point values.
-Nevertheless the resulting spectrum was found to contain a small number of quantisation ``errors'': slightly under $1\%$ of the output 4-bit values differed from the FPGA-produced values by 1.
-To quantify the effect of these quantisation errors, we recorded a small amount of coarse channel data (dominated by telescope noise) along with the contemporaneous spectrum output by the FPGA PFB.
-We used the GPU-based synthesis filter described in Section \ref{sec:ipfb} to reconstruct the coarse channel data from both the FPGA spectrum and the CPU spectrum generated by our own implementation.
-We found the results to differ from each other at less than the $-20\,$dB power level, which is much less than the estimated difference between the reconstructed coarse channel data and the original.
-
 \end{appendix}

### 2020-05-28 referee-report-20200409-response.txt
Started crafting a response to the referee

Dear editor & referee,

We would like to thank both of you for encouraging us to look more deeply into the justification of the synthesis filter that we were using. The result has been not only an improved paper (hopefully!) but also an improved system. We found it interesting to compare the performance of different kinds of filters, and hope that the extra rigour we've inserted into the "Synthesis filters" section will be acceptable to the referee and useful to the readers. On account of the extra work, several sections of the paper have been completely rewritten, as described below in the detailed comments.

----------------------------

Referee: This paper present a method for inversion of the 2nd-stage (fine) PFB on data recorded with the Murchison Widefield Array's Voltage Capture System, in order to recover high time resolution instead of the VCS' nominal fine (10kHz) frequency resolution. The authors demonstrate the performance on a trio of pulsars with known short-timescale emission structure. I appreciate very much the effort the authors went to to write up this work, and generally feel that more papers of this sort, covering signal analyses suitable suitable to radio observations, are needed in the literature. Unfortunately, as it stands, I don't see the novelty or scientific impact of this work, and cannot recommend it for publication in a peer-reviewed science journal. I strongly encourage the authors to flesh out their derivations, to justify and characterize the implementation more quantitatively, and re-submit. Detailed comments follow.

Referee: The paper begins with a concise review of PFBs. An overview of synthesis filters used to reverse their operation is given, and the problem is overall well motived. I applaud the authors for laying out the task so clearly.

Referee: The specific choice of synthesis filter, however, seems completely unmotivated and unjustified in any quantitative sense. The authors seem to simply argue "good enough is good enough," but for the central point of the paper I find this woefully insufficient, particularly when well-justified formulations are easily found online and in the community. A quick google reveals https://github.com/jrs65/pfb-inverse as the top result, where a least-squares solution to the inversion is presented. It appears to operate offline, but solves the artefacts described in this work. If the authors require realtime inversion to make it a part of the MWA VCS pipeline, computationally inexpensive solutions exist which vastly reduce the temporal echoes they see. Given that such solutions are in the community already, I would expect at minimum some proof of optimality for some well-chosen metric.

Authors: In hindsight, we completely agree that a paper such as this, if it does not attempt to provide a proper justification for the choice of synthesis filter, cannot possibly offer any value to the radio astronomy community who might be interested in replicating, or improving upon, our method. Accordingly, we investigated the least-squares solution that the referee recommended, and have provided a full, quantitative comparison of a multiple synthesis filters, including our original "mirror" filter and a few least-squares solutions of different lengths. In so doing, we inevitably found that the least-squares solution performs better than our original filter, and we provide a metric (with accompanying derivation) for comparing them.

I was glad to see the impulse response to characterize performance, but the comparison to an ifft seems silly except to point out that one should not expect iffts to invert pfbs.

The pulsar observations constitute a nice proof-of-concept, and serve as demonstrations of the chosen filter in the field as the authors do not pursue them to novel results. I do not understand the comparison of incoherently- to coherently-dedispersed profiles, it seems very much apples-to-oranges and not directly relevant to the variable time/freq division of the data. The time-resolved sub-pulse microstructure of B0950+08, however, is an impressive demonstration, well worth including in a revised paper.

Lastly, I would be remiss if I didn't express some concern that the PFB implemented on the FPGAs cannot be exactly reproduced on general-purpose compute hardware! The difference in hardware can hardly matter for a digital operation, and myriad libraries exist to implement arbitrary bit-depth arithmetic in CPUs. It's clear from the properties presented in appendix A that a number of awkward features are already reproduced, and I'd strongly encourage the authors to find an FFT implementation (or implement one themselves) which perfectly mimics that on the FPGA.

I'll close by saying again that I think the literature needs more papers covering topics like this, but they need to be addressed in at least the depth available via my quick google search. Please motivate the design of your synthesis filter, show that it is in some sense the correct filter to choose: optimal for some metric, or with artefacts below the noise floor for plausible observations, or at least theoretically motivated somehow. I would be delighted to have a solid PFB inversion process in the formal literature, and would like to see the authors resubmit after a more careful exploration or justification of the filter choice.

### 2020-05-28 referee-report-20200409-response.txt
Here is the version going out to the co-authors for pre-approval before getting returned to the referee

@@
 Authors: In hindsight, we completely agree that a paper such as this, if it does not attempt to provide a proper justification for the choice of synthesis filter, cannot possibly offer any value to the radio astronomy community who might be interested in replicating, or improving upon, our method.
-Accordingly, we investigated the least-squares solution that the referee recommended, and have provided a full, quantitative comparison of a multiple synthesis filters, including our original "mirror" filter and a few least-squares solutions of different lengths.
+Accordingly, we investigated the least-squares solution that the referee recommended, and have provided a full, quantitative comparison of multiple synthesis filters, including our original "mirror" filter and a few least-squares solutions of different lengths.
 In so doing, we inevitably found that the least-squares solution performs better than our original filter, and we provide a metric (with accompanying derivation) for comparing them.
+Armed with this analysis, we implemented (one of) the least squares filters in our software, which is now available.
+All of this is reflected in the completely written Sections 3 and 4.
 
-I was glad to see the impulse response to characterize performance, but the comparison to an ifft seems silly except to point out that one should not expect iffts to invert pfbs.
+Authors: The analysis also revealed that our earlier analysis of the temporal echoes was flawed.
+Our previous estimates of the magnitude of this effect were greatly exaggerated, and all subsequent test show that the temporal echoes that we see are consistent with the $\lesssim -25$ dB "ringing" shown in the bottom panel of (the new) Fig.
+4, which is a general feature of all imperfect back-to-back systems.
+Accordingly, we no longer had any reason to suppose that any of the features we saw in our pulsar observations were due to this effect, and have removed the relevant sentences from that section.
 
-The pulsar observations constitute a nice proof-of-concept, and serve as demonstrations of the chosen filter in the field as the authors do not pursue them to novel results.
+Referee: I was glad to see the impulse response to characterize performance, but the comparison to an ifft seems silly except to point out that one should not expect iffts to invert pfbs.
+
+Authors: Yes, we agree.
+The comparison with the ifft is not useful, and we have removed those paragraphs.
+However, the referee will note that the new version no longer contains an impulse response test.
+The justification for this decision we give in the paper itself (the second paragraph of Section 4), which amounts to an argument that the impulse response is not the best way to characterise the performance of our particular system (whose implementation introduces significant non-linearities).
+We therefore focus our efforts on the empirical test done on actual data (Section 4), being careful to quantify its performance in terms of the same metric introduced earlier (Section 3.1).
+
+Referee: The pulsar observations constitute a nice proof-of-concept, and serve as demonstrations of the chosen filter in the field as the authors do not pursue them to novel results.
 I do not understand the comparison of incoherently- to coherently-dedispersed profiles, it seems very much apples-to-oranges and not directly relevant to the variable time/freq division of the data.
@@
 
-Lastly, I would be remiss if I didn't express some concern that the PFB implemented on the FPGAs cannot be exactly reproduced on general-purpose compute hardware!
+Authors: The relevance of the comparison between coherent and incoherent de-dispersion lies in the fact having a high time resolution is useless if the resolution is limited by dispersive smearing across a fine channel, which can easily become the dominant factor for MSPs de-dispersed incoherently.
+In the original (non-high-time resolution) mode, coherent de-dispersion was not an option, and we wanted to showcase the difference.
+However, the point is well taken: this has more to do with the limitations of the downstream analysis, and not so much with the synthesis system itself.
+In order not to belabour that point, we have removed the incoherently de-dispersed version of the J2241−5236 plot (Fig 7); however, we have left both J0437-4715 plots in the paper (Fig 8), in order to help the reader identify the "notches" discussed in the text.
+
+Referee: Lastly, I would be remiss if I didn't express some concern that the PFB implemented on the FPGAs cannot be exactly reproduced on general-purpose compute hardware!
 The difference in hardware can hardly matter for a digital operation, and myriad libraries exist to implement arbitrary bit-depth arithmetic in CPUs.
@@
 
-I'll close by saying again that I think the literature needs more papers covering topics like this, but they need to be addressed in at least the depth available via my quick google search.
+Authors: Finding and running the correct version of the fixed-point FFT implemented on the FPGAs proved difficult: that version is no longer supported, and our early attempts to replicate it were not successful...
+although in honesty we cannot be 100% sure of the reason.
+Neverthess, this point may now be moot.
+If the referee accepts our arguments that the impulse response test does not adequately characterise the system, then there is no longer any need to reproduce the forward PFB.
+Instead, the empirical test we offer instead uses the actual implemented system, meaning that the reported performance includes any peculiarites introduced by the FPGA (related to the FFT or otherwise).
+Obviously it's less than satisfactory not to have a complete account of what the forward PFB is doing, but our investigations indicate that the rounding errors described in Section 4 and the Appendix account for virtually the entire error budget (beyond that introduced by the choice of synthesis filter itself).
+Any deeper investigation would only be warranted if there was some indication that such effects could be mitigated, which we don't find here.
+
+Referee: I'll close by saying again that I think the literature needs more papers covering topics like this, but they need to be addressed in at least the depth available via my quick google search.
 Please motivate the design of your synthesis filter, show that it is in some sense the correct filter to choose: optimal for some metric, or with artefacts below the noise floor for plausible observations, or at least theoretically motivated somehow.
 I would be delighted to have a solid PFB inversion process in the formal literature, and would like to see the authors resubmit after a more careful exploration or justification of the filter choice.
+
+Authors: We thank the referee again for this encouragement towards rigour, and hope that this latest version meets those standards!

### 2020-05-28 ipfb.tex
Here is the version going out to the co-authors for pre-approval before getting returned to the referee

@@
 This mode makes use of a polyphase synthesis filter to ``undo'' the polyphase analysis filter stage of the standard MWA's Voltage Capture System (VCS) observing mode.
-Sources of potential error in the reconstruction of the high time resolution data are identified and quantified, the most significant of which relate to ``temporal echoes'' seen in impulse response tests.
+Sources of potential error in the reconstruction of the high time resolution data are identified and quantified, with the S/N loss induced by the back-to-back system not exceeding $-0.65\,$dB for typical noise-dominated samples.
 The system is further verified by observing three pulsars with known structure on microsecond timescales.
@@
 
-\subsection{System performance}
+\section{System performance}
 
@@
 
-\section{Verification using pulsar observations}
+\subsection{Verification using pulsar observations}
 \label{sec:pulsardata}
@@
 Observations of three pulsars are presented here to validate the synthesis filter as a useful tool for undertaking high time resolution studies of pulsars with the MWA: MSPs \psrkaurJ{} and \psrbhatJ{}, and the bright, long-period PSR \psrslowB{}.
+All three of these observations were taken before the 12-tap least squares synthesis filter had been implemented, and were processed with the mirror filter.
+As Fig. \ref{fig:snr_measured} implies, the use of the mirror filter instead of the more optimal least squares filter would result in a further $\sim 0.1\,$dB reduction in S/N.
 
-\subsection{PSR \psrkaurJ{}}
+\subsubsection{PSR \psrkaurJ{}}
 
 \psrkaurJ{} has a rotation period of $2.18\,$ms and a dispersion measure (DM) of $11.41\,\dmunits$.
-The resulting dispersion smear across $10\,$kHz channels at the central observing frequency of $150.4\,$MHz is approximately $0.2\,$ms, or $45^\circ$ of rotation phase, consistent with the width of the average profile formed from incoherently de-dispersed, fine channelised data recorded with the MWA-VCS system (Fig.
-\ref{fig:J2241_profiles}, top panel).
+The resulting dispersion smear across $10\,$kHz channels at the central observing frequency of $150.4\,$MHz is approximately $0.2\,$ms, or $45^\circ$ of rotation phase, consistent with the width of the average profile formed from incoherently de-dispersed, fine channelised data recorded with the MWA-VCS system.
 Upon applying the synthesis filter and coherently de-dispersing the reconstructed time series sampled at the much higher rate of $1.28\,$MHz, the same data revealed exquisite detail in the average profile, including a pair of pre-cursor components that are only marginally visible (if at all) at higher frequencies (Fig.
-\ref{fig:J2241_profiles}, bottom panel).
+\ref{fig:J2241_profiles}).
 These have since been confirmed during follow-up observations (Kaur et al., in prep) using the Band 3 receiver ($250$ to $500\,$MHz) of the upgraded Giant Metrewave Radio Telescope (uGMRT).
@@
     \centering
-    \includegraphics[angle=270,width=\columnwidth]{J2241_063-172_FITS_profile.eps} \\[10pt]
     \includegraphics[angle=270,width=\columnwidth]{J2241_063-172_vdif_profile.eps}
-    \caption{Profiles of PSR \psrkaurJ{} made using incoherently de-dispersed, $10\,$kHz fine channels (top) and coherently de-dispersed, reconstructed coarse channels (bottom) from the same data set \citep{Kaur2019} (the flux scales are arbitrary).
-The possibility that the two small components on the leading side of the main pulse are artefacts of the synthesis filter has been ruled out (see accompanying text).}
+    \caption{The coherently de-dispersed profile of PSR \psrkaurJ{} made from the reconstructed coarse channels \citep{Kaur2019} (the flux scales are arbitrary).
+The two pre-cursor components on the leading side of the main pulse are separated by approximately $50\,\mu$s, and were first detected using the high time resolution mode.}
     \label{fig:J2241_profiles}
@@
 
-\subsection{PSR \psrbhatJ{}}
+\subsubsection{PSR \psrbhatJ{}}
 
@@
 
-\subsection{PSR \psrslowB{}}
+\subsubsection{PSR \psrslowB{}}
 
@@
 The result is a reconstructed, coarse channelised (pre-PFB) time series, suitable for high-time resolution studies of MSPs and other rapid transient signals.
-Although the reconstruction is not perfect, the introduced errors are quantified (up to $-10\,$dB in certain samples, and no more than $-20\,$dB elsewhere).
-The most significant artefacts, the ``temporal echoes'' of the impulse response, can be identified by virtue of the known timescale of their recurrence ($50\,\mu$s).
+Although the reconstruction is not perfect, the introduced errors are quantified (no exceeding $-0.65\,$dB for noise-dominated samples).
 
@@
 In each case, our results have been shown to be consistent with observations at other radio frequencies.
-In particular, we have demonstrated that the errors introduced by the imperfect analysis-synthesis filter pair are negligible compared to the pulsar signals themselves, which have been reconstructed with full polarisation at the faster sampling rate ($1.28\,$MHz) with high fidelity.
 The advent of the VCS high time resolution observing mode thus distinguishes the MWA as a premier low-frequency instrument for studying pulsars and other transients at microsecond resolution, with important implications for studies of the pulsar emission mechanism, the characterisation of the ISM in the ongoing search for gravitational waves, and others.
@@
 \begin{acknowledgements}
+We thank the anonymous referee for suggestions that greatly improved this work.
 This scientific work uses data obtained from the Murchison Radio-astronomy Observatory. We acknowledge the Wajarri Yamatji people as the traditional owners of the Observatory site.

### 2020-06-10 ipfb.tex
Put in changes re: updated B0950 plots, and added Keegan to the author list.

@@
 
-\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$, B. W. Meyers$^{1,2,3}$, S. E. Tremblay, J. Jones$^1$, B. Crosse$^1$
+\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$, B. W. Meyers$^{1,2,3}$, S. E. Tremblay, J. Jones$^1$, B. Crosse$^1$, K. Smith$^1$
 \affil{$^1$International Centre for Radio Astronomy Research (ICRAR), Curtin University, 1 Turner Avenue, Technology Park, Bentley, 6102, W.A., Australia}
@@
 To wit, the results of an impulse response test depend sensitively on at least three factors: the magnitude of the impulse; its position within a tap; and the arbitrary scaling factor and quantisation applied at the end of the test required by the integer-based output formats.
-For example, an impulse at tap position $n = 0$ will be perfectly reproduced if its magnitude is chosen to minimise the amount of rounding that takes place during analysis.
-One the other hand, an impulse at $n = 64$ can be chosen such that the response is significantly worse than that implied by Fig. \ref{fig:snr}.
+For example, an impulse at tap position $n \equiv 0$ (mod $K$) will be perfectly reproduced if its magnitude is such that the amount of rounding that takes place during analysis is minimised.
+On the other hand, an impulse at $n \equiv 64$ (mod $K$) can be chosen such that the response is significantly worse than that implied by Fig. \ref{fig:snr}.
 
@@
 
-\subsubsection{Mitigating rounding errors}
+\subsubsection*{Mitigation of rounding errors}
 
@@
 As Fig. \ref{fig:snr_measured} shows, this is not met for any tap position, so we did not pursue this possibility further.
+However, systems that are able to achieve better than $\sigma_N^2 \lesssim 0.29$ may do better yet by re-quantising the suitably scaled reconstructed samples.
 
@@
 Observations of three pulsars are presented here to validate the synthesis filter as a useful tool for undertaking high time resolution studies of pulsars with the MWA: MSPs \psrkaurJ{} and \psrbhatJ{}, and the bright, long-period PSR \psrslowB{}.
-All three of these observations were taken before the 12-tap least squares synthesis filter had been implemented, and were processed with the mirror filter.
+The first two pulsars were processed with the mirror filter, and \psrslowB{} was processed with the 12-tap least squares filter.
 As Fig. \ref{fig:snr_measured} implies, the use of the mirror filter instead of the more optimal least squares filter would result in a further $\sim 0.1\,$dB reduction in S/N.
@@
 A total of eighty seconds (315 pulses) of data ($128 \times 10\,$kHz fine channels) were recorded, beamformed, and subjected to the polyphase synthesis filter.
-The mean profile formed from the entire data set is shown in Fig. \ref{fig:0950_80_secs}.
+Across the MWA bandwidth, we used PSRCHIVE's RMFIT to measure an approximate rotation measure (RM) of $1.43 \pm 0.15\,$rad m$^{-2}$, which is consistent with previous measurements of this pulsar's RM \citep[e.g.][]{Noutsos2015}.
+The mean profile formed from the one coarse channel is shown in Fig. \ref{fig:0950_80_secs}.
 Several individual pulses were sufficiently bright to see substructure.
-One such pulse is showcased in Fig. \ref{fig:0950_single_pulse} at three different time resolutions (corresponding to the chosen bin width of each plot).
+One such pulse is showcased in Fig. \ref{fig:0950_single_pulse}, where all 24 coarse channels were integrated to maximise the S/N.
+To highlight the pulse's substructure, we show it at three different time resolutions (corresponding to the chosen bin width of each plot).
 
@@
     \centering
-    \includegraphics[width=\columnwidth]{200ms_res.eps} \\[10pt]
-    \includegraphics[width=\columnwidth]{50ms_res.eps} \\[10pt]
-    \includegraphics[width=\columnwidth]{5ms_res.eps}
-    \caption{A bright, single pulse of \psrslowB{}, displayed with full polarisation at time resolutions of $\sim 200\,\mu$s (top), $\sim 50\,\mu$s (middle), and $\sim 5\,\mu$s (bottom).
-The total time span of the displayed windows are $253\,$ms, $25.3\,$ms, and $2.53\,$ms, respectively.}
+    \includegraphics[width=0.7\columnwidth,angle=270]{200us.eps} \\[10pt]
+    \includegraphics[width=0.7\columnwidth,angle=270]{50us.eps} \\[10pt]
+    \includegraphics[width=0.7\columnwidth,angle=270]{5us.eps}
+    \caption{A bright, single pulse of \psrslowB{}, integrated over $24 \times 1.28\,$MHz coarse channels, and displayed with full polarisation at time resolutions of $\sim 200\,\mu$s (top), $\sim 50\,\mu$s (middle), and $\sim 5\,\mu$s (bottom).}
     \label{fig:0950_single_pulse}
@@
 
-Using observations at $102.5\,$MHz, \citet{Kuzmin2003} report microstructure with a characteristic timescale of $\sim 60\mu$s.
-Despite the proximity of this timescale to the temporal ``echoes'' induced by the synthesis filter ($50\,\mu$s), we are able to unambiguously identify the $\sim 60\,\mu$s microstructure.
-We also suggest that the finest observable structures (Fig. \ref{fig:0950_single_pulse}, bottom plot) might correspond to the $\sim 10\,\mu$s structures reported by \citet{Popov2002} at $1.65\,$GHz.
+Using observations at $102.5\,$MHz, \citet{Kuzmin2003} report microstructure with a characteristic timescale of $\sim 60\mu$s, which we are able to unambiguously identify in our data.
+We suggest that the finest observable structures (Fig. \ref{fig:0950_single_pulse}, bottom plot) might correspond to the $\sim 10\,\mu$s structures reported by \citet{Popov2002} at $1.65\,$GHz.
 However, \citet{Kuzmin2003} used only a single linear polarisation feed, and \citet{Popov2002}, only a left-handed circularly polarised feed.
@@
 The result is a reconstructed, coarse channelised (pre-PFB) time series, suitable for high-time resolution studies of MSPs and other rapid transient signals.
-Although the reconstruction is not perfect, the introduced errors are quantified (no exceeding $-0.65\,$dB for noise-dominated samples).
+Although the reconstruction is not perfect, the average error does not exceed $-0.65\,$dB for noise-dominated samples.
 

### 2020-06-10 referee-report-20200409-response.txt
Updated the response to the referee to include Keegan's contributions and to touch up a few other bits and pieces.

@@
 On account of the extra work, several sections of the paper have been completely rewritten, as described below in the detailed comments.
+
+The task of getting the improved filter into production was carried out by K.
+Smith.
+Because we would not have an in-production system ready by this point if it had not been for his efforts, I would like to request that he be allowed to join the list of authors, as indicated in the manuscript.
+Please advise us if this is a problem.
 
@@
 Authors: In hindsight, we completely agree that a paper such as this, if it does not attempt to provide a proper justification for the choice of synthesis filter, cannot possibly offer any value to the radio astronomy community who might be interested in replicating, or improving upon, our method.
-Accordingly, we investigated the least-squares solution that the referee recommended, and have provided a full, quantitative comparison of multiple synthesis filters, including our original "mirror" filter and a few least-squares solutions of different lengths.
+Accordingly, we investigated the least-squares solution that the referee recommended, and have provided a full, quantitative comparison of multiple synthesis filters, including our original "mirror" filter and a few least-squares solutions of different tap lengths.
 In so doing, we inevitably found that the least-squares solution performs better than our original filter, and we provide a metric (with accompanying derivation) for comparing them.
@@
 However, the referee will note that the new version no longer contains an impulse response test.
-The justification for this decision we give in the paper itself (the second paragraph of Section 4), which amounts to an argument that the impulse response is not the best way to characterise the performance of our particular system (whose implementation introduces significant non-linearities).
+The justification for this decision we give in the paper itself (the second paragraph of Section 4), which amounts to an argument that the impulse response is not the best way to characterise the performance of our particular system, where significant non-linearities are introduced by rounding effects.
 We therefore focus our efforts on the empirical test done on actual data (Section 4), being careful to quantify its performance in terms of the same metric introduced earlier (Section 3.1).
@@
 Instead, the empirical test we offer instead uses the actual implemented system, meaning that the reported performance includes any peculiarites introduced by the FPGA (related to the FFT or otherwise).
-Obviously it's less than satisfactory not to have a complete account of what the forward PFB is doing, but our investigations indicate that the rounding errors described in Section 4 and the Appendix account for virtually the entire error budget (beyond that introduced by the choice of synthesis filter itself).
+Obviously it's less than satisfactory not to have a complete account of what the forward PFB is doing, but our investigations indicate that the rounding errors described in Section 4 and in the Appendix account for virtually the entire error budget (beyond that introduced by the choice of synthesis filter itself).
 Any deeper investigation would only be warranted if there was some indication that such effects could be mitigated, which we don't find here.

### 2020-07-07 ipfb.tex
Accepted version (without the boldface change markups)

@@
 
-\newcommand{\changes}[1]{{\color{red}#1}}
-
 \title[MWA tied-array processing III]{MWA tied-array processing III: Microsecond time resolution via a polyphase synthesis filter}
 
-\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$, B. W. Meyers$^{1,2,3}$, S. E. Tremblay, J. Jones$^1$, B. Crosse$^1$, K. Smith$^1$
+\author[McSweeney et al.]{S. J. McSweeney$^1$, S. M. Ord$^2$, D. Kaur$^1$, N. D. R. Bhat$^1$, B. W. Meyers$^{1,2,3}$, S. E. Tremblay, J. Jones$^1$, B. Crosse$^1$, K. R. Smith$^1$
 \affil{$^1$International Centre for Radio Astronomy Research (ICRAR), Curtin University, 1 Turner Avenue, Technology Park, Bentley, 6102, W.A., Australia}
@@
 However, observations of pulsars only rarely fall into this regime, even for observations of single pulses, where typically many samples must be averaged before the signal becomes more significant than the noise.
-A more detailed analysis of these effects are therefore outside the scope of the present work.
+A more detailed analysis of these effects is therefore outside the scope of the present work.
 
@@
 A total of eighty seconds (315 pulses) of data ($128 \times 10\,$kHz fine channels) were recorded, beamformed, and subjected to the polyphase synthesis filter.
-Across the MWA bandwidth, we used PSRCHIVE's RMFIT to measure an approximate rotation measure (RM) of $1.43 \pm 0.15\,$rad m$^{-2}$, which is consistent with previous measurements of this pulsar's RM \citep[e.g.][]{Noutsos2015}.
+Across the MWA bandwidth, we used the RM synthesis technique\footnote{\url{https://github.com/gheald/RMtoolkit}} \citep{Brentjens2005} to measure a rotation measure (RM) of $1.43 \pm 0.15\,$rad m$^{-2}$, which is consistent with previous measurements of this pulsar's RM \citep[e.g.][]{Noutsos2015}.
 The mean profile formed from the one coarse channel is shown in Fig. \ref{fig:0950_80_secs}.
